---
title: Multilevel missingess
author: "Heleen Brüggen"
format: 
    html:
        toc: true
        number-sections: true
        toc-location: right
bibliography: references.bib
---

```{r}
#| label: set-up
#| warning: false
#| message: false
#| echo: false

#############
# Libraries #
#############
library(tidyverse)
library(knitr)
library(DT)
library(lme4)
library(mitml)
library(mice)
library(lmerTest)
library(magrittr)
library(purrr)
library(furrr)
library(dplyr)
library(pbapply)
library(parallel)
library(readr)
library(jtools)
library(broom.mixed)
library(ggmice)
library(nlme)
library(ggplot2)
################
# Setting seed #
################
set.seed(123)
################
# Setting path #
################
path <-"/Users/Heleen/Library/Mobile Documents/com~apple~CloudDocs/Master Thesis/MBART-MICE files/"
#######################
# Defining parameters #
#######################
combinations <- read_rds(paste(path, "data/combinations.rds", sep = "") )
#############################
# Storing names of datasets #
#############################
names <- read_rds(paste(path, "data/names.rds", sep = ""))
```

## Creating missing data in a univariate way

### Adding code from Gerko for univariate missing data
The following code is a function to ampute data according the univariate missingness mechanismsL MAR, MCAR or MNAR.
The function has the following arguments: 

- `data`: the data in matrix or data-frame format
- `mis.var`: the column specifier (number) for the variable to be amputed.
- `cov.var`:the column specifier (number) for the covariate the MAR missingness is based on
- `prop.mis`:	proportion of missingness. Options are `c(.25, .5)`.
- `m.mech`:	The missingness mechanism. Options are `c("MARleft", "MARright", "MARmid","MARtail", "MCAR")`.

The output is: 

- `data.rm`: the data with missing values
- `p.MAR`: the probability of missingness
- `mis.info`: a data frame with the missingness mechanism and the proportion of missing data.
```{r}
#| label: univatiatemissingdata
#| echo: true
#| code-fold: false

ampute.data <- function(data, mis.var, cov.var, prop.mis, m.mech = "MARleft") {
    data.rm <- data # assigning data to new object
    n <- nrow(data.rm) # amount of rows in data
    inv.log <- function(x) { # inverse logit function
        exp(x) / (1 + exp(x))
    }
    m.cov <- mean(data.rm[, cov.var]) # mean of covariate variable

    if (prop.mis == .1) { # if prop = 10% ...
        ML <- (mean(data[, cov.var]) - data[, cov.var]) / sd(data[, cov.var]) - 2.56 # ... then MARleft is calculated as ...
        MR <- (-mean(data[, cov.var]) + data[, cov.var]) / sd(data[, cov.var]) - 2.56 # ... MARright is calculated as ...
        MM <- (.75 - abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) - 2.25 # ... MARmid is calculated as ...
        MT <- (-.75 + abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) - 2.4 # ... MARtail is calculated as ...
    }
    if (prop.mis == .25) { # if prop = 25% ...
        ML <- (mean(data[, cov.var]) - data[, cov.var]) / sd(data[, cov.var]) - 1.3 # ... then MARleft is calculated as ...
        MR <- (-mean(data[, cov.var]) + data[, cov.var]) / sd(data[, cov.var]) - 1.3 # ... MARright is calculated as ...
        MM <- (.75 - abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) - 1.15 # ... MARmid is calculated as ...
        MT <- (-.75 + abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) - 1.225 # ... MARtail is calculated as ...
    }
    if (prop.mis == .5) { # if prop = 50% ...
        ML <- (mean(data[, cov.var]) - data[, cov.var]) / sd(data[, cov.var]) # ... then MARleft is calculated as ...
        MR <- (-mean(data[, cov.var]) + data[, cov.var]) / sd(data[, cov.var]) # ... MARright is calculated as ...
        MM <- (.75 - abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) # ... MARmid is calculated as ...
        MT <- (-.75 + abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) # ... MARtail is calculated as ...
    }


    if (m.mech == "MARleft") { # if missingness mechanism is MARleft ...
        p.MAR <- inv.log(ML) # ... then take inverse logit of ML ...
        data.rm[1 == rbinom(n, 1, p.MAR), mis.var] <- NA # ... and assign NA to the missing variable with a probability of p.MAR
    }

    if (m.mech == "MARright") {
        p.MAR <- inv.log(MR)
        data.rm[1 == rbinom(n, 1, p.MAR), mis.var] <- NA
    }

    if (m.mech == "MARmid") {
        p.MAR <- inv.log(MM)
        data.rm[1 == rbinom(n, 1, p.MAR), mis.var] <- NA
    }

    if (m.mech == "MARtail") {
        p.MAR <- inv.log(MT)
        data.rm[1 == rbinom(n, 1, p.MAR), mis.var] <- NA
    }

    if (m.mech == "MCAR") {
        p.MAR <- rep(prop.mis, nrow(data.rm))
        data.rm[0 == rbinom(n, 1, 1 - prop.mis), mis.var] <- NA
    }

    # Prepare data for return
    true.mis <- mean(is.na(data.rm[, mis.var])) # calculate proportion of missing data
    mis.info <- data.frame(Mechanism = m.mech, Proportion = true.mis) # create data frame with missingness mechanism and proportion of missing data
    output <- list(data.rm, p.MAR, mis.info) # create list with data, p.MAR and mis.info
    names(output) <- c("data", "p.mis", "info") # assign names to list elements
    return(output)
}
```

### Loading data
```{r}
#| label: loadingdata
#| echo: true
#| code-fold: false

data <- list()
data.relevant <- list()
for (i in seq_len(nrow(combinations))) {
    data[[i]] <- read_rds(paste(path, "data/complete/simdata_", names[i], ".rds", sep = ""))[1:100]
    data.relevant[[i]] <- map(data[[i]], \(x) x %>%
        select(y, x1, x2, x3, x4, x5, x6, x7, z1, z2) %>%
        as.data.frame())
}

missing_data <- list()
for (i in seq_len(nrow(combinations))) {
    missing_data[[i]] <- read_rds(paste(path, "data/missing/simdata_miss_", names[i], ".rds", sep = ""))[1:100]
}
missing_data.relevant <- map(missing_data, \(x) map(x, \(y) y %>%
    select(y, x1, x2, x3, x4, x5, x6, x7, z1, z2) %>%
    as.data.frame()))
```

### Creating missing data

```{r}
#| label: correlations
#| echo: false

cor <- map(seq_len(nrow(combinations)), function(i) {
    cor_dat <- lapply(data[[i]], function(x) cor(x[, c("y", "x1", "x2", "x3", "x4", "x5", "x6", "x7", "z1", "z2")])) %>%
        Reduce("+", .) / length(data[[i]])
})
```

::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| label: tbl-cor30_15_mar
#| echo: false

datatable(
    cor[[1]],
    caption = paste("Correlation of", names[1]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 50_15_mar
```{r}
#| label: tbl-cor50_15_mar
#| echo: false

datatable(
    cor[[2]],
    caption = paste("Correlation of", names[2]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 30_50_mar
```{r}
#| label: tbl-cor30_50_mar
#| echo: false

datatable(
    cor[[3]],
    caption = paste("Correlation of", names[3]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 50_50_mar 
```{r}
#| label: tbl-cor50_50_mar
#| echo: false

datatable(
    cor[[4]],
    caption = paste("Correlation of", names[4]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 30_15_mcar
```{r}
#| label: tbl-cor30_15_mcar
#| echo: false

datatable(
    cor[[5]],
    caption = paste("Correlation of", names[5]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 50_15_mcar
```{r}
#| label: tbl-cor50_15_mcar
#| echo: false

datatable(
    cor[[6]],
    caption = paste("Correlation of", names[6]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 30_50_mcar
```{r}
#| label: tbl-cor30_50_mcar
#| echo: false

datatable(
    cor[[7]],
    caption = paste("Correlation of", names[7]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 50_50_mcar
```{r}
#| label: tbl-cor50_50_mcar
#| echo: false

datatable(
    cor[[8]],
    caption = paste("Correlation of", names[8]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

:::

:::

Next, we will ampute the data according to a univariate MAR right mechanism -- x1, x2, x3, x5, x6, x7, z1, z2, and y will be made incomplete based in x4. The proportion of missing data is set to 10% to try to mimic the missing data patterns in the multivariate missing data.
```{r}
#| label: singularmissingdata
#| echo: true
#| code-fold: true
#| eval: false

missing <- list()
data.relevant <- list()
shadow.data <- list()
for (i in seq_len(nrow(combinations))) {
    data.relevant[[i]] <- map(data[[i]], \(x) x %>%
        select(y, x1, x2, x3, x4, x5, x6, x7, z1, z2) %>%
        as.data.frame())

    shadow.data[[i]] <- map(data.relevant[[i]], \(x) cbind(x, x %>% select(x4, z2)))

    if (combinations[i, 4] == "mar") {
        m.mech <- "MARright"
    } else {
        m.mech <- "MCAR"
    }

    missing[[i]] <- map(shadow.data[[i]], \(x) ampute.data(x, mis.var = 1, cov.var = 11, prop.mis = .1, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 2, cov.var = 11, prop.mis = .1, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 3, cov.var = 11, prop.mis = .1, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 4, cov.var = 11, prop.mis = .1, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 5, cov.var = 11, prop.mis = .1, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 6, cov.var = 11, prop.mis = .1, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 7, cov.var = 11, prop.mis = .1, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 8, cov.var = 11, prop.mis = .1, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 9, cov.var = 11, prop.mis = .1, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 10, cov.var = 11, prop.mis = .1, m.mech = m.mech)) %>%
        map(., \(x) x$data[, 1:10] %>% as.data.frame())
    
    write_rds(missing[[i]], paste(path, "data/missinguni/simdata_miss_", names[i], ".rds", sep = ""))
}

missing_data.relevant[[1]][[1]] %>% ggmice::plot_pattern()
missing[[1]][[1]] %>% ggmice::plot_pattern()
```

```{r}
#| label: loading-data-univariate
#| echo: true
#| code-fold: false

missing <- list()
for (i in seq_len(nrow(combinations))) {
    missing[[i]] <- read_rds(paste(path, "data/missinguni/simdata_miss_", names[i], ".rds", sep = ""))
}
```

### Inspecting the missingess in the data
Let's inspect the first data set with missing data.

#### Density plots of the complete and incomplete data 

::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| label: fig-inspectmissingdata
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[1]][[1]], missing[[1]][[1]], missing_data.relevant[[1]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "univariate incomplete", "multivariate incomplete"), each = ncol(data.relevant[[1]][[1]]), times = nrow(data.relevant[[1]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_15_mar
```{r}
#| label: fig-inspectmissingdata2
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[2]][[1]], missing[[2]][[1]], missing_data.relevant[[2]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "univariate incomplete", "multivariate incomplete"), each = ncol(data.relevant[[2]][[1]]), times = nrow(data.relevant[[2]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_50_mar
```{r}
#| label: fig-inspectmissingdata3
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[3]][[1]], missing[[3]][[1]], missing_data.relevant[[3]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "univariate incomplete", "multivariate incomplete"), each = ncol(data.relevant[[3]][[1]]), times = nrow(data.relevant[[3]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_50_mar
```{r}
#| label: fig-inspectmissingdata4
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[4]][[1]], missing[[4]][[1]], missing_data.relevant[[4]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "univariate incomplete", "multivariate incomplete"), each = ncol(data.relevant[[4]][[1]]), times = nrow(data.relevant[[4]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_15_mcar
```{r}
#| label: fig-inspectmissingdata5
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[5]][[1]], missing[[5]][[1]], missing_data.relevant[[5]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "univariate incomplete", "multivariate incomplete"), each = ncol(data.relevant[[5]][[1]]), times = nrow(data.relevant[[5]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_15_mcar
```{r}
#| label: fig-inspectmissingdata6
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[6]][[1]], missing[[6]][[1]], missing_data.relevant[[6]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "univariate incomplete", "multivariate incomplete"), each = ncol(data.relevant[[6]][[1]]), times = nrow(data.relevant[[6]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_50_mar
```{r}
#| label: fig-inspectmissingdata7
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[7]][[1]], missing[[7]][[1]], missing_data.relevant[[7]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "univariate incomplete", "multivariate incomplete"), each = ncol(data.relevant[[7]][[1]]), times = nrow(data.relevant[[7]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_50_mar
```{r}
#| label: fig-inspectmissingdata8
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[8]][[1]], missing[[8]][[1]], missing_data.relevant[[8]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "univariate incomplete", "multivariate incomplete"), each = ncol(data.relevant[[8]][[1]]), times = nrow(data.relevant[[8]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

:::

:::

#### Density plots of the non-missing and missing data

::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| label: fig-is.naplots
#| echo: true
#| code-fold: true
#| fig.cap: 
#|  - "Density plot of non-missing and univariate missing data for every variable"
#|  - "Density plot of non-missing and multivariate missing data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[1]][[1]] %>% is.na()
missing_data.na <- missing_data.relevant[[1]][[1]] %>% is.na()

data.long <- data.relevant[[1]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.multivariate <- cbind(data.long, missing.long$value)
colnames(combined.multivariate) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.multivariate, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_15_mar
```{r}
#| label: fig-is.naplots2
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and univariate missing data for every variable"
#|  - "Density plot of non-missing and multivariate missing data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[2]][[1]] %>% is.na()
missing_data.na <- missing_data.relevant[[2]][[1]] %>% is.na()

data.long <- data.relevant[[2]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.multivariate <- cbind(data.long, missing.long$value)
colnames(combined.multivariate) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.multivariate, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_50_mar
```{r}
#| label: fig-is.naplots3
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and univariate missing data for every variable"
#|  - "Density plot of non-missing and multivariate missing data for every variable"#| fig.width: 12
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[3]][[1]] %>% is.na()
missing_data.na <- missing_data.relevant[[3]][[1]] %>% is.na()

data.long <- data.relevant[[3]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.multivariate <- cbind(data.long, missing.long$value)
colnames(combined.multivariate) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.multivariate, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_50_mar
```{r}
#| label: fig-is.naplots4
##| | echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and univariate missing data for every variable"
#|  - "Density plot of non-missing and multivariate missing data for every variable"#| fig.width: 12
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[4]][[1]] %>% is.na()
missing_data.na <- missing_data.relevant[[4]][[1]] %>% is.na()

data.long <- data.relevant[[4]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.multivariate <- cbind(data.long, missing.long$value)
colnames(combined.multivariate) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.multivariate, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_15_mcar
```{r}
#| label: fig-is.naplots5
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and univariate missing data for every variable"
#|  - "Density plot of non-missing and multivariate missing data for every variable"#| fig.width: 12
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[5]][[1]] %>% is.na()
missing_data.na <- missing_data.relevant[[5]][[1]] %>% is.na()

data.long <- data.relevant[[5]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.multivariate <- cbind(data.long, missing.long$value)
colnames(combined.multivariate) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.multivariate, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_15_mcar
```{r}
#| label: fig-is.naplots6
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and univariate missing data for every variable"
#|  - "Density plot of non-missing and multivariate missing data for every variable"#| fig.width: 12
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[6]][[1]] %>% is.na()
missing_data.na <- missing_data.relevant[[6]][[1]] %>% is.na()

data.long <- data.relevant[[6]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.multivariate <- cbind(data.long, missing.long$value)
colnames(combined.multivariate) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.multivariate, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_50_mcar
```{r}
#| label: fig-is.naplots7
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and univariate missing data for every variable"
#|  - "Density plot of non-missing and multivariate missing data for every variable"#| fig.width: 12
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[7]][[1]] %>% is.na()
missing_data.na <- missing_data.relevant[[7]][[1]] %>% is.na()

data.long <- data.relevant[[7]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.multivariate <- cbind(data.long, missing.long$value)
colnames(combined.multivariate) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.multivariate, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_50_mcar
```{r}
#| label: fig-is.naplots8
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and univariate missing data for every variable"
#|  - "Density plot of non-missing and multivariate missing data for every variable"#| fig.width: 12
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[8]][[1]] %>% is.na()
missing_data.na <- missing_data.relevant[[8]][[1]] %>% is.na()

data.long <- data.relevant[[8]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.multivariate <- cbind(data.long, missing.long$value)
colnames(combined.multivariate) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.multivariate, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```
:::

:::

### Results

#### Groupsizes after listwise deletion
```{r}
#| label: listwise-groups
#| code-fold: true
#| df-print: paged

count <- list()
for (i in seq_len(nrow(combinations))) {
    count[[i]] <- map2(missing[[i]], data[[i]], function(x, y) {
        x %>%
            cbind(group = y$group) %>%
            setNames(c(colnames(x), "group")) %>%
            na.omit() %>%
            group_by(group) %>%
            summarise(n = n())
    }) %>%
        reduce(full_join, by = "group")

    colnames(count[[i]]) <- c("group", paste("n", 1:100, sep = "_"), "NAs")

    count[[i]] <- count[[i]] %>%
        mutate(NAs = rowSums(is.na(count[[i]][, 2:101]))) %>%
        select(group, NAs, everything())
}
```

::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| echo: false
datatable(count[[1]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_15_mar
```{r}
#| echo: false
datatable(count[[2]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 30_50_mar
```{r}
#| echo: false
datatable(count[[3]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_50_mar
```{r}
#| echo: false
datatable(count[[4]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 30_15_mcar
```{r}
#| echo: false
datatable(count[[5]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_15_mcar
```{r}
#| echo: false
datatable(count[[6]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 30_50_mcar
```{r}
#| echo: false
datatable(count[[7]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_50_mcar
```{r}
#| echo: false
datatable(count[[8]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

:::

:::

#### Analysis
```{r}
#| label: listwise-analysis-singular-missing
#| code-fold: true
#| message: false
#| eval: false

############
# Set seed #
############
set.seed(123)
############################
# Plan parallel processing #
############################
cl <- makeForkCluster(5)
#######################
# Multilevel analysis #
#######################
# Define model
lmer.model.ld <- function(x) {
    model <- x %>% lme4::lmer(y ~ x1 + x2 + x3 + x4 + x5 + x6 + x7 + z1 + z2 + x1 * z1 + x2 * z1 + x3 * z2 + (1 + x1 + x2 + x3 | group),
        REML = TRUE,
        control = lmerControl(optimizer = "bobyqa"),
        data = .
    )
    results <- broom.mixed::tidy(model, conf.int = TRUE)

    return(list(results = results, model = model))
}
results_ld <- list()
# Perform analyses
# map(seq_len(nrow(combinations)), ~ {
#     # Extract data
#     # d <- map(missing[[.x]], ~ .x$data)
#     d <- missing[[.x]]
#     other <- map(data[[.x]], \(x) x %>% select(-y, -x1, -x2, -x3, -x4, -x5, -x6, -x7, -z1, -z2) %>% as.data.frame())
#     d <- map2(d, other, ~ cbind(.x, .y))
#     # Perform analyses
#     analyses[[.x]] <- pblapply(d, lmer.model.ld, cl = cl)
# })
for (i in seq_len(nrow(combinations))) {
    # Extract data
    # d <- map(missing[[i]], ~ .x$data)
    d <- missing[[i]]
    other <- map(data[[i]], \(x) x %>%
        select(-y, -x1, -x2, -x3, -x4, -x5, -x6, -x7, -z1, -z2) %>%
        as.data.frame())
    d <- map2(d, other, ~ cbind(.x, .y))
    # Perform analyses
    results_ld[[i]] <- pblapply(d, lmer.model.ld, cl = cl)
}
############################
# Stop parallel processing #
############################
stopCluster(cl)

# Extracting analyses results
analyses <- list()
for(i in seq_len(nrow(combinations))) {
    analyses[[i]] <- map(results_ld[[i]], ~ .x$results)
}
write_rds(analyses, file = paste(path, "data/resultsuni/analyses.rds", sep = ""))
# Extracting models 
models <- list()
for(i in seq_len(nrow(combinations))) {
    models[[i]] <- map(results_ld[[i]], ~ .x$model)
}
write_rds(models, file = paste(path, "data/resultsuni/models.rds", sep = ""))
```

```{r}
#| label: listwise-results-univariate
#| code-fold: true
#| message: false

analyses <- read_rds(paste(path, "data/resultsuni/analyses.rds", sep = ""))
models <- read_rds(paste(path, "data/resultsuni/models.rds", sep = ""))
```

#### Evaluation
```{r}
#| label: evaluation-functions
#| code-fold: true
#| message: false

#####################################
# Creating functions for evaluation #
#####################################
# Bias function
bias <- function(estimated) {
    # Extracting estimates
    estimates <- estimated %>%
        map(function(x) {
            fixed <- x %>%
                filter(term == "(Intercept)" | term == "x1" | term == "x2" | term == "x3" | term == "x4" | term == "x5" | term == "x6" | term == "x7" | term == "z1" | term == "z2" | term == "x1:z1" | term == "x2:z1" | term == "x3:z2") %>%
                pull(estimate, term)
            random <- x %>%
                filter(term == "sd__(Intercept)" | term == "sd__x1" | term == "sd__x2" | term == "sd__x3" | term == "sd__Observation") %>%
                pull(estimate, term) %>%
                sapply(function(x) x^2)
            c(fixed, random)
        })
    # Defining truth
    truth <- tibble(
        beta0j = 10,
        beta1j = .5,
        beta2j = .5,
        beta3j = .5,
        beta4j = .5,
        beta5j = .5,
        beta6j = .5,
        beta7j = .5,
        z1 = .5,
        z2 = .5,
        `x1:z1` = .35,
        `x2:z1` = .35,
        `x3:z2` = .35,
        u0 = 84.74903,
        u1 = 1,
        u2 = 1,
        u3 = 1,
        eij = 25
    )
    # Calculating bias for all datasets
    bias.datasets <- map(estimates, \(x) (x - truth)) %>%
        list_rbind() %>%
        as_tibble()
    # Average bias
    bias <- colMeans(bias.datasets) %>%
        t() %>%
        as_tibble()
    # Mean of estimates
    mean_estimates <- estimates %>%
        do.call(rbind, .) %>%
        colMeans() %>%
        t() %>%
        as_tibble()
    # Calculating MCSE
    mcse <- map(estimates, \(x) (x - mean_estimates)^2) %>%
        list_rbind() %>%
        colSums() %>%
        map_vec(\(x) sqrt(x / (length(estimates) * (length(estimates) - 1)))) %>%
        t() %>%
        as_tibble()
    colnames(mcse) <- colnames(bias)

    return(list(bias.datasets = bias.datasets, bias = bias, bias.mcse = mcse))
}
# Coverage function
coverage <- function(estimated) {
    # Extracting estimates
    estimates <- estimated %>%
        map(~ .x %>%
            filter(term == "(Intercept)" | term == "x1" | term == "x2" | term == "x3" | term == "x4" | term == "x5" | term == "x6" | term == "x7" | term == "z1" | term == "z2" | term == "x1:z1" | term == "x2:z1" | term == "x3:z2") %>%
            select(conf.low, conf.high))
    # Defining truth
    truth <- tibble(
        beta0j = 10,
        beta1j = .5,
        beta2j = .5,
        beta3j = .5,
        beta4j = .5,
        beta5j = .5,
        beta6j = .5,
        beta7j = .5,
        z1 = .5,
        z2 = .5,
        `x1:z1` = .35,
        `x2:z1` = .35,
        `x3:z2` = .35
    ) %>%
        t() %>%
        as_tibble() %>%
        rename(value = V1)
    # Combining estimates and truth
    combined <- map(estimates, \(x) cbind(x, truth))
    # Coverage of all data sets
    coverage.datasets <- map(combined, \(x) x %>%
        mutate(coverage = value > conf.low & value < conf.high) %>%
        select(coverage) %>%
        mutate(coverage = as.numeric(coverage)) %>%
        t() %>%
        as_tibble() %>%
        rename(beta0j = V1, beta1j = V2, beta2j = V3, beta3j = V4, beta4j = V5, beta5j = V6, beta6j = V7, beta7j = V8, z1 = V9, z2 = V10, `x1:z1` = V11, `x2:z1` = V12, `x3:z2` = V13)) %>%
        list_rbind()
    # Average coverage
    coverage <- colMeans(coverage.datasets) %>%
        t() %>%
        as_tibble()
    # Calculating MCSE of coverage
    mcse <- sqrt(coverage * (1 - coverage) / length(estimates)) %>%
        as_tibble()

    return(list(coverage.datasets = coverage.datasets, coverage = coverage, coverage.mcse = mcse))
}
# Confidence interval width function
ciw <- function(estimated) {
    # Extracting estimates
    estimates <- estimated %>%
        map(~ .x %>%
            filter(term == "(Intercept)" | term == "x1" | term == "x2" | term == "x3" | term == "x4" | term == "x5" | term == "x6" | term == "x7" | term == "z1" | term == "z2" | term == "x1:z1" | term == "x2:z1" | term == "x3:z2") %>%
            select(conf.low, conf.high))
    # Calculating CIW for all datasets
    ciw.datasets <- map(estimates, ~ .x %>%
        mutate(ciw = conf.high - conf.low) %>%
        select(ciw) %>%
        t() %>%
        as_tibble() %>%
        rename(beta0j = V1, beta1j = V2, beta2j = V3, beta3j = V4, beta4j = V5, beta5j = V6, beta6j = V7, beta7j = V8, z1 = V9, z2 = V10, `x1:z1` = V11, `x2:z1` = V12, `x3:z2` = V13)) %>%
        list_rbind()
    # Average CIW
    ciw <- colMeans(ciw.datasets) %>%
        t() %>%
        as_tibble()

    return(list(ciw.datasets = ciw.datasets, ciw = ciw))
}
```

##### Bias 
```{r}
#| label: bias-singular-missing
#| code-fold: true
#| message: false

bias.datasets_ld <- list()
for (i in seq_len(nrow(combinations))) {
    # Bias
    bias.datasets_ld[[i]] <- bias(analyses[[i]])
}

format.bias <- function(x, y, method, name = c("Bias", "MCSE")) {
    data <- cbind(x, y) %>%
        pivot_longer(cols = beta0j:eij, names_to = "term", values_to = name) %>%
        mutate(ngroup = as.factor(ngroup), groupsize = as.factor(groupsize), icc = as.factor(icc), mar_mcar = as.factor(mar_mcar), miss = as.factor(miss), g = as.factor(g), method = method)
    colnames(data) <- c("Number of groups", "Group size", "ICC", "Missingness mechanism", "Percentage of missing data", "Gamma", "Term", name, "Method")
    data <- data %>%
        mutate(`Missingness mechanism` = ifelse(`Missingness mechanism` == "mar", "MAR", "MCAR"))
    return(data)
}

bias_ld_univariate <- map(bias.datasets_ld, \(x) x$bias) %>%
    list_rbind() %>%
    as_tibble() %>%
    format.bias(combinations, method = "ld_univariate", name = "Bias") %>%
    cbind(map(bias.datasets_ld, \(x) x$bias.mcse) %>%
        list_rbind() %>%
        as_tibble() %>%
        format.bias(combinations, method = "ld_univariate", name = "MCSE") %>%
        dplyr::select(MCSE))

bias_ld_multivariate <- read_rds(paste(path, "results/evaluations/bias_ld.rds", sep = "")) %>%
    format.bias(., combinations, method = "ld_multivariate", name = "Bias") %>%
    cbind(read_rds(paste(path, "results/evaluations/mcse_bias_ld.rds", sep = "")) %>%
        format.bias(., combinations, method = "ld_multivariate", name = "MCSE") %>%
        dplyr::select(MCSE))

bias_ld <- bind_rows(bias_ld_univariate, bias_ld_multivariate)
```

::: {.column-screen-inset-left} 

```{r}
#| label: fig-bias-singular-missing
#| echo: false
#| message: false
#| fig.cap:
#|  - "Bias of the residual and intercept variance for all datasets"
#|  - "Bias of the overall intercept for all datasets"
#|  - "Bias of the fixed level-1 effects for all datasets"
#|  - "Bias of the fixed level-2 effects for all datasets"
#|  - "Bias of the cross-level interactions for all datasets"
#|  - "Bias of the random slopes for all datasets"
#| fig.width: 14

# Define color palette
cbbPalette <- c("#000000", "#E69F00", "#009E73", "#CC79A7", "#56B4E9", "#D55E00", "#5D478B", "#0072B2", "#F0E442")

bias_ld %>%
    filter(Term == "eij" | Term == "u0") %>%
    ggplot(aes(
        x = Bias,
        y = Term,
        color = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .2)) +
    geom_errorbar(aes(xmin = Bias - MCSE, xmax = Bias + MCSE), position = position_jitter(seed = 123, width = 0, height = .2), width = .25) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    scale_x_continuous(n.breaks = 15, minor_breaks = seq(-11, 11, .5), limits = c(-10, 10)) +
    scale_y_discrete(limits = c("eij", "u0"), labels = c(expression(paste(epsilon, "ij")), expression(paste(upsilon, "0")))) +
    geom_vline(xintercept = 0, color = "gray40") +
    geom_segment(y = 0, yend = 1.5, x = -2.5, linetype = "dashed", color = "gray40") +
    geom_segment(y = 0, yend = 1.5, x = 2.5, linetype = "dashed", color = "gray40") +
    geom_segment(y = 1.5, yend = 3, x = -8.474903, linetype = "dashed", color = "gray40") +
    geom_segment(y = 1.5, yend = 3, x = 8.474903, linetype = "dashed", color = "gray40") +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Absolute bias",
        y = "Term",
        color = "Method"
    )

bias_ld %>%
    filter(Term == "beta0j") %>%
    ggplot(aes(
        x = Bias,
        y = Term,
        color = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .3)) +
    geom_errorbar(aes(xmin = Bias - MCSE, xmax = Bias + MCSE), position = position_jitter(seed = 123, width = 0, height = .3), width = .08) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    scale_x_continuous(n.breaks = 10, minor_breaks = seq(-.4, .4, .025)) +
    scale_y_discrete(limits = c("beta0j"), labels = c(expression(paste(gamma, "00")))) +
    geom_vline(xintercept = 0, color = "gray40") +
    geom_segment(y = 0, yend = 2, x = -.1, linetype = "dashed", color = "gray40") +
    geom_segment(y = 0, yend = 2, x = .1, linetype = "dashed", color = "gray40") +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Absolute bias",
        y = "Term",
        color = "Method"
    )

bias_ld %>%
    filter(Term == "beta1j" | Term == "beta2j" | Term == "beta3j" | Term == "beta4j" | Term == "beta5j" | Term == "beta6j" | Term == "beta7j") %>%
    ggplot(aes(
        x = Bias,
        y = Term,
        color = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .2)) +
    geom_errorbar(aes(xmin = Bias - MCSE, xmax = Bias + MCSE), position = position_jitter(seed = 123, width = 0, height = .2), width = .3) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    scale_x_continuous(n.breaks = 10, minor_breaks = seq(-.08, .08, .005)) +
    scale_y_discrete(limits = c("beta1j", "beta2j", "beta3j", "beta4j", "beta5j", "beta6j", "beta7j"), labels = c(expression(paste(gamma, "10")), expression(paste(gamma, "20")), expression(paste(gamma, "30")), expression(paste(gamma, "40")), expression(paste(gamma, "50")), expression(paste(gamma, "60")), expression(paste(gamma, "70")))) +
    geom_vline(xintercept = 0, color = "gray40") +
    geom_vline(xintercept = -.05, linetype = "dashed", color = "gray40") +
    geom_vline(xintercept = .05, linetype = "dashed", color = "gray40") +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Absolute bias",
        y = "Term",
        color = "Method"
    )

bias_ld %>%
    filter(Term == "z1" | Term == "z2") %>%
    ggplot(aes(
        x = Bias,
        y = Term,
        color = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .2)) +
    geom_errorbar(aes(xmin = Bias - MCSE, xmax = Bias + MCSE), position = position_jitter(seed = 123, width = 0, height = .2), width = .25) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    scale_x_continuous(n.breaks = 10, minor_breaks = seq(-.4, .4, .025)) +
    scale_y_discrete(limits = c("z1", "z2"), labels = c(expression(paste(gamma, "01")), expression(paste(gamma, "02")))) +
    geom_vline(xintercept = 0, color = "gray40") +
    geom_segment(y = 0, yend = 3, x = -.05, linetype = "dashed", color = "gray40") +
    geom_segment(y = 0, yend = 3, x = .05, linetype = "dashed", color = "gray40") +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Absolute bias",
        y = "Term",
        color = "Method"
    )

bias_ld %>%
    filter(Term == "x1:z1" | Term == "x2:z1" | Term == "x3:z2") %>%
    ggplot(aes(
        x = Bias,
        y = Term,
        color = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .1)) +
    geom_errorbar(aes(xmin = Bias - MCSE, xmax = Bias + MCSE), position = position_jitter(seed = 123, width = 0, height = .1), width = .25) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    scale_x_continuous(n.breaks = 10, minor_breaks = seq(-.07, .07, .005)) +
    scale_y_discrete(limits = c("x1:z1", "x2:z1", "x3:z2"), labels = c(expression(paste(gamma, "11")), expression(paste(gamma, "21")), expression(paste(gamma, "32")))) +
    geom_vline(xintercept = 0, color = "gray40") +
    geom_segment(y = 0, yend = 4, x = -.035, linetype = "dashed", color = "gray40") +
    geom_segment(y = 0, yend = 4, x = .035, linetype = "dashed", color = "gray40") +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Absolute bias",
        y = "Term",
        color = "Method"
    )

bias_ld %>%
    filter(Term == "u1" | Term == "u2" | Term == "u3") %>%
    ggplot(aes(
        x = Bias,
        y = Term,
        color = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .1)) +
    geom_errorbar(aes(xmin = Bias - MCSE, xmax = Bias + MCSE), position = position_jitter(seed = 123, width = 0, height = .1), width = .25) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    scale_x_continuous(n.breaks = 10, minor_breaks = seq(-.1, .3, .01)) +
    scale_y_discrete(limits = c("u1", "u2", "u3"), labels = c(expression(paste(upsilon, "1")), expression(paste(upsilon, "2")), expression(paste(upsilon, "3")))) +
    geom_vline(xintercept = 0, color = "gray40") +
    geom_segment(y = 0, yend = 4, x = -.1, linetype = "dashed", color = "gray40") +
    geom_segment(y = 0, yend = 4, x = .1, linetype = "dashed", color = "gray40") +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Absolute bias",
        y = "Term",
        color = "Method"
    )
```

:::

##### Coverage
```{r}
#| label: coverage-singular-missing
#| code-fold: true
#| message: false

coverage.datasets_ld <- list()
for (i in seq_len(nrow(combinations))) {
    # Coverage
    coverage.datasets_ld[[i]] <- coverage(analyses[[i]])
}

format.coverage <- function(x, y, method, name = c("Coverage", "MCSE")) {
    data <- cbind(x, y) %>%
        pivot_longer(cols = beta0j:`x3:z2`, names_to = "term", values_to = name) %>%
        mutate(ngroup = as.factor(ngroup), groupsize = as.factor(groupsize), icc = as.factor(icc), mar_mcar = as.factor(mar_mcar), miss = as.factor(miss), g = as.factor(g), method = method)
    colnames(data) <- c("Number of groups", "Group size", "ICC", "Missingness mechanism", "Percentage of missing data", "Gamma", "Term", name, "Method")
    data <- data %>%
        mutate(`Missingness mechanism` = ifelse(`Missingness mechanism` == "mar", "MAR", "MCAR"))
    return(data)
}

coverage_ld_univariate <- map(coverage.datasets_ld, \(x) x$coverage) %>%
    list_rbind() %>%
    as_tibble() %>%
    format.coverage(combinations, method = "ld_univariate", name = "Coverage") %>%
    cbind(map(coverage.datasets_ld, \(x) x$coverage.mcse) %>%
        list_rbind() %>%
        as_tibble() %>%
        format.coverage(combinations, method = "ld_univariate", name = "MCSE") %>%
        dplyr::select(MCSE))

coverage_ld_multivariate <- read_rds(paste(path, "results/evaluations/coverage_ld.rds", sep = "")) %>%
    format.coverage(., combinations, method = "ld", name = "Coverage") %>%
    cbind(read_rds(paste(path, "results/evaluations/mcse_coverage_ld.rds", sep = "")) %>%
        format.coverage(., combinations, method = "ld", name = "MCSE") %>%
        dplyr::select(MCSE))

coverage_ld <- bind_rows(coverage_ld_univariate, coverage_ld_multivariate)
```

::: {.column-screen-inset-left}

```{r}
#| label: fig-coverage-singular-missing
#| echo: false
#| message: false
#| fig.cap:
#|  - "Coverage of the fixed level-1 effects for all datasets"
#|  - "Coverage of the fixed level-2 effects and cross-level interactions for all datasets"
#| fig.width: 14

coverage_ld %>%
    filter(Term == "beta0j" | Term == "beta1j" | Term == "beta2j" | Term == "beta3j" | Term == "beta4j" | Term == "beta5j" | Term == "beta6j" | Term == "beta7j") %>%
    ggplot(aes(
        x = Coverage,
        y = Term,
        color = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .2)) +
    geom_errorbar(aes(xmin = Coverage - MCSE, xmax = Coverage + MCSE), position = position_jitter(seed = 123, width = 0, height = .2), width = .3) +
    geom_vline(xintercept = .95, color = "gray40") +
    geom_vline(xintercept = .925, linetype = "dashed", color = "gray40") +
    geom_vline(xintercept = .975, linetype = "dashed", color = "gray40") +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    scale_x_continuous(n.breaks = 10, minor_breaks = seq(0, 1, .005)) +
    scale_y_discrete(limits = c("beta0j", "beta1j", "beta2j", "beta3j", "beta4j", "beta5j", "beta6j", "beta7j"), labels = c(expression(paste(gamma, "00")), expression(paste(gamma, "10")), expression(paste(gamma, "20")), expression(paste(gamma, "30")), expression(paste(gamma, "40")), expression(paste(gamma, "50")), expression(paste(gamma, "60")), expression(paste(gamma, "70")))) +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Coverage of 95% confidence intervals",
        y = "Term",
        color = "Method"
    )

coverage_ld %>%
    filter(Term == "z1" | Term == "z2" | Term == "x1:z1" | Term == "x2:z1" | Term == "x3:z2") %>%
    ggplot(aes(
        x = Coverage,
        y = Term,
        color = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .2)) +
    geom_errorbar(aes(xmin = Coverage - MCSE, xmax = Coverage + MCSE), position = position_jitter(seed = 123, width = 0, height = .2), width = .25) +
    geom_vline(xintercept = .95, color = "gray40") +
    geom_vline(xintercept = .925, linetype = "dashed", color = "gray40") +
    geom_vline(xintercept = .975, linetype = "dashed", color = "gray40") +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    scale_x_continuous(n.breaks = 10, minor_breaks = seq(0, 1, .005)) +
    scale_y_discrete(limits = c("z1", "z2", "x1:z1", "x2:z1", "x3:z2"), labels = c(expression(paste(gamma, "01")), expression(paste(gamma, "02")), expression(paste(gamma, "11")), expression(paste(gamma, "21")), expression(paste(gamma, "32")))) +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Coverage of 95% confidence intervals",
        y = "Term",
        color = "Method"
    )
```

:::

##### Confidence interval width
```{r}
#| label: ciw-singular-missing
#| code-fold: true
#| message: false

ciw.datasets_ld <- list()
for (i in seq_len(nrow(combinations))) {
    # CIW
    ciw.datasets_ld[[i]] <- ciw(analyses[[i]])
}

format.ciw <- function(x, y, method, name = "CIW") {
    data <- cbind(x, y) %>%
        pivot_longer(cols = beta0j:`x3:z2`, names_to = "term", values_to = name) %>%
        mutate(ngroup = as.factor(ngroup), groupsize = as.factor(groupsize), icc = as.factor(icc), mar_mcar = as.factor(mar_mcar), miss = as.factor(miss), g = as.factor(g), method = method)
    colnames(data) <- c("Number of groups", "Group size", "ICC", "Missingness mechanism", "Percentage of missing data", "Gamma", "Term", name, "Method")
    data <- data %>%
        mutate(`Missingness mechanism` = ifelse(`Missingness mechanism` == "mar", "MAR", "MCAR"))
    return(data)
}

ciw_ld_univariate <- map(ciw.datasets_ld, \(x) x$ciw) %>%
    list_rbind() %>%
    as_tibble() %>%
    format.ciw(combinations, method = "ld_univariate", name = "CIW")

ciw_ld_multivariate <- read_rds(paste(path, "results/evaluations/ciw_ld.rds", sep = "")) %>%
    format.ciw(., combinations, method = "ld", name = "CIW")

ciw_ld <- bind_rows(ciw_ld_univariate, ciw_ld_multivariate)
```

::: {.column-screen-inset-left} 

```{r}
#| label: fig-ciw-singular-missing
#| echo: false
#| message: false
#| fig.cap:
#|  - "Confidence interval width of the overall intercept for all datasets"
#|  - "Confidence interval width of the fixed level-1 effects for all datasets"
#|  - "Confidence interval width of the fixed level-2 effects for all datasets"
#|  - "Confidence interval width of the cross-level interactions for all datasets"
#| fig.width: 14

ciw_ld %>%
    filter(Term == "beta0j") %>%
    ggplot(aes(
        x = CIW,
        y = Term,
        color = Method
        # fill = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .1)) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    scale_x_continuous(n.breaks = 5, minor_breaks = seq(4, 8, .05)) +
    scale_y_discrete(limits = c("beta0j"), labels = c(expression(paste(gamma, "00")))) +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 0, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Confidence interval width",
        y = "Term",
        color = "Method"
    )

ciw_ld %>%
    filter(Term == "beta1j" | Term == "beta2j" | Term == "beta3j" | Term == "beta4j" | Term == "beta5j" | Term == "beta6j" | Term == "beta7j") %>%
    ggplot(aes(
        x = CIW,
        y = Term,
        color = Method
        # fill = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .1)) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = "label_both") +
    scale_x_continuous(n.breaks = 10) +
    scale_y_discrete(limits = c("beta1j", "beta2j", "beta3j", "beta4j", "beta5j", "beta6j", "beta7j"), labels = c(expression(paste(gamma, "10")), expression(paste(gamma, "20")), expression(paste(gamma, "30")), expression(paste(gamma, "40")), expression(paste(gamma, "50")), expression(paste(gamma, "60")), expression(paste(gamma, "70")))) +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Confidence interval width",
        y = "Term",
        color = "Method"
    )

ciw_ld %>%
    filter(Term == "z1" | Term == "z2") %>%
    ggplot(aes(
        x = CIW,
        y = Term,
        color = Method
        # fill = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .2)) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    scale_x_continuous(n.breaks = 10, minor_breaks = seq(0, 8, .25)) +
    scale_y_discrete(limits = c("z1", "z2"), labels = c(expression(paste(gamma, "01")), expression(paste(gamma, "02")))) +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 0, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Confidence interval width",
        y = "Term",
        color = "Method"
    )

ciw_ld %>%
    filter(Term == "x1:z1" | Term == "x2:z1" | Term == "x3:z2") %>%
    ggplot(aes(
        x = CIW,
        y = Term,
        color = Method
        # fill = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .2)) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    scale_x_continuous(n.breaks = 10) +
    scale_y_discrete(limits = c("x1:z1", "x2:z1", "x3:z2"), labels = c(expression(paste(gamma, "11")), expression(paste(gamma, "21")), expression(paste(gamma, "32")))) +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Confidence interval width",
        y = "Term",
        color = "Method"
    )
```

:::

::: {.column-screen-inset-left} 

#### Singularity
```{r}
#| label: listwise-results
#| code-fold: true
#| message: false

singular <- list()
for (i in seq_len(nrow(combinations))) {
    singular[[i]] <- map_lgl(models[[i]], ~ isSingular(.x)) %>% as.data.frame()
}
singular <- list_cbind(singular)
colnames(singular) <- c("30_15_mar", "50_15_mar", "30_50_mar", "50_50_mar", "30_15_mcar", "50_15_mcar", "30_50_mcar", "50_50_mcar")
```

```{r}
#| label: listwise-table
#| echo: false
#| column: screen-inset-left

datatable(singular,
    rownames = TRUE
) %>%
    formatStyle(
        columns = 1:8,
        backgroundColor = styleEqual(c(FALSE), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 1:8,
        backgroundColor = styleEqual(c(TRUE), c("#FF3030"))
    )

singular %>%
    summarise(across(everything(), ~ sum(.x))) %>%
    t() %>%
    kable(caption = "Amount of singular fits", align = "l")
```

:::

## Creating missingness with logistic regression 

```{r}
#| label: univatiatemissingdatalogit
#| echo: true
#| code-fold: false
#| eval: false


test <- data[[1]][[1]] %>% select(y, x1, x2, x3, x4, x5, x6, x7, z1, z2)
chol(cor(test))

test <- test %>% 
    # mutate(Rhat = .2 * x4 + sqrt(1 - .2^2) * rnorm(nrow(test)))
    mutate(Rhat = chol(cor(test)) %*% rnorm(ncol(test)))
cor(test)


ampute.data.logistic <- function(data, mis.var, cov.var, prop.mis, m.mech = "MARleft") {
    data.rm <- data # assigning data to new object
    n <- nrow(data.rm) # amount of rows in data
    inv.log <- function(x) { # inverse logit function
        exp(x) / (1 + exp(x))
    }
    # m.cov <- mean(data.rm[, cov.var]) # mean of covariate variable

    # if (prop.mis == .1) { # if prop = 10% ...
    #     ML <- (mean(data[, cov.var]) - data[, cov.var]) / sd(data[, cov.var]) - 2.56 # ... then MARleft is calculated as ...
    #     MR <- (-mean(data[, cov.var]) + data[, cov.var]) / sd(data[, cov.var]) - 2.56 # ... MARright is calculated as ...
    #     MM <- (.75 - abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) - 2.25 # ... MARmid is calculated as ...
    #     MT <- (-.75 + abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) - 2.4 # ... MARtail is calculated as ...
    # }
    # if (prop.mis == .25) { # if prop = 25% ...
    #     ML <- (mean(data[, cov.var]) - data[, cov.var]) / sd(data[, cov.var]) - 1.3 # ... then MARleft is calculated as ...
    #     MR <- (-mean(data[, cov.var]) + data[, cov.var]) / sd(data[, cov.var]) - 1.3 # ... MARright is calculated as ...
    #     MM <- (.75 - abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) - 1.15 # ... MARmid is calculated as ...
    #     MT <- (-.75 + abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) - 1.225 # ... MARtail is calculated as ...
    # }
    # if (prop.mis == .5) { # if prop = 50% ...
    #     ML <- (mean(data[, cov.var]) - data[, cov.var]) / sd(data[, cov.var]) # ... then MARleft is calculated as ...
    #     MR <- (-mean(data[, cov.var]) + data[, cov.var]) / sd(data[, cov.var]) # ... MARright is calculated as ...
    #     MM <- (.75 - abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) # ... MARmid is calculated as ...
    #     MT <- (-.75 + abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) # ... MARtail is calculated as ...
    # }


    if (m.mech == "MARleft") { # if missingness mechanism is MARleft ...
        p.MAR <- inv.log(ML) # ... then take inverse logit of ML ...
        data.rm[1 == rbinom(n, 1, p.MAR), mis.var] <- NA # ... and assign NA to the missing variable with a probability of p.MAR
    }

    if (m.mech == "MARright") {
        p.MAR <- inv.log(MR)
        data.rm[1 == rbinom(n, 1, p.MAR), mis.var] <- NA
    }

    if (m.mech == "MARmid") {
        p.MAR <- inv.log(MM)
        data.rm[1 == rbinom(n, 1, p.MAR), mis.var] <- NA
    }

    if (m.mech == "MARtail") {
        p.MAR <- inv.log(MT)
        data.rm[1 == rbinom(n, 1, p.MAR), mis.var] <- NA
    }

    if (m.mech == "MCAR") {
        p.MAR <- rep(prop.mis, nrow(data.rm))
        data.rm[0 == rbinom(n, 1, 1 - prop.mis), mis.var] <- NA
    }

    # Prepare data for return
    true.mis <- mean(is.na(data.rm[, mis.var])) # calculate proportion of missing data
    mis.info <- data.frame(Mechanism = m.mech, Proportion = true.mis) # create data frame with missingness mechanism and proportion of missing data
    output <- list(data.rm, p.MAR, mis.info) # create list with data, p.MAR and mis.info
    names(output) <- c("data", "p.mis", "info") # assign names to list elements
    return(output)
}
```

## Creating missing data in a multivariate way 

### No grouping

### Grouping

## Other articles

### Generating data according to @enders2023

First we need to load the necessary packages. 

```{r}
#| label: load-packages
#| echo: true
#| message: false
library(mlmpower)
library(mvtnorm)
library(varTestnlme)
```

Now we use the `mlmpower` package to solve the MLM parameters given @rights2019 effect sizes. First, we need to define some population parameters, namely the R^2 affect sizes. 

We will adopt Cohen's benchmark for a medium effect size [@cohen1990]. So, f^2 = .3 and R^2 = 0.2307692. Then we can define the within and between variation. R^2_w = 0.1153846 and R^2_b = 0.1153846. The within and between variation are equally distributed, so we can use the same value for both. The variation of the cross-level interactions will be R^2_p = .01 and and the random slope variation will be R^2_rc = .03.

Next, we need to define the weights of the predictors determining their contribution to a particulat source of variance. We will define non-uniform weights for the withing and between predictors. We will define x1, x2, x3, x4, z1, and z2 as focal variables and x5, x6, and x7 as covariates. Then the overall weights will be .80 for the focal variables and .20 for the covariates. We set equal weights for the random slopes and cross-level interactions. 

```{r}
#| label: mlmpower
#| echo: true
#| message: false

ranslope <- (
    effect_size(
        icc          = c(.50),
        within       = 0.2307692,
        between      = 0.2307692,
        product      = .01,
        random_slope = .03
    )
    + outcome("y", mean = 10, sd = 5)
        + within_predictor("x1", weight = .8, icc = 0)
        + within_predictor("x2", weight = .8, icc = 0)
        + within_predictor("x3", weight = .8, icc = 0)
        + within_predictor("x4", weight = .8)
        + within_predictor("x5", weight = .2)
        + within_predictor("x6", weight = .2)
        + within_predictor("x7", weight = .2)
        + between_predictor("z1", weight = .8)
        + between_predictor("z2", weight = .8)
        + random_slope("x1", weight = .5)
        + random_slope("x2", weight = .5)
        + random_slope("x3", weight = .5)
        + product("x1", "z1", weight = .5)
        + product("x2", "z1", weight = .5)
        + product("x3", "z2", weight = .5)
        + correlations(
            within = fixed(.3),
            between = fixed(.3),
            randeff = 0
        )
)
summary(ranslope) %>% lapply(kable)
```

#### Generating data

```{r}
#| label: create-data
#| eval: false
#| echo: true
#| message: false

combinations <- rbind(read_rds(paste(path, "data/nomissing/combinations.rds", sep = "")), combinations)

set.seed(123)
for (i in seq_len(nrow(combinations))) {
    # Generate data
    simdata <- generate(
        ranslope,
        n_within = combinations$groupsize[i],
        n_between = combinations$ngroup[i],
        ndata = 100
    )
    simdata <- map(simdata, \(x) setNames(x, c("group", "y", "x1", "x2", "x3", "x4", "x5", "x6", "x7", "z1", "z2")))

    # Generate names for each dataset
    name <- paste("mlmsimdata",
        colnames(combinations)[1], combinations[i, 1],
        colnames(combinations)[2], combinations[i, 2],
        colnames(combinations)[3], combinations[i, 3],
        colnames(combinations)[4], combinations[i, 4],
        colnames(combinations)[5], combinations[i, 5],
        colnames(combinations)[6], combinations[i, 6],
        sep = "_"
    )

    # Saving data in appropriate data folder
    if (combinations$miss[i] != 0) {
        write_rds(simdata, file = paste(path, "mlmdata/complete/", name, ".rds", sep = ""))
    } else {
        write_rds(simdata, file = paste(path, "mlmdata/nomissing/", name, ".rds", sep = ""))
    }
}
```

#### Creating missingness

##### 50% missingness
```{r}
#| label: create-missing
#| echo: true
#| eval: false
#| message: false

combinations <- combinations %>%
    filter(miss != 0)

# Defining patterns for missing mechanism
patterns <- expand.grid(c(1, 1), c(0, 1), c(0, 1), c(0, 1), c(0, 1), c(0, 1), c(0, 1), c(0, 1), c(0, 1), c(0, 1), c(0, 1)) %>%
    filter(rowSums(.) == 9 | rowSums(.) == 8 | rowSums(.) == 7 | rowSums(.) == 6 | rowSums(.) == 5) %>%
    as.matrix()
colnames(patterns) <- c("group", "y", "x1", "x2", "x3", "x4", "x5", "x6", "x7", "z1", "z2")
patterns <- patterns[sample(nrow(patterns), 10, replace = FALSE), ] # Sample only 10 patterns for all possibilities

# Determining the frequency of each pattern
freq <- ampute.default.freq(patterns)

# Determining the weights of each pattern
weights <- ampute.default.weights(patterns, "MAR")
colnames(weights) <- c("group", "y", "x1", "x2", "x3", "x4", "x5", "x6", "x7", "z1", "z2")
# Increasing weights for z2 and x4
weights[, "z2"] <- weights[, "z2"] * 1.5
weights[, "x4"] <- weights[, "x4"] * 2

# Creating missing data
for (i in seq_len(nrow(combinations))) {
    # Logging iteration
    cat("Processing iteration:", i, "\n")

    if (combinations[i, "mar_mcar"] == "mcar") {
        simdata_miss <-
            read_rds(paste(path, "mlmdata/complete/mlmsimdata_", names[i], ".rds", sep = "")) %>%
            map(
                ~ ampute(
                    data = .x,
                    prop = (combinations[i, "miss"] * .01),
                    mech = "MCAR",
                    patterns = patterns,
                    freq = freq,
                ),
                .progress = TRUE
            )
    } else {
        simdata_miss <-
            read_rds(paste(path, "mlmdata/complete/mlmsimdata_", names[i], ".rds", sep = "")) %>%
            map(
                ~ ampute(
                    data = .x,
                    prop = (combinations[i, "miss"] * .01),
                    mech = "MAR",
                    patterns = patterns,
                    freq = freq,
                    weights = weights
                ),
                .progress = TRUE
            )
    }

    # Saving data in appropriate data folder
    write_rds(simdata_miss, file = paste(path, "mlmdata/missing/miss_", names[i], ".rds", sep = ""))
}
# Also save only imputed datasets
for (i in seq_len(nrow(combinations))) { # For each combination ...
    # Logging iteration
    cat("Processing iteration:", i, "\n")
    # Loading data
    data <- read_rds(paste(path, "mlmdata/missing/miss_", names[i], ".rds", sep = "")) %>%
        map(., \(x) x$amp)

    # Saving amputed data
    write_rds(data, file = paste(path, "mlmdata/missing/simdata_miss_", names[i], ".rds", sep = ""))
}
```

##### 90% missingness
```{r}
#| label: create-missing90
#| echo: true
#| eval: false
#| message: false

combinations <- combinations %>%
    filter(miss != 0)

# Defining patterns for missing mechanism
patterns <- expand.grid(c(1, 1), c(0, 1), c(0, 1), c(0, 1), c(0, 1), c(0, 1), c(0, 1), c(0, 1), c(0, 1), c(0, 1), c(0, 1)) %>%
    filter(rowSums(.) == 9 | rowSums(.) == 8 | rowSums(.) == 7 | rowSums(.) == 6 | rowSums(.) == 5) %>%
    as.matrix()
colnames(patterns) <- c("group", "y", "x1", "x2", "x3", "x4", "x5", "x6", "x7", "z1", "z2")
patterns <- patterns[sample(nrow(patterns), 10, replace = FALSE), ] # Sample only 10 patterns for all possibilities

# Determining the frequency of each pattern
freq <- ampute.default.freq(patterns)

# Determining the weights of each pattern
weights <- ampute.default.weights(patterns, "MAR")
colnames(weights) <- c("group", "y", "x1", "x2", "x3", "x4", "x5", "x6", "x7", "z1", "z2")
# Increasing weights for z2 and x4
weights[, "z2"] <- weights[, "z2"] * 1.5
weights[, "x4"] <- weights[, "x4"] * 2

# Creating missing data
for (i in seq_len(nrow(combinations))) {
    # Logging iteration
    cat("Processing iteration:", i, "\n")

    if (combinations[i, "mar_mcar"] == "mcar") {
        simdata_miss <-
            read_rds(paste(path, "mlmdata/complete/mlmsimdata_", names[i], ".rds", sep = "")) %>%
            map(
                ~ ampute(
                    data = .x,
                    prop = .90,
                    mech = "MCAR",
                    patterns = patterns,
                    freq = freq,
                ),
                .progress = TRUE
            )
    } else {
        simdata_miss <-
            read_rds(paste(path, "mlmdata/complete/mlmsimdata_", names[i], ".rds", sep = "")) %>%
            map(
                ~ ampute(
                    data = .x,
                    prop = .90,
                    mech = "MAR",
                    patterns = patterns,
                    freq = freq,
                    weights = weights
                ),
                .progress = TRUE
            )
    }

    # Saving data in appropriate data folder
    write_rds(simdata_miss, file = paste(path, "mlmdata/missing/miss90_", names[i], ".rds", sep = ""))
}
# Also save only imputed datasets
for (i in seq_len(nrow(combinations))) { # For each combination ...
    # Logging iteration
    cat("Processing iteration:", i, "\n")
    # Loading data
    data <- read_rds(paste(path, "mlmdata/missing/miss90_", names[i], ".rds", sep = "")) %>%
        map(., \(x) x$amp)

    # Saving amputed data
    write_rds(data, file = paste(path, "mlmdata/missing/simdata_miss90_", names[i], ".rds", sep = ""))
}
```

##### missingness in y
```{r}
#| label: create-missingy
#| echo: true
#| eval: false
#| message: false

combinations <- combinations %>%
    filter(miss != 0)

# Creating missing data
for (i in seq_len(nrow(combinations))) {
    # Logging iteration
    cat("Processing iteration:", i, "\n")

    if (combinations[i, "mar_mcar"] == "mcar") {
        simdata_miss <-
            generate(
                ranslope,
                n_within = combinations$groupsize[i],
                n_between = combinations$ngroup[i],
                ndata = 100,
                mechanism = MCAR(.50)
            )
    } else {
        simdata_miss <-
            generate(
                ranslope,
                n_within = combinations$groupsize[i],
                n_between = combinations$ngroup[i],
                ndata = 100,
                mechanism = MAR(.50, cause = "x4", r2 = .80, lower = FALSE)
            )
    }

    simdata_miss <- map(simdata_miss, \(x) setNames(x, c("group", "y", "x1", "x2", "x3", "x4", "x5", "x6", "x7", "z1", "z2")))

    # Saving data in appropriate data folder
    write_rds(simdata_miss, file = paste(path, "mlmdata/missing/missy_", names[i], ".rds", sep = ""))
}
# Also save only imputed datasets
for (i in seq_len(nrow(combinations))) { # For each combination ...
    # Logging iteration
    cat("Processing iteration:", i, "\n")
    # Loading data
    data <- read_rds(paste(path, "mlmdata/missing/missy_", names[i], ".rds", sep = "")) %>%
        map(., \(x) x$amp)

    # Saving amputed data
    write_rds(data, file = paste(path, "mlmdata/missing/simdata_missy_", names[i], ".rds", sep = ""))
}
```

#### Loading data
```{r}
#| label: loadingdatamlm
#| echo: true
#| code-fold: false

missing_data_mlm <- list()
for (i in seq_len(nrow(combinations))) {
    missing_data_mlm[[i]] <- read_rds(paste(path, "mlmdata/missing/simdata_miss_", names[i], ".rds", sep = ""))
}
missing90_data_mlm <- list()
for (i in seq_len(nrow(combinations))) {
    missing90_data_mlm[[i]] <- read_rds(paste(path, "mlmdata/missing/simdata_miss90_", names[i], ".rds", sep = ""))
}
missingy_data_mlm <- list()
for (i in seq_len(nrow(combinations))) {
    missingy_data_mlm[[i]] <- read_rds(paste(path, "mlmdata/missing/simdata_missy_", names[i], ".rds", sep = ""))
}
data_mlm <- list()
for (i in seq_len(nrow(combinations))) {
    data_mlm[[i]] <- read_rds(paste(path, "mlmdata/complete/mlmsimdata_", names[i], ".rds", sep = ""))
}
```

#### Density plots of the complete and incomplete data 
##### 50% missingness
::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| label: fig-inspectmissingdatamlm
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data_mlm[[1]][[1]][, 2:11], missing_data_mlm[[1]][[1]][, 2:11]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "missing mlmpower"), each = ncol(data_mlm[[1]][[1]][, 2:11]), times = nrow(data_mlm[[1]][[1]][, 2:11])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_15_mar
```{r}
#| label: fig-inspectmissingdata2mlm
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data_mlm[[2]][[1]][, 2:11], missing_data_mlm[[2]][[1]][, 2:11]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "missing mlmpower"), each = ncol(data_mlm[[2]][[1]][, 2:11]), times = nrow(data_mlm[[2]][[1]][, 2:11])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_50_mar
```{r}
#| label: fig-inspectmissingdata3mlm
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data_mlm[[3]][[1]][, 2:11], missing_data_mlm[[3]][[1]][, 2:11]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "missing mlmpower"), each = ncol(data_mlm[[3]][[1]][, 2:11]), times = nrow(data_mlm[[3]][[1]][, 2:11])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_50_mar
```{r}
#| label: fig-inspectmissingdata4mlm
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data_mlm[[4]][[1]][, 2:11], missing_data_mlm[[4]][[1]][,2:11]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "missing mlmpower"), each = ncol(data_mlm[[4]][[1]][,2:11]), times = nrow(data_mlm[[4]][[1]][,2:11])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_15_mcar
```{r}
#| label: fig-inspectmissingdata5mlm
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data_mlm[[5]][[1]][,2:11], missing_data_mlm[[5]][[1]][,2:11]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "missing mlmpower"), each = ncol(data_mlm[[5]][[1]][,2:11]), times = nrow(data_mlm[[5]][[1]][,2:11])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_15_mcar
```{r}
#| label: fig-inspectmissingdata6mlm
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data_mlm[[6]][[1]][, 2:11], missing_data_mlm[[6]][[1]][, 2:11]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "missing mlmpower"), each = ncol(data_mlm[[6]][[1]][, 2:11]), times = nrow(data_mlm[[6]][[1]][, 2:11])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_50_mcar
```{r}
#| label: fig-inspectmissingdata7mlm
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data_mlm[[7]][[1]][,2:11], missing_data_mlm[[7]][[1]][,2:11]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "missing mlmpower"), each = ncol(data_mlm[[7]][[1]][,2:11]), times = nrow(data_mlm[[7]][[1]][,2:11])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_50_mcar
```{r}
#| label: fig-inspectmissingdata8mlm
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data_mlm[[8]][[1]][,2:11], missing_data_mlm[[8]][[1]][, 2:11]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "missing mlmpower"), each = ncol(data_mlm[[8]][[1]][,2:11]), times = nrow(data_mlm[[8]][[1]][,2:11])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

:::

:::
##### 90% missingness
::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| label: fig-inspectmissingdatamlm90
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data_mlm[[1]][[1]][, 2:11], missing90_data_mlm[[1]][[1]][, 2:11]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "missing mlmpower"), each = ncol(data_mlm[[1]][[1]][, 2:11]), times = nrow(data_mlm[[1]][[1]][, 2:11])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_15_mar
```{r}
#| label: fig-inspectmissingdata2mlm90
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data_mlm[[2]][[1]][, 2:11], missing90_data_mlm[[2]][[1]][, 2:11]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "missing mlmpower"), each = ncol(data_mlm[[2]][[1]][, 2:11]), times = nrow(data_mlm[[2]][[1]][, 2:11])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_50_mar
```{r}
#| label: fig-inspectmissingdata3mlm90
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data_mlm[[3]][[1]][, 2:11], missing90_data_mlm[[3]][[1]][, 2:11]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "missing mlmpower"), each = ncol(data_mlm[[3]][[1]][, 2:11]), times = nrow(data_mlm[[3]][[1]][, 2:11])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_50_mar
```{r}
#| label: fig-inspectmissingdata4mlm90
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data_mlm[[4]][[1]][, 2:11], missing90_data_mlm[[4]][[1]][,2:11]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "missing mlmpower"), each = ncol(data_mlm[[4]][[1]][,2:11]), times = nrow(data_mlm[[4]][[1]][,2:11])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_15_mcar
```{r}
#| label: fig-inspectmissingdata5mlm90
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data_mlm[[5]][[1]][,2:11], missing90_data_mlm[[5]][[1]][,2:11]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "missing mlmpower"), each = ncol(data_mlm[[5]][[1]][,2:11]), times = nrow(data_mlm[[5]][[1]][,2:11])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_15_mcar
```{r}
#| label: fig-inspectmissingdata6mlm90
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data_mlm[[6]][[1]][, 2:11], missing90_data_mlm[[6]][[1]][, 2:11]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "missing mlmpower"), each = ncol(data_mlm[[6]][[1]][, 2:11]), times = nrow(data_mlm[[6]][[1]][, 2:11])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_50_mcar
```{r}
#| label: fig-inspectmissingdata7mlm90
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data_mlm[[7]][[1]][,2:11], missing90_data_mlm[[7]][[1]][,2:11]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "missing mlmpower"), each = ncol(data_mlm[[7]][[1]][,2:11]), times = nrow(data_mlm[[7]][[1]][,2:11])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_50_mcar
```{r}
#| label: fig-inspectmissingdata8mlm90
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data_mlm[[8]][[1]][,2:11], missing90_data_mlm[[8]][[1]][, 2:11]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "missing mlmpower"), each = ncol(data_mlm[[8]][[1]][,2:11]), times = nrow(data_mlm[[8]][[1]][,2:11])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00", "#9370DB")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

:::

:::

#### Density plots of the non-missing and missing data
##### 50% missingness
::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| label: fig-is.naplotsmlm
#| echo: true
#| code-fold: true
#| fig.cap: 
#|  - "Density plot of non-missing and missing mlmpower data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

missing_data_mlm_na <- missing_data_mlm[[1]][[1]][,2:11] %>% is.na()

data.long <- data_mlm[[1]][[1]][,2:11] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.mlm <- missing_data_mlm_na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined.mlm <- cbind(data.long, missing.mlm$value)
colnames(combined.mlm) <- c("variables", "value", "missing")

ggplot(combined.mlm, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_15_mar
```{r}
#| label: fig-is.naplots2mlm
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing mlmpower data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

missing_data_mlm_na <- missing_data_mlm[[2]][[1]][, 2:11] %>% is.na()

data.long <- data_mlm[[2]][[1]][, 2:11] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

missing.mlm <- missing_data_mlm_na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined.mlm <- cbind(data.long, missing.mlm$value)
colnames(combined.mlm) <- c("variables", "value", "missing")

ggplot(combined.mlm, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_50_mar
```{r}
#| label: fig-is.naplots3mlm
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing mlmpower data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

missing_data_mlm_na <- missing_data_mlm[[3]][[1]][, 2:11] %>% is.na()

data.long <- data_mlm[[3]][[1]][, 2:11] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.mlm <- missing_data_mlm_na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined.mlm <- cbind(data.long, missing.mlm$value)
colnames(combined.mlm) <- c("variables", "value", "missing")

ggplot(combined.mlm, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_50_mar
```{r}
#| label: fig-is.naplots4mlm
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing mlmpower data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

missing_data_mlm_na <- missing_data_mlm[[4]][[1]][, 2:11] %>% is.na()

data.long <- data_mlm[[4]][[1]][, 2:11] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.mlm <- missing_data_mlm_na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined.mlm <- cbind(data.long, missing.mlm$value)
colnames(combined.mlm) <- c("variables", "value", "missing")

ggplot(combined.mlm, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_15_mcar
```{r}
#| label: fig-is.naplots5mlm
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing mlmpower data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

missing_data_mlm_na <- missing_data_mlm[[5]][[1]][, 2:11] %>% is.na()

data.long <- data_mlm[[5]][[1]][, 2:11] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.mlm <- missing_data_mlm_na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined.mlm <- cbind(data.long, missing.mlm$value)
colnames(combined.mlm) <- c("variables", "value", "missing")

ggplot(combined.mlm, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_15_mcar
```{r}
#| label: fig-is.naplots6mlm
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing mlmpower data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

missing_data_mlm_na <- missing_data_mlm[[6]][[1]][, 2:11] %>% is.na()

data.long <- data_mlm[[6]][[1]][, 2:11] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.mlm <- missing_data_mlm_na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined.mlm <- cbind(data.long, missing.mlm$value)
colnames(combined.mlm) <- c("variables", "value", "missing")

ggplot(combined.mlm, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_50_mcar
```{r}
#| label: fig-is.naplots7mlm
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing mlmpower data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

missing_data_mlm_na <- missing_data_mlm[[7]][[1]][,2:11] %>% is.na()

data.long <- missing_data_mlm[[7]][[1]][,2:11] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.mlm <- missing_data_mlm_na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined.mlm <- cbind(data.long, missing.mlm$value)
colnames(combined.mlm) <- c("variables", "value", "missing")

ggplot(combined.mlm, aes(x = value)) +  
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_50_mcar
```{r}
#| label: fig-is.naplots8mlm
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing mlmpower data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

missing_data_mlm_na <- missing_data_mlm[[8]][[1]][, 2:11] %>% is.na()

data.long <- missing_data_mlm[[8]][[1]][, 2:11] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.mlm <- missing_data_mlm_na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined.mlm <- cbind(data.long, missing.mlm$value)
colnames(combined.mlm) <- c("variables", "value", "missing")

ggplot(combined.mlm, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```   
    
:::

:::
##### 90% missingness
::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| label: fig-is.naplotsmlm90
#| echo: true
#| code-fold: true
#| fig.cap: 
#|  - "Density plot of non-missing and missing mlmpower data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

missing_data_mlm_na <- missing90_data_mlm[[1]][[1]][,2:11] %>% is.na()

data.long <- data_mlm[[1]][[1]][,2:11] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.mlm <- missing_data_mlm_na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined.mlm <- cbind(data.long, missing.mlm$value)
colnames(combined.mlm) <- c("variables", "value", "missing")

ggplot(combined.mlm, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_15_mar
```{r}
#| label: fig-is.naplots2mlm90
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing mlmpower data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

missing_data_mlm_na <- missing90_data_mlm[[2]][[1]][, 2:11] %>% is.na()

data.long <- data_mlm[[2]][[1]][, 2:11] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

missing.mlm <- missing_data_mlm_na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined.mlm <- cbind(data.long, missing.mlm$value)
colnames(combined.mlm) <- c("variables", "value", "missing")

ggplot(combined.mlm, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_50_mar
```{r}
#| label: fig-is.naplots3mlm90
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing mlmpower data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

missing_data_mlm_na <- missing90_data_mlm[[3]][[1]][, 2:11] %>% is.na()

data.long <- data_mlm[[3]][[1]][, 2:11] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.mlm <- missing_data_mlm_na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined.mlm <- cbind(data.long, missing.mlm$value)
colnames(combined.mlm) <- c("variables", "value", "missing")

ggplot(combined.mlm, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_50_mar
```{r}
#| label: fig-is.naplots4mlm90
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing mlmpower data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

missing_data_mlm_na <- missing90_data_mlm[[4]][[1]][, 2:11] %>% is.na()

data.long <- data_mlm[[4]][[1]][, 2:11] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.mlm <- missing_data_mlm_na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined.mlm <- cbind(data.long, missing.mlm$value)
colnames(combined.mlm) <- c("variables", "value", "missing")

ggplot(combined.mlm, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_15_mcar
```{r}
#| label: fig-is.naplots5mlm90
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing mlmpower data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

missing_data_mlm_na <- missing90_data_mlm[[5]][[1]][, 2:11] %>% is.na()

data.long <- data_mlm[[5]][[1]][, 2:11] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.mlm <- missing_data_mlm_na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined.mlm <- cbind(data.long, missing.mlm$value)
colnames(combined.mlm) <- c("variables", "value", "missing")

ggplot(combined.mlm, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_15_mcar
```{r}
#| label: fig-is.naplots6mlm90
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing mlmpower data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

missing_data_mlm_na <- missing90_data_mlm[[6]][[1]][, 2:11] %>% is.na()

data.long <- data_mlm[[6]][[1]][, 2:11] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.mlm <- missing_data_mlm_na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined.mlm <- cbind(data.long, missing.mlm$value)
colnames(combined.mlm) <- c("variables", "value", "missing")

ggplot(combined.mlm, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_50_mcar
```{r}
#| label: fig-is.naplots7mlm90
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing mlmpower data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

missing_data_mlm_na <- missing90_data_mlm[[7]][[1]][,2:11] %>% is.na()

data.long <- missing_data_mlm[[7]][[1]][,2:11] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.mlm <- missing_data_mlm_na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined.mlm <- cbind(data.long, missing.mlm$value)
colnames(combined.mlm) <- c("variables", "value", "missing")

ggplot(combined.mlm, aes(x = value)) +  
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_50_mcar
```{r}
#| label: fig-is.naplots8mlm90
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing mlmpower data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

missing_data_mlm_na <- missing90_data_mlm[[8]][[1]][, 2:11] %>% is.na()

data.long <- missing_data_mlm[[8]][[1]][, 2:11] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.mlm <- missing_data_mlm_na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined.mlm <- cbind(data.long, missing.mlm$value)
colnames(combined.mlm) <- c("variables", "value", "missing")

ggplot(combined.mlm, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```   
    
:::

:::

#### Groupsizes after listwise deletion
```{r}
#| label: listwise-groups-mlm
#| code-fold: true
#| df-print: paged

count <- list()
for (i in seq_len(nrow(combinations))) {
    count[[i]] <- map(missing_data_mlm[[i]], function(x) {
        x %>%
            na.omit() %>%
            group_by(group) %>%
            summarise(n = n())
    }) %>%
        reduce(full_join, by = "group")

    colnames(count[[i]]) <- c("group", paste("n", 1:100, sep = "_"), "NAs")

    count[[i]] <- count[[i]] %>%
        mutate(NAs = rowSums(is.na(count[[i]][, 2:101]))) %>%
        select(group, NAs, everything())
}
```

::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| echo: false
datatable(count[[1]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_15_mar
```{r}
#| echo: false
datatable(count[[2]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 30_50_mar
```{r}
#| echo: false
datatable(count[[3]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_50_mar
```{r}
#| echo: false
datatable(count[[4]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 30_15_mcar
```{r}
#| echo: false
datatable(count[[5]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_15_mcar
```{r}
#| echo: false
datatable(count[[6]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 30_50_mcar
```{r}
#| echo: false
datatable(count[[7]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_50_mcar
```{r}
#| echo: false
datatable(count[[8]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

:::

:::

#### Analysis
```{r}
#| label: listwise-analysis-singular-missing-mlm
#| code-fold: true
#| message: false
#| eval: false

############
# Set seed #
############
set.seed(123)
############################
# Plan parallel processing #
############################
cl <- makeForkCluster(5)
#######################
# Multilevel analysis #
#######################
# Define model
lmer.model.ld <- function(x) {
    model <- x %>% lme4::lmer(y ~ x1 + x2 + x3 + x4 + x5 + x6 + x7 + z1 + z2 + x1 * z1 + x2 * z1 + x3 * z2 + (1 + x1 + x2 + x3 | group),
        REML = TRUE,
        control = lmerControl(optimizer = "bobyqa"),
        data = .
    )
    results <- broom.mixed::tidy(model, conf.int = TRUE)

    return(list(results = results, model = model))
}
results_ld <- list()
for (i in seq_len(nrow(combinations))) {
    # Perform analyses
    results_ld[[i]] <- pblapply(missing_data_mlm[[i]], lmer.model.ld, cl = cl)
}
results_ld90 <- list()
for (i in seq_len(nrow(combinations))) {
    # Perform analyses
    results_ld90[[i]] <- pblapply(missing90_data_mlm[[i]], lmer.model.ld, cl = cl)
}
results_ldy <- list()
for (i in seq_len(nrow(combinations))) {
    # Perform analyses
    results_ldy[[i]] <- pblapply(missingy_data_mlm[[i]], lmer.model.ld, cl = cl)
}
############################
# Stop parallel processing #
############################
stopCluster(cl)

# Extracting analyses results
analyses <- list()
for (i in seq_len(nrow(combinations))) {
    analyses[[i]] <- map(results_ld[[i]], ~ .x$results)
}
write_rds(analyses, file = paste(path, "mlmdata/results/analyses.rds", sep = ""))
analyses90 <- list()
for (i in seq_len(nrow(combinations))) {
    analyses90[[i]] <- map(results_ld90[[i]], ~ .x$results)
}
write_rds(analyses90, file = paste(path, "mlmdata/results/analyses90.rds", sep = ""))
# Extracting models
models90 <- list()
for (i in seq_len(nrow(combinations))) {
    models90[[i]] <- map(results_ld90[[i]], ~ .x$model)
}
write_rds(models90, file = paste(path, "mlmdata/results/models90.rds", sep = ""))
```

```{r}
#| label: read-results-mlm
#| code-fold: true
#| message: false

analyses_mlm <- read_rds(paste(path, "mlmdata/results/analyses.rds", sep = ""))
models_mlm <- read_rds(paste(path, "mlmdata/results/models.rds", sep = ""))
# analyses90_mlm <- read_rds(paste(path, "mlmdata/results/analyses90.rds", sep = ""))
# models90_mlm <- read_rds(paste(path, "mlmdata/results/models90.rds", sep = ""))
```

#### Evaluation
```{r}
#| label: evaluation-functions-mlm
#| code-fold: true
#| message: false

#####################################
# Creating functions for evaluation #
#####################################
# Bias function
bias.mlm <- function(estimated) {
    # Extracting estimates
    estimates <- estimated %>%
        map(function(x) {
            fixed <- x %>%
                filter(term == "(Intercept)" | term == "x1" | term == "x2" | term == "x3" | term == "x4" | term == "x5" | term == "x6" | term == "x7" | term == "z1" | term == "z2" | term == "x1:z1" | term == "x2:z1" | term == "x3:z2") %>%
                pull(estimate, term)
            random <- x %>%
                filter(term == "sd__(Intercept)" | term == "sd__x1" | term == "sd__x2" | term == "sd__x3" | term == "sd__Observation") %>%
                pull(estimate, term) %>%
                sapply(function(x) x^2)
            c(fixed, random)
        })
    # Defining truth
    truth <- tibble(
        beta0j = 10,
        beta1j = 0.7712107,
        beta2j = 0.7712107,
        beta3j = 0.7712107,
        beta4j = 1.0906567,
        beta5j = 0.2726642,
        beta6j = 0.2726642,
        beta7j = 0.2726642,
        z1 = 1.7697084,
        z2 = 1.7697084,
        `x1:z1` = 0.2512595,
        `x2:z1` = 0.2512595,
        `x3:z2` = 0.2512595,
        u0 = 0.4501855,
        u1 = .25,
        u2 = .25,
        u3 = .25,
        eij = 5.73077
    )
    # Calculating bias for all datasets
    bias.datasets <- map(estimates, \(x) (x - truth)) %>%
        list_rbind() %>%
        as_tibble()
    # Average bias
    bias <- colMeans(bias.datasets) %>%
        t() %>%
        as_tibble()
    # Mean of estimates
    mean_estimates <- estimates %>%
        do.call(rbind, .) %>%
        colMeans() %>%
        t() %>%
        as_tibble()
    # Calculating MCSE
    mcse <- map(estimates, \(x) (x - mean_estimates)^2) %>%
        list_rbind() %>%
        colSums() %>%
        map_vec(\(x) sqrt(x / (length(estimates) * (length(estimates) - 1)))) %>%
        t() %>%
        as_tibble()
    colnames(mcse) <- colnames(bias)

    return(list(bias.datasets = bias.datasets, bias = bias, bias.mcse = mcse))
}
# Coverage function
coverage.mlm <- function(estimated) {
    # Extracting estimates
    estimates <- estimated %>%
        map(~ .x %>%
            filter(term == "(Intercept)" | term == "x1" | term == "x2" | term == "x3" | term == "x4" | term == "x5" | term == "x6" | term == "x7" | term == "z1" | term == "z2" | term == "x1:z1" | term == "x2:z1" | term == "x3:z2") %>%
            select(conf.low, conf.high))
    # Defining truth
    truth <- tibble(
        beta0j = 10,
        beta1j = 0.7712107,
        beta2j = 0.7712107,
        beta3j = 0.7712107,
        beta4j = 1.0906567,
        beta5j = 0.2726642,
        beta6j = 0.2726642,
        beta7j = 0.2726642,
        z1 = 1.7697084,
        z2 = 1.7697084,
        `x1:z1` = 0.2512595,
        `x2:z1` = 0.2512595,
        `x3:z2` = 0.2512595
    ) %>%
        t() %>%
        as_tibble() %>%
        rename(value = V1)
    # Combining estimates and truth
    combined <- map(estimates, \(x) cbind(x, truth))
    # Coverage of all data sets
    coverage.datasets <- map(combined, \(x) x %>%
        mutate(coverage = value > conf.low & value < conf.high) %>%
        select(coverage) %>%
        mutate(coverage = as.numeric(coverage)) %>%
        t() %>%
        as_tibble() %>%
        rename(beta0j = V1, beta1j = V2, beta2j = V3, beta3j = V4, beta4j = V5, beta5j = V6, beta6j = V7, beta7j = V8, z1 = V9, z2 = V10, `x1:z1` = V11, `x2:z1` = V12, `x3:z2` = V13)) %>%
        list_rbind()
    # Average coverage
    coverage <- colMeans(coverage.datasets) %>%
        t() %>%
        as_tibble()
    # Calculating MCSE of coverage
    mcse <- sqrt(coverage * (1 - coverage) / length(estimates)) %>%
        as_tibble()

    return(list(coverage.datasets = coverage.datasets, coverage = coverage, coverage.mcse = mcse))
}
# Confidence interval width function
ciw.mlm <- function(estimated) {
    # Extracting estimates
    estimates <- estimated %>%
        map(~ .x %>%
            filter(term == "(Intercept)" | term == "x1" | term == "x2" | term == "x3" | term == "x4" | term == "x5" | term == "x6" | term == "x7" | term == "z1" | term == "z2" | term == "x1:z1" | term == "x2:z1" | term == "x3:z2") %>%
            select(conf.low, conf.high))
    # Calculating CIW for all datasets
    ciw.datasets <- map(estimates, ~ .x %>%
        mutate(ciw = conf.high - conf.low) %>%
        select(ciw) %>%
        t() %>%
        as_tibble() %>%
        rename(beta0j = V1, beta1j = V2, beta2j = V3, beta3j = V4, beta4j = V5, beta5j = V6, beta6j = V7, beta7j = V8, z1 = V9, z2 = V10, `x1:z1` = V11, `x2:z1` = V12, `x3:z2` = V13)) %>%
        list_rbind()
    # Average CIW
    ciw <- colMeans(ciw.datasets) %>%
        t() %>%
        as_tibble()

    return(list(ciw.datasets = ciw.datasets, ciw = ciw))
}
```

##### Bias
```{r}
#| label: bias-singular-missing-mlm
#| code-fold: true
#| message: false

bias.datasets_ld_mlm <- list()
for (i in seq_len(nrow(combinations))) {
    # Bias
    bias.datasets_ld_mlm[[i]] <- bias.mlm(analyses_mlm[[i]])
}

format.bias <- function(x, y, method, name = c("Bias", "MCSE")) {
    data <- cbind(x, y) %>%
        pivot_longer(cols = beta0j:eij, names_to = "term", values_to = name) %>%
        mutate(ngroup = as.factor(ngroup), groupsize = as.factor(groupsize), icc = as.factor(icc), mar_mcar = as.factor(mar_mcar), miss = as.factor(miss), g = as.factor(g), method = method)
    colnames(data) <- c("Number of groups", "Group size", "ICC", "Missingness mechanism", "Percentage of missing data", "Gamma", "Term", name, "Method")
    data <- data %>%
        mutate(`Missingness mechanism` = ifelse(`Missingness mechanism` == "mar", "MAR", "MCAR"))
    return(data)
}

bias_ld_univariate <- map(bias.datasets_ld, \(x) x$bias) %>%
    list_rbind() %>%
    as_tibble() %>%
    format.bias(combinations, method = "ld_univariate", name = "Bias") %>%
    cbind(map(bias.datasets_ld, \(x) x$bias.mcse) %>%
        list_rbind() %>%
        as_tibble() %>%
        format.bias(combinations, method = "ld_univariate", name = "MCSE") %>%
        dplyr::select(MCSE))

bias_ld_multivariate <- read_rds(paste(path, "results/evaluations/bias_ld.rds", sep = "")) %>%
    format.bias(., combinations, method = "ld_multivariate", name = "Bias") %>%
    cbind(read_rds(paste(path, "results/evaluations/mcse_bias_ld.rds", sep = "")) %>%
        format.bias(., combinations, method = "ld_multivariate", name = "MCSE") %>%
        dplyr::select(MCSE))

bias_ld_mlm <- map(bias.datasets_ld_mlm, \(x) x$bias) %>%
    list_rbind() %>%
    as_tibble() %>%
    format.bias(combinations, method = "ld_mlm", name = "Bias") %>%
    cbind(map(bias.datasets_ld_mlm, \(x) x$bias.mcse) %>%
        list_rbind() %>%
        as_tibble() %>%
        format.bias(combinations, method = "ld_mlm", name = "MCSE") %>%
        dplyr::select(MCSE))

bias_ld <- bind_rows(bias_ld_univariate, bias_ld_multivariate, bias_ld_mlm)
```

:::{.column-screen-inset-left} 

```{r}
#| label: fig-bias-singular-missing-mlm
#| echo: false
#| message: false
#| fig.cap:
#|  - "Bias of the residual and intercept variance for all datasets"
#|  - "Bias of the overall intercept for all datasets"
#|  - "Bias of the fixed level-1 effects for all datasets"
#|  - "Bias of the fixed level-2 effects for all datasets"
#|  - "Bias of the cross-level interactions for all datasets"
#|  - "Bias of the random slopes for all datasets"
#| fig.width: 14

# Define color palette
cbbPalette <- c("#000000", "#E69F00", "#009E73", "#CC79A7", "#56B4E9", "#D55E00", "#5D478B", "#0072B2", "#F0E442")

bias_ld %>%
    filter(Term == "eij" | Term == "u0") %>%
    filter(Method == "ld_mlm") %>%
    ggplot(aes(
        x = Bias,
        y = Term,
        color = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .2)) +
    geom_errorbar(aes(xmin = Bias - MCSE, xmax = Bias + MCSE), position = position_jitter(seed = 123, width = 0, height = .2), width = .25) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    # scale_x_continuous(n.breaks = 15, minor_breaks = seq(-11, 11, .5), limits = c(-10, 10)) +
    scale_y_discrete(limits = c("eij", "u0"), labels = c(expression(paste(epsilon, "ij")), expression(paste(upsilon, "0")))) +
    geom_vline(xintercept = 0, color = "gray40") +
    geom_segment(y = 0, yend = 1.5, x = -2.5, linetype = "dashed", color = "gray40") +
    geom_segment(y = 0, yend = 1.5, x = 2.5, linetype = "dashed", color = "gray40") +
    geom_segment(y = 1.5, yend = 3, x = -8.474903, linetype = "dashed", color = "gray40") +
    geom_segment(y = 1.5, yend = 3, x = 8.474903, linetype = "dashed", color = "gray40") +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Absolute bias",
        y = "Term",
        color = "Method"
    )

bias_ld %>%
    filter(Term == "beta0j") %>%
    filter(Method == "ld_mlm") %>%
    ggplot(aes(
        x = Bias,
        y = Term,
        color = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .3)) +
    geom_errorbar(aes(xmin = Bias - MCSE, xmax = Bias + MCSE), position = position_jitter(seed = 123, width = 0, height = .3), width = .08) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    # scale_x_continuous(n.breaks = 10, minor_breaks = seq(-.4, .4, .025)) +
    scale_y_discrete(limits = c("beta0j"), labels = c(expression(paste(gamma, "00")))) +
    geom_vline(xintercept = 0, color = "gray40") +
    geom_segment(y = 0, yend = 2, x = -.1, linetype = "dashed", color = "gray40") +
    geom_segment(y = 0, yend = 2, x = .1, linetype = "dashed", color = "gray40") +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Absolute bias",
        y = "Term",
        color = "Method"
    )

bias_ld %>%
    filter(Term == "beta1j" | Term == "beta2j" | Term == "beta3j" | Term == "beta4j" | Term == "beta5j" | Term == "beta6j" | Term == "beta7j") %>%
    filter(Method == "ld_mlm") %>%
    ggplot(aes(
        x = Bias,
        y = Term,
        color = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .2)) +
    geom_errorbar(aes(xmin = Bias - MCSE, xmax = Bias + MCSE), position = position_jitter(seed = 123, width = 0, height = .2), width = .3) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    # scale_x_continuous(n.breaks = 10, minor_breaks = seq(-.08, .08, .005)) +
    scale_y_discrete(limits = c("beta1j", "beta2j", "beta3j", "beta4j", "beta5j", "beta6j", "beta7j"), labels = c(expression(paste(gamma, "10")), expression(paste(gamma, "20")), expression(paste(gamma, "30")), expression(paste(gamma, "40")), expression(paste(gamma, "50")), expression(paste(gamma, "60")), expression(paste(gamma, "70")))) +
    geom_vline(xintercept = 0, color = "gray40") +
    geom_vline(xintercept = -.05, linetype = "dashed", color = "gray40") +
    geom_vline(xintercept = .05, linetype = "dashed", color = "gray40") +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Absolute bias",
        y = "Term",
        color = "Method"
    )

bias_ld %>%
    filter(Term == "z1" | Term == "z2") %>%
    filter(Method == "ld_mlm") %>%
    ggplot(aes(
        x = Bias,
        y = Term,
        color = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .2)) +
    geom_errorbar(aes(xmin = Bias - MCSE, xmax = Bias + MCSE), position = position_jitter(seed = 123, width = 0, height = .2), width = .25) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    # scale_x_continuous(n.breaks = 10, minor_breaks = seq(-.4, .4, .025)) +
    scale_y_discrete(limits = c("z1", "z2"), labels = c(expression(paste(gamma, "01")), expression(paste(gamma, "02")))) +
    geom_vline(xintercept = 0, color = "gray40") +
    geom_segment(y = 0, yend = 3, x = -.05, linetype = "dashed", color = "gray40") +
    geom_segment(y = 0, yend = 3, x = .05, linetype = "dashed", color = "gray40") +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Absolute bias",
        y = "Term",
        color = "Method"
    )

bias_ld %>%
    filter(Term == "x1:z1" | Term == "x2:z1" | Term == "x3:z2") %>%
    filter(Method == "ld_mlm") %>%
    ggplot(aes(
        x = Bias,
        y = Term,
        color = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .1)) +
    geom_errorbar(aes(xmin = Bias - MCSE, xmax = Bias + MCSE), position = position_jitter(seed = 123, width = 0, height = .1), width = .25) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    # scale_x_continuous(n.breaks = 10, minor_breaks = seq(-.07, .07, .005)) +
    scale_y_discrete(limits = c("x1:z1", "x2:z1", "x3:z2"), labels = c(expression(paste(gamma, "11")), expression(paste(gamma, "21")), expression(paste(gamma, "32")))) +
    geom_vline(xintercept = 0, color = "gray40") +
    geom_segment(y = 0, yend = 4, x = -.035, linetype = "dashed", color = "gray40") +
    geom_segment(y = 0, yend = 4, x = .035, linetype = "dashed", color = "gray40") +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Absolute bias",
        y = "Term",
        color = "Method"
    )

bias_ld %>%
    filter(Term == "u1" | Term == "u2" | Term == "u3") %>%
    filter(Method == "ld_mlm") %>%
    ggplot(aes(
        x = Bias,
        y = Term,
        color = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .1)) +
    geom_errorbar(aes(xmin = Bias - MCSE, xmax = Bias + MCSE), position = position_jitter(seed = 123, width = 0, height = .1), width = .25) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    # scale_x_continuous(n.breaks = 10, minor_breaks = seq(-.1, .3, .01)) +
    scale_y_discrete(limits = c("u1", "u2", "u3"), labels = c(expression(paste(upsilon, "1")), expression(paste(upsilon, "2")), expression(paste(upsilon, "3")))) +
    geom_vline(xintercept = 0, color = "gray40") +
    geom_segment(y = 0, yend = 4, x = -.1, linetype = "dashed", color = "gray40") +
    geom_segment(y = 0, yend = 4, x = .1, linetype = "dashed", color = "gray40") +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Absolute bias",
        y = "Term",
        color = "Method"
    )
```

:::

### References

::: {#refs}
:::
