---
title: Multilevel missingess
author: "Heleen Brüggen"
format: 
    html:
        toc: true
        number-sections: true
        toc-location: right
bibliography: references.bib
---

```{r}
#| label: set-up
#| warning: false
#| message: false
#| echo: false

#############
# Libraries #
#############
library(tidyverse)
library(knitr)
library(DT)
library(lme4)
library(mitml)
library(mice)
library(lmerTest)
library(magrittr)
library(purrr)
library(furrr)
library(dplyr)
library(pbapply)
library(parallel)
library(readr)
library(jtools)
library(broom.mixed)
library(ggmice)
library(nlme)
################
# Setting seed #
################
set.seed(123)
################
# Setting path #
################
path <- "/Volumes/Heleen 480GB/MBART-MICE files/"
#######################
# Defining parameters #
#######################
combinations <- read_rds(paste(path, "data/combinations.rds", sep = ""))
#############################
# Storing names of datasets #
#############################
names <- read_rds(paste(path, "data/names.rds", sep = ""))
```

## Creating missing data in a univariate way

### Adding code from Gerko for univariate missing data
The following code is a function to ampute data according the univariate missingness mechanismsL MAR, MCAR or MNAR.
The function has the following arguments: 

- `data`: the data in matrix or data-frame format
- `mis.var`: the column specifier (number) for the variable to be amputed.
- `cov.var`:the column specifier (number) for the covariate the MAR missingness is based on
- `prop.mis`:	proportion of missingness. Options are `c(.25, .5)`.
- `m.mech`:	The missingness mechanism. Options are `c("MARleft", "MARright", "MARmid","MARtail", "MCAR")`.

The output is: 

- `data.rm`: the data with missing values
- `p.MAR`: the probability of missingness
- `mis.info`: a data frame with the missingness mechanism and the proportion of missing data.
```{r}
#| label: univatiatemissingdata
#| echo: true
#| code-fold: false

ampute.data <- function(data, mis.var, cov.var, prop.mis, m.mech = "MARleft") {
    data.rm <- data # assigning data to new object
    n <- nrow(data.rm) # amount of rows in data
    inv.log <- function(x) { # inverse logit function
        exp(x) / (1 + exp(x))
    }
    m.cov <- mean(data.rm[, cov.var]) # mean of covariate variable

    if (prop.mis == .25) { # if prop = 25% ...
        ML <- (mean(data[, cov.var]) - data[, cov.var]) / sd(data[, cov.var]) - 1.3 # ... then MARleft is calculated as ...
        MR <- (-mean(data[, cov.var]) + data[, cov.var]) / sd(data[, cov.var]) - 1.3 # ... MARright is calculated as ...
        MM <- (.75 - abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) - 1.15 # ... MARmid is calculated as ...
        MT <- (-.75 + abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) - 1.225 # ... MARtail is calculated as ...
    }
    if (prop.mis == .5) { # if prop = 50% ...
        ML <- (mean(data[, cov.var]) - data[, cov.var]) / sd(data[, cov.var]) # ... then MARleft is calculated as ...
        MR <- (-mean(data[, cov.var]) + data[, cov.var]) / sd(data[, cov.var]) # ... MARright is calculated as ...
        MM <- (.75 - abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) # ... MARmid is calculated as ...
        MT <- (-.75 + abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) # ... MARtail is calculated as ...
    }


    if (m.mech == "MARleft") { # if missingness mechanism is MARleft ...
        p.MAR <- inv.log(ML) # ... then take inverse logit of ML ...
        data.rm[1 == rbinom(n, 1, p.MAR), mis.var] <- NA # ... and assign NA to the missing variable with a probability of p.MAR
    }

    if (m.mech == "MARright") {
        p.MAR <- inv.log(MR)
        data.rm[1 == rbinom(n, 1, p.MAR), mis.var] <- NA
    }

    if (m.mech == "MARmid") {
        p.MAR <- inv.log(MM)
        data.rm[1 == rbinom(n, 1, p.MAR), mis.var] <- NA
    }

    if (m.mech == "MARtail") {
        p.MAR <- inv.log(MT)
        data.rm[1 == rbinom(n, 1, p.MAR), mis.var] <- NA
    }

    if (m.mech == "MCAR") {
        p.MAR <- rep(prop.mis, nrow(data.rm))
        data.rm[0 == rbinom(n, 1, 1 - prop.mis), mis.var] <- NA
    }

    # Prepare data for return
    true.mis <- mean(is.na(data.rm[, mis.var])) # calculate proportion of missing data
    mis.info <- data.frame(Mechanism = m.mech, Proportion = true.mis) # create data frame with missingness mechanism and proportion of missing data
    output <- list(data.rm, p.MAR, mis.info) # create list with data, p.MAR and mis.info
    names(output) <- c("data", "p.mis", "info") # assign names to list elements
    return(output)
}
```

### Loading data
```{r}
#| label: loadingdata
#| echo: true
#| code-fold: false

data <- list()
for (i in seq_len(nrow(combinations))) {
    data[[i]] <- read_rds(paste(path, "data/complete/simdata_", names[i], ".rds", sep = ""))[1:100]
}

missing_data <- list()
for (i in seq_len(nrow(combinations))) {
    missing_data[[i]] <- read_rds(paste(path, "data/missing/simdata_miss_", names[i], ".rds", sep = ""))[1:100]
}
missing_data.relevant <- map(missing_data, \(x) map(x, \(y) y %>% select(y, x1, x2, x3, x4, x5, x6, x7, z1, z2) %>% as.data.frame()))
```

### Creating missing data

```{r}
#| label: correlations
#| echo: false

cor <- map(seq_len(nrow(combinations)), function(i) {
    cor_dat <- lapply(data[[i]], function(x) cor(x[, c("y", "x1", "x2", "x3", "x4", "x5", "x6", "x7", "z1", "z2")])) %>%
        Reduce("+", .) / length(data[[i]])
})
```

::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| label: tbl-cor30_15_mar
#| echo: false

datatable(
    cor[[1]],
    caption = paste("Correlation of", names[1]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 50_15_mar
```{r}
#| label: tbl-cor50_15_mar
#| echo: false

datatable(
    cor[[2]],
    caption = paste("Correlation of", names[2]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 30_50_mar
```{r}
#| label: tbl-cor30_50_mar
#| echo: false

datatable(
    cor[[3]],
    caption = paste("Correlation of", names[3]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 50_50_mar 
```{r}
#| label: tbl-cor50_50_mar
#| echo: false

datatable(
    cor[[4]],
    caption = paste("Correlation of", names[4]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 30_15_mcar
```{r}
#| label: tbl-cor30_15_mcar
#| echo: false

datatable(
    cor[[5]],
    caption = paste("Correlation of", names[5]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 50_15_mcar
```{r}
#| label: tbl-cor50_15_mcar
#| echo: false

datatable(
    cor[[6]],
    caption = paste("Correlation of", names[6]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 30_50_mcar
```{r}
#| label: tbl-cor30_50_mcar
#| echo: false

datatable(
    cor[[7]],
    caption = paste("Correlation of", names[7]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 50_50_mcar
```{r}
#| label: tbl-cor50_50_mcar
#| echo: false

datatable(
    cor[[8]],
    caption = paste("Correlation of", names[8]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

:::

:::

Next, we will ampute the data according to a univariate MAR right mechanism -- x1, x2, x3, x5, x6, and x7 will be made incomplete based in x4, z1 will be made incomplete based on z2, and x1 and z2 will be made incomplete based on y. The proportion of missing data is set to 50%. 
```{r}
#| label: singularmissingdata
#| echo: true
#| code-fold: true

missing <- list()
data.relevant <- list()
for (i in seq_len(nrow(combinations))) {
    data.relevant[[i]] <- map(data[[i]], \(x) x %>%
        select(y, x1, x2, x3, x4, x5, x6, x7, z1, z2) %>%
        as.data.frame())

    if (combinations[i, 4] == "mar") {
        m.mech <- "MARright"
    } else {
        m.mech <- "MCAR"
    }

    missing[[i]] <- map(data.relevant[[i]], \(x) ampute.data(x, mis.var = 2, cov.var = 5, prop.mis = .25, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 3, cov.var = 5, prop.mis = .25, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 4, cov.var = 5, prop.mis = .25, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 6, cov.var = 5, prop.mis = .25, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 7, cov.var = 5, prop.mis = .25, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 8, cov.var = 5, prop.mis = .25, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 9, cov.var = 10, prop.mis = .25, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 5, cov.var = 1, prop.mis = .25, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 10, cov.var = 1, prop.mis = .25, m.mech = m.mech))
}
```

### Inspecting the missingess in the data
Let's inspect the first data set with missing data.

#### Density plots of the complete and incomplete data 

::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| label: fig-inspectmissingdata
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[1]][[1]], missing[[1]][[1]]$data, missing_data.relevant[[1]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "incomplete", "original incomplete"), each = ncol(data.relevant[[1]][[1]]), times = nrow(data.relevant[[1]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_15_mar
```{r}
#| label: fig-inspectmissingdata2
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[2]][[1]], missing[[2]][[1]]$data, missing_data.relevant[[2]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "incomplete", "original incomplete"), each = ncol(data.relevant[[2]][[1]]), times = nrow(data.relevant[[2]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_50_mar
```{r}
#| label: fig-inspectmissingdata3
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[3]][[1]], missing[[3]][[1]]$data, missing_data.relevant[[3]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "incomplete", "original incomplete"), each = ncol(data.relevant[[3]][[1]]), times = nrow(data.relevant[[3]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_50_mar
```{r}
#| label: fig-inspectmissingdata4
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[4]][[1]], missing[[4]][[1]]$data, missing_data.relevant[[4]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "incomplete", "original incomplete"), each = ncol(data.relevant[[4]][[1]]), times = nrow(data.relevant[[4]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_15_mcar
```{r}
#| label: fig-inspectmissingdata5
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[5]][[1]], missing[[5]][[1]]$data, missing_data.relevant[[5]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "incomplete", "original incomplete"), each = ncol(data.relevant[[5]][[1]]), times = nrow(data.relevant[[5]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_15_mcar
```{r}
#| label: fig-inspectmissingdata6
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[6]][[1]], missing[[6]][[1]]$data, missing_data.relevant[[6]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "incomplete", "original incomplete"), each = ncol(data.relevant[[6]][[1]]), times = nrow(data.relevant[[6]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_50_mar
```{r}
#| label: fig-inspectmissingdata7
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[7]][[1]], missing[[7]][[1]]$data, missing_data.relevant[[7]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "incomplete", "original incomplete"), each = ncol(data.relevant[[7]][[1]]), times = nrow(data.relevant[[7]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_50_mar
```{r}
#| label: fig-inspectmissingdata8
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[8]][[1]], missing[[8]][[1]]$data, missing_data.relevant[[8]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "incomplete", "original incomplete"), each = ncol(data.relevant[[8]][[1]]), times = nrow(data.relevant[[8]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

:::

:::

#### Density plots of the non-missing and missing data

::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| label: fig-is.naplots
#| echo: true
#| code-fold: true
#| fig.cap: 
#|  - "Density plot of non-missing and missing data for every variable"
#|  - "Density plot of non-missing and original missing data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[1]][[1]]$data %>% is.na()
missing_data.na <- missing_data.relevant[[1]][[1]] %>% is.na()

data.long <- data.relevant[[1]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.original <- cbind(data.long, missing.long$value)
colnames(combined.original) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.original, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_15_mar
```{r}
#| label: fig-is.naplots2
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing data for every variable"
#|  - "Density plot of non-missing and original missing data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[2]][[1]]$data %>% is.na()
missing_data.na <- missing_data.relevant[[2]][[1]] %>% is.na()

data.long <- data.relevant[[2]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.original <- cbind(data.long, missing.long$value)
colnames(combined.original) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.original, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_50_mar
```{r}
#| label: fig-is.naplots3
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing data for every variable"
#|  - "Density plot of non-missing and original missing data for every variable"#| fig.width: 12
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[3]][[1]]$data %>% is.na()
missing_data.na <- missing_data.relevant[[3]][[1]] %>% is.na()

data.long <- data.relevant[[3]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.original <- cbind(data.long, missing.long$value)
colnames(combined.original) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.original, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_50_mar
```{r}
#| label: fig-is.naplots4
##| | echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing data for every variable"
#|  - "Density plot of non-missing and original missing data for every variable"#| fig.width: 12
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[4]][[1]]$data %>% is.na()
missing_data.na <- missing_data.relevant[[4]][[1]] %>% is.na()

data.long <- data.relevant[[4]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.original <- cbind(data.long, missing.long$value)
colnames(combined.original) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.original, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_15_mcar
```{r}
#| label: fig-is.naplots5
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing data for every variable"
#|  - "Density plot of non-missing and original missing data for every variable"#| fig.width: 12
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[5]][[1]]$data %>% is.na()
missing_data.na <- missing_data.relevant[[5]][[1]] %>% is.na()

data.long <- data.relevant[[5]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.original <- cbind(data.long, missing.long$value)
colnames(combined.original) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.original, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_15_mcar
```{r}
#| label: fig-is.naplots6
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing data for every variable"
#|  - "Density plot of non-missing and original missing data for every variable"#| fig.width: 12
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[6]][[1]]$data %>% is.na()
missing_data.na <- missing_data.relevant[[6]][[1]] %>% is.na()

data.long <- data.relevant[[6]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.original <- cbind(data.long, missing.long$value)
colnames(combined.original) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.original, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_50_mcar
```{r}
#| label: fig-is.naplots7
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing data for every variable"
#|  - "Density plot of non-missing and original missing data for every variable"#| fig.width: 12
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[7]][[1]]$data %>% is.na()
missing_data.na <- missing_data.relevant[[7]][[1]] %>% is.na()

data.long <- data.relevant[[7]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.original <- cbind(data.long, missing.long$value)
colnames(combined.original) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.original, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_50_mcar
```{r}
#| label: fig-is.naplots8
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and missing data for every variable"
#|  - "Density plot of non-missing and original missing data for every variable"#| fig.width: 12
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[8]][[1]]$data %>% is.na()
missing_data.na <- missing_data.relevant[[8]][[1]] %>% is.na()

data.long <- data.relevant[[8]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.original <- cbind(data.long, missing.long$value)
colnames(combined.original) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.original, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```
:::

:::

### Results

#### Groupsizes after listwise deletion
```{r}
#| label: listwise-groups
#| code-fold: true
#| df-print: paged

count <- list()
for (i in seq_len(nrow(combinations))) {
    count[[i]] <- map2(missing[[i]], data[[i]], function(x, y) {
        x$data %>%
            cbind(group = y$group) %>%
            setNames(c(colnames(x$data), "group")) %>%
            na.omit() %>%
            group_by(group) %>%
            summarise(n = n())
    }) %>%
        reduce(full_join, by = "group")

    colnames(count[[i]]) <- c("group", paste("n", 1:100, sep = "_"), "NAs")

    count[[i]] <- count[[i]] %>%
        mutate(NAs = rowSums(is.na(count[[i]][, 2:101]))) %>%
        select(group, NAs, everything())
}
```

::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| echo: false
datatable(count[[1]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_15_mar
```{r}
#| echo: false
datatable(count[[2]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 30_50_mar
```{r}
#| echo: false
datatable(count[[3]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_50_mar
```{r}
#| echo: false
datatable(count[[4]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 30_15_mcar
```{r}
#| echo: false
datatable(count[[5]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_15_mcar
```{r}
#| echo: false
datatable(count[[6]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 30_50_mcar
```{r}
#| echo: false
datatable(count[[7]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_50_mcar
```{r}
#| echo: false
datatable(count[[8]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

:::

:::

#### Analysis
```{r}
#| label: listwise-analysis-singular-missing
#| code-fold: true
#| message: false
#| eval: false

############
# Set seed #
############
set.seed(123)
############################
# Plan parallel processing #
############################
cl <- makeForkCluster(5)
#######################
# Multilevel analysis #
#######################
# Define model
lmer.model.ld <- function(x) {
    model <- x %>% lme4::lmer(y ~ x1 + x2 + x3 + x4 + x5 + x6 + x7 + z1 + z2 + x1 * z1 + x2 * z1 + x3 * z2 + (1 + x1 + x2 + x3 | group),
        REML = TRUE,
        control = lmerControl(optimizer = "bobyqa"),
        data = .
    )
    results <- broom.mixed::tidy(model, conf.int = TRUE)

    return(results)
}
analyses <- list()
# Perform analyses
map(seq_len(nrow(combinations)), ~ {
    # Extract data 
    d <- map(missing[[.x]], ~ .x$data)
    other <- map(data[[.x]], \(x) x %>% select(-y, -x1, -x2, -x3, -x4, -x5, -x6, -x7, -z1, -z2) %>% as.data.frame())
    d <- map2(d, other, ~ cbind(.x, .y))
    # Perform analyses
    analyses[[.x]] <- pblapply(d, lmer.model.ld, cl = cl)
})
############################
# Stop parallel processing #
############################
stopCluster(cl)
```

#### Bias

## Creating missing data in a multivariate way

### No grouping 

### Grouping

## Other articles
