---
title: Multilevel missingess
author: "Heleen Brüggen"
format: 
    html:
        toc: true
        number-sections: true
        toc-location: right
bibliography: references.bib
---

```{r}
#| label: set-up
#| warning: false
#| message: false
#| echo: false

#############
# Libraries #
#############
library(tidyverse)
library(knitr)
library(DT)
library(lme4)
library(mitml)
library(mice)
library(lmerTest)
library(magrittr)
library(purrr)
library(furrr)
library(dplyr)
library(pbapply)
library(parallel)
library(readr)
library(jtools)
library(broom.mixed)
library(ggmice)
library(nlme)
library(ggplot2)
################
# Setting seed #
################
set.seed(123)
################
# Setting path #
################
path <- "/Volumes/Heleen 480GB/MBART-MICE files/"
#######################
# Defining parameters #
#######################
combinations <- read_rds(paste(path, "data/combinations.rds", sep = ""))
#############################
# Storing names of datasets #
#############################
names <- read_rds(paste(path, "data/names.rds", sep = ""))
```

## Creating missing data in a univariate way

### Adding code from Gerko for univariate missing data
The following code is a function to ampute data according the univariate missingness mechanismsL MAR, MCAR or MNAR.
The function has the following arguments: 

- `data`: the data in matrix or data-frame format
- `mis.var`: the column specifier (number) for the variable to be amputed.
- `cov.var`:the column specifier (number) for the covariate the MAR missingness is based on
- `prop.mis`:	proportion of missingness. Options are `c(.25, .5)`.
- `m.mech`:	The missingness mechanism. Options are `c("MARleft", "MARright", "MARmid","MARtail", "MCAR")`.

The output is: 

- `data.rm`: the data with missing values
- `p.MAR`: the probability of missingness
- `mis.info`: a data frame with the missingness mechanism and the proportion of missing data.
```{r}
#| label: univatiatemissingdata
#| echo: true
#| code-fold: false

ampute.data <- function(data, mis.var, cov.var, prop.mis, m.mech = "MARleft") {
    data.rm <- data # assigning data to new object
    n <- nrow(data.rm) # amount of rows in data
    inv.log <- function(x) { # inverse logit function
        exp(x) / (1 + exp(x))
    }
    m.cov <- mean(data.rm[, cov.var]) # mean of covariate variable

    if (prop.mis == .1) { # if prop = 10% ...
        ML <- (mean(data[, cov.var]) - data[, cov.var]) / sd(data[, cov.var]) - 2.56 # ... then MARleft is calculated as ...
        MR <- (-mean(data[, cov.var]) + data[, cov.var]) / sd(data[, cov.var]) - 2.56 # ... MARright is calculated as ...
        MM <- (.75 - abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) - 2.25 # ... MARmid is calculated as ...
        MT <- (-.75 + abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) - 2.4 # ... MARtail is calculated as ...
    }
    if (prop.mis == .25) { # if prop = 25% ...
        ML <- (mean(data[, cov.var]) - data[, cov.var]) / sd(data[, cov.var]) - 1.3 # ... then MARleft is calculated as ...
        MR <- (-mean(data[, cov.var]) + data[, cov.var]) / sd(data[, cov.var]) - 1.3 # ... MARright is calculated as ...
        MM <- (.75 - abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) - 1.15 # ... MARmid is calculated as ...
        MT <- (-.75 + abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) - 1.225 # ... MARtail is calculated as ...
    }
    if (prop.mis == .5) { # if prop = 50% ...
        ML <- (mean(data[, cov.var]) - data[, cov.var]) / sd(data[, cov.var]) # ... then MARleft is calculated as ...
        MR <- (-mean(data[, cov.var]) + data[, cov.var]) / sd(data[, cov.var]) # ... MARright is calculated as ...
        MM <- (.75 - abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) # ... MARmid is calculated as ...
        MT <- (-.75 + abs((data[, cov.var] - mean(data[, cov.var])) / sd(data[, cov.var]))) # ... MARtail is calculated as ...
    }


    if (m.mech == "MARleft") { # if missingness mechanism is MARleft ...
        p.MAR <- inv.log(ML) # ... then take inverse logit of ML ...
        data.rm[1 == rbinom(n, 1, p.MAR), mis.var] <- NA # ... and assign NA to the missing variable with a probability of p.MAR
    }

    if (m.mech == "MARright") {
        p.MAR <- inv.log(MR)
        data.rm[1 == rbinom(n, 1, p.MAR), mis.var] <- NA
    }

    if (m.mech == "MARmid") {
        p.MAR <- inv.log(MM)
        data.rm[1 == rbinom(n, 1, p.MAR), mis.var] <- NA
    }

    if (m.mech == "MARtail") {
        p.MAR <- inv.log(MT)
        data.rm[1 == rbinom(n, 1, p.MAR), mis.var] <- NA
    }

    if (m.mech == "MCAR") {
        p.MAR <- rep(prop.mis, nrow(data.rm))
        data.rm[0 == rbinom(n, 1, 1 - prop.mis), mis.var] <- NA
    }

    # Prepare data for return
    true.mis <- mean(is.na(data.rm[, mis.var])) # calculate proportion of missing data
    mis.info <- data.frame(Mechanism = m.mech, Proportion = true.mis) # create data frame with missingness mechanism and proportion of missing data
    output <- list(data.rm, p.MAR, mis.info) # create list with data, p.MAR and mis.info
    names(output) <- c("data", "p.mis", "info") # assign names to list elements
    return(output)
}
```

### Loading data
```{r}
#| label: loadingdata
#| echo: true
#| code-fold: false

data <- list()
for (i in seq_len(nrow(combinations))) {
    data[[i]] <- read_rds(paste(path, "data/complete/simdata_", names[i], ".rds", sep = ""))[1:100]
}

missing_data <- list()
for (i in seq_len(nrow(combinations))) {
    missing_data[[i]] <- read_rds(paste(path, "data/missing/simdata_miss_", names[i], ".rds", sep = ""))[1:100]
}
missing_data.relevant <- map(missing_data, \(x) map(x, \(y) y %>% select(y, x1, x2, x3, x4, x5, x6, x7, z1, z2) %>% as.data.frame()))
```

### Creating missing data

```{r}
#| label: correlations
#| echo: false

cor <- map(seq_len(nrow(combinations)), function(i) {
    cor_dat <- lapply(data[[i]], function(x) cor(x[, c("y", "x1", "x2", "x3", "x4", "x5", "x6", "x7", "z1", "z2")])) %>%
        Reduce("+", .) / length(data[[i]])
})
```

::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| label: tbl-cor30_15_mar
#| echo: false

datatable(
    cor[[1]],
    caption = paste("Correlation of", names[1]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 50_15_mar
```{r}
#| label: tbl-cor50_15_mar
#| echo: false

datatable(
    cor[[2]],
    caption = paste("Correlation of", names[2]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 30_50_mar
```{r}
#| label: tbl-cor30_50_mar
#| echo: false

datatable(
    cor[[3]],
    caption = paste("Correlation of", names[3]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 50_50_mar 
```{r}
#| label: tbl-cor50_50_mar
#| echo: false

datatable(
    cor[[4]],
    caption = paste("Correlation of", names[4]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 30_15_mcar
```{r}
#| label: tbl-cor30_15_mcar
#| echo: false

datatable(
    cor[[5]],
    caption = paste("Correlation of", names[5]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 50_15_mcar
```{r}
#| label: tbl-cor50_15_mcar
#| echo: false

datatable(
    cor[[6]],
    caption = paste("Correlation of", names[6]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 30_50_mcar
```{r}
#| label: tbl-cor30_50_mcar
#| echo: false

datatable(
    cor[[7]],
    caption = paste("Correlation of", names[7]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

## 50_50_mcar
```{r}
#| label: tbl-cor50_50_mcar
#| echo: false

datatable(
    cor[[8]],
    caption = paste("Correlation of", names[8]),
    options = list(pageLength = 10)
) %>%
    formatRound(columns = 1:10, digits = 3)
```

:::

:::

Next, we will ampute the data according to a univariate MAR right mechanism -- x1, x2, x3, x5, x6, x7, z1, z2, and y will be made incomplete based in x4. The proportion of missing data is set to 10% to try to mimic the missing data patterns in the multivariate missing data.
```{r}
#| label: singularmissingdata
#| echo: true
#| code-fold: true

missing <- list()
data.relevant <- list()
shadow.data <- list()
for (i in seq_len(nrow(combinations))) {
    data.relevant[[i]] <- map(data[[i]], \(x) x %>%
        select(y, x1, x2, x3, x4, x5, x6, x7, z1, z2) %>%
        as.data.frame())

    shadow.data[[i]] <- map(data.relevant[[i]], \(x) cbind(x, x %>% select(x4, z2)))

    if (combinations[i, 4] == "mar") {
        m.mech <- "MARright"
    } else {
        m.mech <- "MCAR"
    }

    missing[[i]] <- map(shadow.data[[i]], \(x) ampute.data(x, mis.var = 1, cov.var = 11, prop.mis = .1, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 2, cov.var = 11, prop.mis = .1, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 3, cov.var = 11, prop.mis = .1, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 4, cov.var = 11, prop.mis = .1, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 5, cov.var = 11, prop.mis = .1, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 6, cov.var = 11, prop.mis = .1, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 7, cov.var = 11, prop.mis = .1, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 8, cov.var = 11, prop.mis = .1, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 9, cov.var = 11, prop.mis = .1, m.mech = m.mech)) %>%
        map(., \(x) ampute.data(x$data, mis.var = 10, cov.var = 11, prop.mis = .1, m.mech = m.mech)) %>%
        map(., \(x) x$data[, 1:10] %>% as.data.frame())
}

missing_data.relevant[[1]][[1]] %>% ggmice::plot_pattern()
missing[[1]][[1]] %>% ggmice::plot_pattern()
```

### Inspecting the missingess in the data
Let's inspect the first data set with missing data.

#### Density plots of the complete and incomplete data 

::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| label: fig-inspectmissingdata
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[1]][[1]], missing[[1]][[1]], missing_data.relevant[[1]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "univariate incomplete", "multivariate incomplete"), each = ncol(data.relevant[[1]][[1]]), times = nrow(data.relevant[[1]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_15_mar
```{r}
#| label: fig-inspectmissingdata2
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[2]][[1]], missing[[2]][[1]], missing_data.relevant[[2]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "univariate incomplete", "multivariate incomplete"), each = ncol(data.relevant[[2]][[1]]), times = nrow(data.relevant[[2]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_50_mar
```{r}
#| label: fig-inspectmissingdata3
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[3]][[1]], missing[[3]][[1]], missing_data.relevant[[3]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "univariate incomplete", "multivariate incomplete"), each = ncol(data.relevant[[3]][[1]]), times = nrow(data.relevant[[3]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_50_mar
```{r}
#| label: fig-inspectmissingdata4
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[4]][[1]], missing[[4]][[1]], missing_data.relevant[[4]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "univariate incomplete", "multivariate incomplete"), each = ncol(data.relevant[[4]][[1]]), times = nrow(data.relevant[[4]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_15_mcar
```{r}
#| label: fig-inspectmissingdata5
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[5]][[1]], missing[[5]][[1]], missing_data.relevant[[5]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "univariate incomplete", "multivariate incomplete"), each = ncol(data.relevant[[5]][[1]]), times = nrow(data.relevant[[5]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_15_mcar
```{r}
#| label: fig-inspectmissingdata6
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[6]][[1]], missing[[6]][[1]], missing_data.relevant[[6]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "univariate incomplete", "multivariate incomplete"), each = ncol(data.relevant[[6]][[1]]), times = nrow(data.relevant[[6]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_50_mar
```{r}
#| label: fig-inspectmissingdata7
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[7]][[1]], missing[[7]][[1]], missing_data.relevant[[7]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "univariate incomplete", "multivariate incomplete"), each = ncol(data.relevant[[7]][[1]]), times = nrow(data.relevant[[7]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_50_mar
```{r}
#| label: fig-inspectmissingdata8
#| echo: true
#| code-fold: true
#| fig.cap: "Density plot of complete and incomplete data for every variable"
#| fig.width: 12
#| fig.height: 6
#| warning: false

dat <- cbind(data.relevant[[8]][[1]], missing[[8]][[1]], missing_data.relevant[[8]][[1]]) %>%
    pivot_longer(cols = everything(), names_to = "data", values_to = "value") %>%
    mutate(missing = rep(c("complete", "univariate incomplete", "multivariate incomplete"), each = ncol(data.relevant[[8]][[1]]), times = nrow(data.relevant[[8]][[1]])))

ggplot(dat, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.1) +
    facet_wrap(~data, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C", "#7FFF00")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

:::

:::

#### Density plots of the non-missing and missing data

::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| label: fig-is.naplots
#| echo: true
#| code-fold: true
#| fig.cap: 
#|  - "Density plot of non-missing and univariate missing data for every variable"
#|  - "Density plot of non-missing and multivariate missing data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[1]][[1]] %>% is.na()
missing_data.na <- missing_data.relevant[[1]][[1]] %>% is.na()

data.long <- data.relevant[[1]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.multivariate <- cbind(data.long, missing.long$value)
colnames(combined.multivariate) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.multivariate, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_15_mar
```{r}
#| label: fig-is.naplots2
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and univariate missing data for every variable"
#|  - "Density plot of non-missing and multivariate missing data for every variable"
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[2]][[1]] %>% is.na()
missing_data.na <- missing_data.relevant[[2]][[1]] %>% is.na()

data.long <- data.relevant[[2]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.multivariate <- cbind(data.long, missing.long$value)
colnames(combined.multivariate) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.multivariate, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_50_mar
```{r}
#| label: fig-is.naplots3
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and univariate missing data for every variable"
#|  - "Density plot of non-missing and multivariate missing data for every variable"#| fig.width: 12
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[3]][[1]] %>% is.na()
missing_data.na <- missing_data.relevant[[3]][[1]] %>% is.na()

data.long <- data.relevant[[3]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.multivariate <- cbind(data.long, missing.long$value)
colnames(combined.multivariate) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.multivariate, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_50_mar
```{r}
#| label: fig-is.naplots4
##| | echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and univariate missing data for every variable"
#|  - "Density plot of non-missing and multivariate missing data for every variable"#| fig.width: 12
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[4]][[1]] %>% is.na()
missing_data.na <- missing_data.relevant[[4]][[1]] %>% is.na()

data.long <- data.relevant[[4]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.multivariate <- cbind(data.long, missing.long$value)
colnames(combined.multivariate) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.multivariate, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_15_mcar
```{r}
#| label: fig-is.naplots5
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and univariate missing data for every variable"
#|  - "Density plot of non-missing and multivariate missing data for every variable"#| fig.width: 12
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[5]][[1]] %>% is.na()
missing_data.na <- missing_data.relevant[[5]][[1]] %>% is.na()

data.long <- data.relevant[[5]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.multivariate <- cbind(data.long, missing.long$value)
colnames(combined.multivariate) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.multivariate, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_15_mcar
```{r}
#| label: fig-is.naplots6
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and univariate missing data for every variable"
#|  - "Density plot of non-missing and multivariate missing data for every variable"#| fig.width: 12
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[6]][[1]] %>% is.na()
missing_data.na <- missing_data.relevant[[6]][[1]] %>% is.na()

data.long <- data.relevant[[6]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.multivariate <- cbind(data.long, missing.long$value)
colnames(combined.multivariate) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.multivariate, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 30_50_mcar
```{r}
#| label: fig-is.naplots7
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and univariate missing data for every variable"
#|  - "Density plot of non-missing and multivariate missing data for every variable"#| fig.width: 12
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[7]][[1]] %>% is.na()
missing_data.na <- missing_data.relevant[[7]][[1]] %>% is.na()

data.long <- data.relevant[[7]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.multivariate <- cbind(data.long, missing.long$value)
colnames(combined.multivariate) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.multivariate, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```

## 50_50_mcar
```{r}
#| label: fig-is.naplots8
#| echo: true
#| code-fold: true
#| fig.cap:
#|  - "Density plot of non-missing and univariate missing data for every variable"
#|  - "Density plot of non-missing and multivariate missing data for every variable"#| fig.width: 12
#| fig.width: 12
#| fig.height: 5
#| warning: false

is.na <- list()
is.na <- missing[[8]][[1]] %>% is.na()
missing_data.na <- missing_data.relevant[[8]][[1]] %>% is.na()

data.long <- data.relevant[[8]][[1]] %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
is.na.long <- is.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")
missing.long <- missing_data.na %>%
    as.data.frame() %>%
    pivot_longer(cols = everything(), names_to = c("variables"), values_to = "value")

combined <- cbind(data.long, is.na.long$value)
colnames(combined) <- c("variables", "value", "missing")

combined.multivariate <- cbind(data.long, missing.long$value)
colnames(combined.multivariate) <- c("variables", "value", "missing")

ggplot(combined, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")

ggplot(combined.multivariate, aes(x = value)) +
    geom_density(aes(fill = missing, color = missing), alpha = 0.3) +
    facet_wrap(~variables, scales = "free") +
    scale_fill_manual(values = c("#63B8FF", "#CD5C5C")) +
    scale_color_manual(values = c("#63B8FF", "#CD5C5C")) +
    theme_minimal() +
    labs(x = "Variable", y = "Density")
```
:::

:::

### Results

#### Groupsizes after listwise deletion
```{r}
#| label: listwise-groups
#| code-fold: true
#| df-print: paged

count <- list()
for (i in seq_len(nrow(combinations))) {
    count[[i]] <- map2(missing[[i]], data[[i]], function(x, y) {
        x %>%
            cbind(group = y$group) %>%
            setNames(c(colnames(x), "group")) %>%
            na.omit() %>%
            group_by(group) %>%
            summarise(n = n())
    }) %>%
        reduce(full_join, by = "group")

    colnames(count[[i]]) <- c("group", paste("n", 1:100, sep = "_"), "NAs")

    count[[i]] <- count[[i]] %>%
        mutate(NAs = rowSums(is.na(count[[i]][, 2:101]))) %>%
        select(group, NAs, everything())
}
```

::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| echo: false
datatable(count[[1]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_15_mar
```{r}
#| echo: false
datatable(count[[2]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 30_50_mar
```{r}
#| echo: false
datatable(count[[3]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_50_mar
```{r}
#| echo: false
datatable(count[[4]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 30_15_mcar
```{r}
#| echo: false
datatable(count[[5]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_15_mcar
```{r}
#| echo: false
datatable(count[[6]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 30_50_mcar
```{r}
#| echo: false
datatable(count[[7]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_50_mcar
```{r}
#| echo: false
datatable(count[[8]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

:::

:::

#### Analysis
```{r}
#| label: listwise-analysis-singular-missing
#| code-fold: true
#| message: false

############
# Set seed #
############
set.seed(123)
############################
# Plan parallel processing #
############################
cl <- makeForkCluster(5)
#######################
# Multilevel analysis #
#######################
# Define model
lmer.model.ld <- function(x) {
    model <- x %>% lme4::lmer(y ~ x1 + x2 + x3 + x4 + x5 + x6 + x7 + z1 + z2 + x1 * z1 + x2 * z1 + x3 * z2 + (1 + x1 + x2 + x3 | group),
        REML = TRUE,
        control = lmerControl(optimizer = "bobyqa"),
        data = .
    )
    results <- broom.mixed::tidy(model, conf.int = TRUE)

    return(results)
}
analyses <- list()
# Perform analyses
# map(seq_len(nrow(combinations)), ~ {
#     # Extract data 
#     # d <- map(missing[[.x]], ~ .x$data)
#     d <- missing[[.x]]
#     other <- map(data[[.x]], \(x) x %>% select(-y, -x1, -x2, -x3, -x4, -x5, -x6, -x7, -z1, -z2) %>% as.data.frame())
#     d <- map2(d, other, ~ cbind(.x, .y))
#     # Perform analyses
#     analyses[[.x]] <- pblapply(d, lmer.model.ld, cl = cl)
# })
for (i in seq_len(nrow(combinations))) {
    # Extract data 
    # d <- map(missing[[i]], ~ .x$data)
    d <- missing[[i]]
    other <- map(data[[i]], \(x) x %>% select(-y, -x1, -x2, -x3, -x4, -x5, -x6, -x7, -z1, -z2) %>% as.data.frame())
    d <- map2(d, other, ~ cbind(.x, .y))
    # Perform analyses
    analyses[[i]] <- pblapply(d, lmer.model.ld, cl = cl)
}
############################
# Stop parallel processing #
############################
stopCluster(cl)
```

#### Evaluation
```{r}
#| label: evaluation-functions
#| code-fold: true
#| message: false

#####################################
# Creating functions for evaluation #
#####################################
# Bias function
bias <- function(estimated) {
    # Extracting estimates
    estimates <- estimated %>%
        map(function(x) {
            fixed <- x %>%
                filter(term == "(Intercept)" | term == "x1" | term == "x2" | term == "x3" | term == "x4" | term == "x5" | term == "x6" | term == "x7" | term == "z1" | term == "z2" | term == "x1:z1" | term == "x2:z1" | term == "x3:z2") %>%
                pull(estimate, term)
            random <- x %>%
                filter(term == "sd__(Intercept)" | term == "sd__x1" | term == "sd__x2" | term == "sd__x3" | term == "sd__Observation") %>%
                pull(estimate, term) %>%
                sapply(function(x) x^2)
            c(fixed, random)
        })
    # Defining truth
    truth <- tibble(
        beta0j = 10,
        beta1j = .5,
        beta2j = .5,
        beta3j = .5,
        beta4j = .5,
        beta5j = .5,
        beta6j = .5,
        beta7j = .5,
        z1 = .5,
        z2 = .5,
        `x1:z1` = .35,
        `x2:z1` = .35,
        `x3:z2` = .35,
        u0 = 84.74903,
        u1 = 1,
        u2 = 1,
        u3 = 1,
        eij = 25
    )
    # Calculating bias for all datasets
    bias.datasets <- map(estimates, \(x) (x - truth)) %>%
        list_rbind() %>%
        as_tibble()
    # Average bias
    bias <- colMeans(bias.datasets) %>%
        t() %>%
        as_tibble()
    # Mean of estimates
    mean_estimates <- estimates %>%
        do.call(rbind, .) %>%
        colMeans() %>%
        t() %>%
        as_tibble()
    # Calculating MCSE
    mcse <- map(estimates, \(x) (x - mean_estimates)^2) %>%
        list_rbind() %>%
        colSums() %>%
        map_vec(\(x) sqrt(x / (length(estimates) * (length(estimates) - 1)))) %>%
        t() %>%
        as_tibble()
    colnames(mcse) <- colnames(bias)

    return(list(bias.datasets = bias.datasets, bias = bias, bias.mcse = mcse))
}
# Coverage function
coverage <- function(estimated) {
    # Extracting estimates
    estimates <- estimated %>%
        map(~ .x %>%
            filter(term == "(Intercept)" | term == "x1" | term == "x2" | term == "x3" | term == "x4" | term == "x5" | term == "x6" | term == "x7" | term == "z1" | term == "z2" | term == "x1:z1" | term == "x2:z1" | term == "x3:z2") %>%
            select(conf.low, conf.high))
    # Defining truth
    truth <- tibble(
        beta0j = 10,
        beta1j = .5,
        beta2j = .5,
        beta3j = .5,
        beta4j = .5,
        beta5j = .5,
        beta6j = .5,
        beta7j = .5,
        z1 = .5,
        z2 = .5,
        `x1:z1` = .35,
        `x2:z1` = .35,
        `x3:z2` = .35
    ) %>%
        t() %>%
        as_tibble() %>%
        rename(value = V1)
    # Combining estimates and truth
    combined <- map(estimates, \(x) cbind(x, truth))
    # Coverage of all data sets
    coverage.datasets <- map(combined, \(x) x %>%
        mutate(coverage = value > conf.low & value < conf.high) %>%
        select(coverage) %>%
        mutate(coverage = as.numeric(coverage)) %>%
        t() %>%
        as_tibble() %>%
        rename(beta0j = V1, beta1j = V2, beta2j = V3, beta3j = V4, beta4j = V5, beta5j = V6, beta6j = V7, beta7j = V8, z1 = V9, z2 = V10, `x1:z1` = V11, `x2:z1` = V12, `x3:z2` = V13)) %>%
        list_rbind()
    # Average coverage
    coverage <- colMeans(coverage.datasets) %>%
        t() %>%
        as_tibble()
    # Calculating MCSE of coverage
    mcse <- sqrt(coverage * (1 - coverage) / length(estimates)) %>%
        as_tibble()

    return(list(coverage.datasets = coverage.datasets, coverage = coverage, coverage.mcse = mcse))
}
# Confidence interval width function
ciw <- function(estimated) {
    # Extracting estimates
    estimates <- estimated %>%
        map(~ .x %>%
            filter(term == "(Intercept)" | term == "x1" | term == "x2" | term == "x3" | term == "x4" | term == "x5" | term == "x6" | term == "x7" | term == "z1" | term == "z2" | term == "x1:z1" | term == "x2:z1" | term == "x3:z2") %>%
            select(conf.low, conf.high))
    # Calculating CIW for all datasets
    ciw.datasets <- map(estimates, ~ .x %>%
        mutate(ciw = conf.high - conf.low) %>%
        select(ciw) %>%
        t() %>%
        as_tibble() %>%
        rename(beta0j = V1, beta1j = V2, beta2j = V3, beta3j = V4, beta4j = V5, beta5j = V6, beta6j = V7, beta7j = V8, z1 = V9, z2 = V10, `x1:z1` = V11, `x2:z1` = V12, `x3:z2` = V13)) %>%
        list_rbind()
    # Average CIW
    ciw <- colMeans(ciw.datasets) %>%
        t() %>%
        as_tibble()

    return(list(ciw.datasets = ciw.datasets, ciw = ciw))
}
```

##### Bias 
```{r}
#| label: bias-singular-missing
#| code-fold: true
#| message: false

bias.datasets_ld <- list()
for (i in seq_len(nrow(combinations))) {
    # Bias
    bias.datasets_ld[[i]] <- bias(analyses[[i]])
}

format.bias <- function(x, y, method, name = c("Bias", "MCSE")) {
    data <- cbind(x, y) %>%
        pivot_longer(cols = beta0j:eij, names_to = "term", values_to = name) %>%
        mutate(ngroup = as.factor(ngroup), groupsize = as.factor(groupsize), icc = as.factor(icc), mar_mcar = as.factor(mar_mcar), miss = as.factor(miss), g = as.factor(g), method = method)
    colnames(data) <- c("Number of groups", "Group size", "ICC", "Missingness mechanism", "Percentage of missing data", "Gamma", "Term", name, "Method")
    data <- data %>%
        mutate(`Missingness mechanism` = ifelse(`Missingness mechanism` == "mar", "MAR", "MCAR"))
    return(data)
}

bias_ld_univariate <- map(bias.datasets_ld, \(x) x$bias) %>%
    list_rbind() %>%
    as_tibble() %>%
    format.bias(combinations, method = "ld_univariate", name = "Bias") %>%
    cbind(map(bias.datasets_ld, \(x) x$bias.mcse) %>%
        list_rbind() %>%
        as_tibble() %>%
        format.bias(combinations, method = "ld_univariate", name = "MCSE") %>%
        dplyr::select(MCSE))

bias_ld_multivariate <- read_rds(paste(path, "results/evaluations/bias_ld.rds", sep = "")) %>%
    format.bias(., combinations, method = "ld_multivariate", name = "Bias") %>%
    cbind(read_rds(paste(path, "results/evaluations/mcse_bias_ld.rds", sep = "")) %>%
        format.bias(., combinations, method = "ld_multivariate", name = "MCSE") %>%
        dplyr::select(MCSE))

bias_ld <- bind_rows(bias_ld_univariate, bias_ld_multivariate)
```

```{r}
#| label: fig-bias-singular-missing
#| echo: false
#| message: false
#| fig.cap:
#|  - "Bias of the residual and intercept variance for all datasets"
#|  - "Bias of the overall intercept for all datasets"
#|  - "Bias of the fixed level-1 effects for all datasets"
#|  - "Bias of the fixed level-2 effects for all datasets"
#|  - "Bias of the cross-level interactions for all datasets"
#|  - "Bias of the random slopes for all datasets"

# Define color palette
cbbPalette <- c("#000000", "#E69F00", "#009E73", "#CC79A7", "#56B4E9", "#D55E00", "#5D478B", "#0072B2", "#F0E442")

bias_ld %>%
    filter(Term == "eij" | Term == "u0") %>%
    ggplot(aes(
        x = Bias,
        y = Term,
        color = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .2)) +
    geom_errorbar(aes(xmin = Bias - MCSE, xmax = Bias + MCSE), position = position_jitter(seed = 123, width = 0, height = .2), width = .25) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    scale_x_continuous(n.breaks = 15, minor_breaks = seq(-11, 11, .5), limits = c(-10, 10)) +
    scale_y_discrete(limits = c("eij", "u0"), labels = c(expression(paste(epsilon, "ij")), expression(paste(upsilon, "0")))) +
    geom_vline(xintercept = 0, color = "gray40") +
    geom_segment(y = 0, yend = 1.5, x = -2.5, linetype = "dashed", color = "gray40") +
    geom_segment(y = 0, yend = 1.5, x = 2.5, linetype = "dashed", color = "gray40") +
    geom_segment(y = 1.5, yend = 3, x = -8.474903, linetype = "dashed", color = "gray40") +
    geom_segment(y = 1.5, yend = 3, x = 8.474903, linetype = "dashed", color = "gray40") +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Absolute bias",
        y = "Term",
        color = "Method"
    )

bias_ld %>%
    filter(Term == "beta0j") %>%
    ggplot(aes(
        x = Bias,
        y = Term,
        color = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .3)) +
    geom_errorbar(aes(xmin = Bias - MCSE, xmax = Bias + MCSE), position = position_jitter(seed = 123, width = 0, height = .3), width = .08) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    scale_x_continuous(n.breaks = 10, minor_breaks = seq(-.4, .4, .025)) +
    scale_y_discrete(limits = c("beta0j"), labels = c(expression(paste(gamma, "00")))) +
    geom_vline(xintercept = 0, color = "gray40") +
    geom_segment(y = 0, yend = 2, x = -.1, linetype = "dashed", color = "gray40") +
    geom_segment(y = 0, yend = 2, x = .1, linetype = "dashed", color = "gray40") +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Absolute bias",
        y = "Term",
        color = "Method"
    )

bias_ld %>%
    filter(Term == "beta1j" | Term == "beta2j" | Term == "beta3j" | Term == "beta4j" | Term == "beta5j" | Term == "beta6j" | Term == "beta7j") %>%
    ggplot(aes(
        x = Bias,
        y = Term,
        color = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .2)) +
    geom_errorbar(aes(xmin = Bias - MCSE, xmax = Bias + MCSE), position = position_jitter(seed = 123, width = 0, height = .2), width = .3) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    scale_x_continuous(n.breaks = 10, minor_breaks = seq(-.08, .08, .005)) +
    scale_y_discrete(limits = c("beta1j", "beta2j", "beta3j", "beta4j", "beta5j", "beta6j", "beta7j"), labels = c(expression(paste(gamma, "10")), expression(paste(gamma, "20")), expression(paste(gamma, "30")), expression(paste(gamma, "40")), expression(paste(gamma, "50")), expression(paste(gamma, "60")), expression(paste(gamma, "70")))) +
    geom_vline(xintercept = 0, color = "gray40") +
    geom_vline(xintercept = -.05, linetype = "dashed", color = "gray40") +
    geom_vline(xintercept = .05, linetype = "dashed", color = "gray40") +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Absolute bias",
        y = "Term",
        color = "Method"
    )

bias_ld %>%
    filter(Term == "z1" | Term == "z2") %>%
    ggplot(aes(
        x = Bias,
        y = Term,
        color = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .2)) +
    geom_errorbar(aes(xmin = Bias - MCSE, xmax = Bias + MCSE), position = position_jitter(seed = 123, width = 0, height = .2), width = .25) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    scale_x_continuous(n.breaks = 10, minor_breaks = seq(-.4, .4, .025)) +
    scale_y_discrete(limits = c("z1", "z2"), labels = c(expression(paste(gamma, "01")), expression(paste(gamma, "02")))) +
    geom_vline(xintercept = 0, color = "gray40") +
    geom_segment(y = 0, yend = 3, x = -.05, linetype = "dashed", color = "gray40") +
    geom_segment(y = 0, yend = 3, x = .05, linetype = "dashed", color = "gray40") +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Absolute bias",
        y = "Term",
        color = "Method"
    )

bias_ld %>%
    filter(Term == "x1:z1" | Term == "x2:z1" | Term == "x3:z2") %>%
    ggplot(aes(
        x = Bias,
        y = Term,
        color = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .1)) +
    geom_errorbar(aes(xmin = Bias - MCSE, xmax = Bias + MCSE), position = position_jitter(seed = 123, width = 0, height = .1), width = .25) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    scale_x_continuous(n.breaks = 10, minor_breaks = seq(-.07, .07, .005)) +
    scale_y_discrete(limits = c("x1:z1", "x2:z1", "x3:z2"), labels = c(expression(paste(gamma, "11")), expression(paste(gamma, "21")), expression(paste(gamma, "32")))) +
    geom_vline(xintercept = 0, color = "gray40") +
    geom_segment(y = 0, yend = 4, x = -.035, linetype = "dashed", color = "gray40") +
    geom_segment(y = 0, yend = 4, x = .035, linetype = "dashed", color = "gray40") +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Absolute bias",
        y = "Term",
        color = "Method"
    )

bias_ld %>%
    filter(Term == "u1" | Term == "u2" | Term == "u3") %>%
    ggplot(aes(
        x = Bias,
        y = Term,
        color = Method
    )) +
    geom_point(position = position_jitter(seed = 123, width = 0, height = .1)) +
    geom_errorbar(aes(xmin = Bias - MCSE, xmax = Bias + MCSE), position = position_jitter(seed = 123, width = 0, height = .1), width = .25) +
    facet_grid(cols = vars(`Number of groups`, `Group size`), rows = vars(`Missingness mechanism`), labeller = labeller(.rows = label_value, .cols = label_both)) +
    scale_x_continuous(n.breaks = 10, minor_breaks = seq(-.1, .3, .01)) +
    scale_y_discrete(limits = c("u1", "u2", "u3"), labels = c(expression(paste(upsilon, "1")), expression(paste(upsilon, "2")), expression(paste(upsilon, "3")))) +
    geom_vline(xintercept = 0, color = "gray40") +
    geom_segment(y = 0, yend = 4, x = -.1, linetype = "dashed", color = "gray40") +
    geom_segment(y = 0, yend = 4, x = .1, linetype = "dashed", color = "gray40") +
    scale_color_manual(values = cbbPalette) +
    theme_minimal() +
    theme(panel.border = element_rect(colour = "gray25", fill = NA, size = .5), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), legend.position = "bottom", legend.text = element_text(size = 9), axis.title = element_text(size = 12), legend.title = element_text(size = 12), panel.grid = element_line(color = "gray80")) +
    labs(
        x = "Absolute bias",
        y = "Term",
        color = "Method"
    )
```

##### Coverage
```{r}
# Coverage
coverage.datasets_ld <- list()
for (i in seq_len(nrow(combinations))) {
    # Logging iteration
    cat("Processing iteration:", i, "\n")
    # Coverage
    coverage.datasets_ld[[i]] <- coverage(analyses[[i]])
}
```

##### Confidence interval width
```{r}
ciw.datasets_ld <- list()
for (i in seq_len(nrow(combinations))) {
    # Logging iteration
    cat("Processing iteration:", i, "\n")
    # CIW
    ciw.datasets_ld[[i]] <- ciw(analyses[[i]])
}
```

## Creating missing data in a multivariate way

### No grouping

### Grouping

## Other articles
