---
title: Simulation according to @enders2018
author: "Heleen Brüggen"
format: 
    html:
        toc: true
        number-sections: true
        toc-location: right
bibliography: references.bib
---
```{r}
#| label: set-up
#| warning: false
#| message: false
#| echo: false

#############
# Libraries #
#############
library(tidyverse)
library(knitr)
library(DT)
library(lme4)
library(mitml)
library(mice)
library(lmerTest)
library(magrittr)
library(purrr)
library(furrr)
library(dplyr)
library(pbapply)
library(parallel)
library(readr)
library(jtools)
library(broom.mixed)
library(ggmice)
library(nlme)
library(ggplot2)
################
# Setting seed #
################
set.seed(123)
```

# Population parameters

The population generating mechanism is: 
$$y_{ij} = \beta_0 + \beta_1x_{ij} + \beta_2w_j + b{0j} + b{1j}x_{ij} + \epsilon_{ij},$$

where $y_{ij}$ is the outcome score for observation i in cluster j, $x_{ij}$ is the level-1 predictor, $w_j$ is the level-2 predictor, $\beta_0$ is the intercept, $\beta_1$ and $\beta_2$ are the fixed slope coefficients, $b{0j}$ and $b_{1j}$ are the random intercept and random slope, and $\epsilon_{ij}$ is the level-1 error term. The random effects are assumed to be normally distributed with mean 0 and covariance matrix $\Sigma_b$. The level-1 error term is assumed to be normally distributed with mean 0 and variance $\sigma^2_e$.

The data generation also included two auxiliary variables $a_1$ and $a_2$. $a_1$ determined the missingness probabilities in $x$ and $a_2$ determined the missingness probabilities in $w$. 

The population correlations are as follows: 

|      | y  | X  | w  | av_1 | av_2 |
|------|----|----|----|------|------|
| y    | 1  | .4 | .3 | .4   | 0    |
| X    | .4 | 1  | .3 | .4   | 0    |
| w    | .3 | .3 | 1  | 0    | .4   |
| av_1 | .4 | .4 | 0  | 1    | 0    |
| av_2 | 0  | 0  | .4 | 0    | 1    |

Next, they solved for the population parameters. They started by setting the total variance of all variables to unity. The level-2 predictor $w$ and the auxiliary variables all had variation assigned to a single level, whereas $y$ and $X$ had variation at both levels, with the between cluster variance set to .1 or .5. 

Then, they computed the level-1 and level-2 covariance matrices ($\Sigma^{(1)}$ and $\Sigma^{(2)}$) by pre- and postmultiplying the total correlation matrix by a diagonal matrix containing the level-1 or level-2 standard deviations.

The total correlation matrix is given by:
$$
\mathbf{r} = \begin{pmatrix}
1 & .4 & .3 & .4 & 0 \\
.4 & 1 & .3 & .4 & 0 \\
.3 & .3 & 1 & 0 & .4 \\
.4 & .4 & 0 & 1 & 0 \\
0 & 0 & .4 & 0 & 1
\end{pmatrix}
$$

The level-1 covariance matrix with ICC = .5 is given by:
$$
\mathbf{\Sigma}^{(1)} = \begin{pmatrix}
\sqrt{.5} & 0 & 0 & 0 & 0 \\
0 & \sqrt{.5} & 0 & 0 & 0 \\
0 & 0 & 0 & 0 & 0 \\
0 & 0 & 0 & 1 & 0 \\
0 & 0 & 0 & 0 & 0
\end{pmatrix} \cdot
\begin{pmatrix}
1 & .4 & .3 & .4 & 0 \\
.4 & 1 & .3 & .4 & 0 \\
.3 & .3 & 1 & 0 & .4 \\
.4 & .4 & 0 & 1 & 0 \\
0 & 0 & .4 & 0 & 1
\end{pmatrix} \cdot
\begin{pmatrix}
\sqrt{.5} & 0 & 0 & 0 & 0 \\
0 & \sqrt{.5} & 0 & 0 & 0 \\
0 & 0 & 0 & 0 & 0 \\
0 & 0 & 0 & 1 & 0 \\
0 & 0 & 0 & 0 & 0
\end{pmatrix}
$$
```{r}
#| label: covariance-matrices-level-1
#| echo: false
#| eval: false

a <- matrix(c(
    1, .4, .3, .4, 0,
    .4, 1, .3, .4, 0,
    .3, .3, 1, 0, .4,
    .4, .4, 0, 1, 0,
    0, 0, .4, 0, 1
), nrow = 5, byrow = TRUE)
b <- matrix(c(
    sqrt(.5), 0, 0, 0, 0,
    0, sqrt(.5), 0, 0, 0,
    0, 0, 0, 0, 0,
    0, 0, 0, 1, 0,
    0, 0, 0, 0, 0
), nrow = 5, byrow = TRUE)
c1 <- b %*% a %*% b
kable(c1, digits = 2)
```
$$ =
\begin{pmatrix}
.50 & .20 & 0 & .28 & 0 \\
.20 & .50 & 0 & .28 & 0 \\
0 & 0 & 0 & 0 & 0 \\
.28 & .28 & 0 & 1 & 0 \\
0 & 0 & 0 & 0 & 0
\end{pmatrix}
$$

The level-2 covariance matrix with ICC = .5 is given by:
$$
\mathbf{\Sigma}^{(2)} = \begin{pmatrix}
\sqrt{.5} & 0 & 0 & 0 & 0 \\
0 & \sqrt{.5} & 0 & 0 & 0 \\
0 & 0 & 1 & 0 & 0 \\
0 & 0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 & 1
\end{pmatrix} \cdot
\begin{pmatrix}
1 & .4 & .3 & .4 & 0 \\
.4 & 1 & .3 & .4 & 0 \\
.3 & .3 & 1 & 0 & .4 \\
.4 & .4 & 0 & 1 & 0 \\
0 & 0 & .4 & 0 & 1
\end{pmatrix} \cdot
\begin{pmatrix}
\sqrt{.5} & 0 & 0 & 0 & 0 \\
0 & \sqrt{.5} & 0 & 0 & 0 \\
0 & 0 & 1 & 0 & 0 \\
0 & 0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 & 1
\end{pmatrix} 
$$
```{r}
#| label: covariance-matrices-level-2
#| echo: false
#| eval: false

a <- matrix(c(
    1, .4, .3, .4, 0,
    .4, 1, .3, .4, 0,
    .3, .3, 1, 0, .4,
    .4, .4, 0, 1, 0,
    0, 0, .4, 0, 1
), nrow = 5, byrow = TRUE)
b <- matrix(c(
    sqrt(.5), 0, 0, 0, 0,
    0, sqrt(.5), 0, 0, 0,
    0, 0, 1, 0, 0,
    0, 0, 0, 0, 0,
    0, 0, 0, 0, 1
), nrow = 5, byrow = TRUE)
c2 <- b %*% a %*% b
kable(c2, digits = 2)
```
$$ = \begin{pmatrix}
.50 & .20 & .21 & 0 & 0 \\
.20 & .50 & .21 & 0 & 0 \\
.21 & .21 & 1.00 & 0 & .40 \\
0 & 0 & 0 & 0 & 0 \\
0 & 0 & .40 & 0 & 1.00
\end{pmatrix}
$$

The total covariance matrix is given by: 
$$
\mathbf{\Sigma} = \begin{pmatrix}
.50 & .20 & 0 & .28 & 0 \\
.20 & .50 & 0 & .28 & 0 \\
0 & 0 & 0 & 0 & 0 \\
.28 & .28 & 0 & 1 & 0 \\
0 & 0 & 0 & 0 & 0
\end{pmatrix} + \begin{pmatrix}
.50 & .20 & .21 & 0 & 0 \\
.20 & .50 & .21 & 0 & 0 \\
.21 & .21 & 1.00 & 0 & .40 \\
0 & 0 & 0 & 0 & 0 \\
0 & 0 & .40 & 0 & 1.00
\end{pmatrix}
$$
```{r}
#| label: covariance-matrix
#| echo: false
#| eval: false

c <- c1 + c2
kable(c, digits = 2)
```
$$ = \begin{pmatrix}
1.00 & .40 & .21 & .28 & 0 \\
.40 & 1.00 & .21 & .28 & 0 \\
.21 & .21 & 1.00 & 0 & .40 \\
.28 & .28 & 0 & 1.00 & 0 \\
0 & 0 & .40 & 0 & 1.00
\end{pmatrix}
$$

Then, they used the following expressions to solve for the population parameters: 
$$
\mathbf{\beta} = \mathbf{\Sigma_{(xw)}^{-1}}\mathbf{\Sigma_{(y,xw)}}
$$
$$
\sigma^2_{b_1} = .40(\sigma^{2(2)}_y)
$$
$$
\sigma^2_e = \sigma^{2(1)}_y-\mathbf{\beta}^{'}\mathbf{\Sigma}^{(1)}_{(xw)}\mathbf{\beta}-\sigma^2_{b_1}\sigma^{2(1)}_x
$$
$$
\sigma^2_{b_0} = \sigma^{2(2)}_y-\mathbf{\beta}^{'}\mathbf{\Sigma}^{(2)}_{(xw)}\mathbf{\beta}-\sigma^2_{b_1}\sigma^{2(2)}_x
$$
$$
\sigma_{b_0b_1}^2 = r_{b_0b_1}(\sigma^2_{b_0}\sigma^2_{b_1})^{-\frac{1}{2}}
$$
$$
\beta_0 = 5
$$

$$
\mathbf{\Sigma}_{(xw)} = \begin{pmatrix}
1.00 & .40 \\
.40 & 1.00
\end{pmatrix}, 
\mathbf{\Sigma}_{(xw)}^{(1)} = \begin{pmatrix}
.50 & 0 \\
0 & 0
\end{pmatrix},
\mathbf{\Sigma}_{(xw)}^{(2)} = \begin{pmatrix}
.50 & .21 \\
.21 & 1.00
\end{pmatrix},
\mathbf{\Sigma}_{(y,xw)} = \begin{pmatrix}
.40 \\
.21 
\end{pmatrix},
$$
$$
\sigma^{2(1)}_y = .5, \sigma^{2(2)}_y = .5
$$

```{r}
#| label: population-parameters
#| echo: false

Sxw <- matrix(c(
    1, .40,
    .40, 1
), nrow = 2, byrow = TRUE)
Syxw <- matrix(c(
    .40,
    .21
), nrow = 2, byrow = TRUE)
Sxw1 <- matrix(c(
    .5, 0,
    0, 0
), nrow = 2, byrow = TRUE)
Sxw2 <- matrix(c(
    .5, .21,
    .21, 1
), nrow = 2, byrow = TRUE)
beta <- solve(Sxw) %*% Syxw

sigmab1 <- .4 * .5

sigmae <- .5 - t(beta) %*% Sxw1 %*% beta - sigmab1 * .5
sigmab0 <- .5 - t(beta) %*% Sxw2 %*% beta - sigmab1 * .5
sigmab0b1 <- .4*sqrt(sigmab0*sigmab1)
```

From this, the following values are obtained:
$$
\mathbf{\beta} = \begin{pmatrix}
.376 \\
.060
\end{pmatrix},
\sigma^2_{b_1} = .20,
\sigma^2_e = .329,
\sigma^2_{b_0} = .316,
\sigma^2_{b_0b_1} = .101
$$
$$
\mathbf{\Sigma}_{b} = \begin{pmatrix}
.316 & .101 \\
.101 & .20
\end{pmatrix}
$$

# Data generation

For the data generation, they used the following steps:

1. Sample the within- and between-cluster components of the predictor variables from a normal distribution with zero means and covariance matrices of $\mathbf{\Sigma}_{(xw)}^{(1)}$ and $\mathbf{\Sigma}_{(xw)}^{(2)}$, respectively.
2. Compute $X$ as the sum of its within- and between-cluster deviation scores.
3. Sample $b_{0j}$ and $b_{1j}$ from a normal distribution with means of 0 and covariance matrix $\mathbf{\Sigma}_{b}$.
3. Sample $e_{ij}$ from a normal distribution with mean 0 and variance $\sigma^2_e$.
4. Compute $y_{ij}$ as the weighted sum of $x$, $w$, $b_{0j}$, $b_{1j}$, and $e_{ij}$.


# References

::: {#refs}
:::