---
title: "Singularity/non convergence problem"
author: "Heleen Brüggen"
format: 
    html:
        toc: true
        number-sections: true
        toc-location: right
---

```{r}
#| label: set-up
#| warning: false
#| message: false
#| echo: false

#############
# Libraries #
#############
library(tidyverse)
library(knitr)
library(DT)
library(lme4)
library(lmerTest)
library(magrittr)
library(purrr)
library(dplyr)
library(pbapply)
library(parallel)
library(readr)
library(jtools)
library(broom.mixed)
################
# Setting seed #
################
set.seed(123)
################
# Setting path #
################
path <- "/Volumes/Heleen 480GB/MBART-MICE files/"
#######################
# Defining parameters #
#######################
combinations <- read_rds(paste(path, "data/combinations.rds", sep = ""))
#############################
# Storing names of datasets #
#############################
names <- read_rds(paste(path, "data/names.rds", sep = ""))
```

# Imputation methods 

## Listwise deletion 

### Groupsizes after listwise deletion

First we load the data for the listwise deletion method. 
```{r}
#| label: listwise-data
#| code-fold: true

data <- list()
for (i in seq_len(nrow(combinations))) {
    data[[i]] <- read_rds(paste(path, "data/missing/simdata_miss_", names[i], ".rds", sep = "")) %>% map(~ .x %>% na.omit())
}
```

Then, we check the amount of observations per group. 

```{r}
#| label: listwise-groups
#| code-fold: true
#| df-print: paged

count <- list()
for (i in seq_len(nrow(combinations))) {
    count[[i]] <- data[[i]] %>%
        map(~ .x %>%
            group_by(group) %>%
            summarise(n = n())) %>%
        reduce(full_join, by = "group")
    colnames(count[[i]]) <- c("group", paste("n", 1:100, sep = "_"))

    # count[[i]] <- count[[i]] %>%
    #     pivot_longer(cols = !group, names_to = "dataset", values_to = "n")

    count[[i]] <- count[[i]] %>%
        mutate(NAs = rowSums(is.na(count[[i]][, 2:101]))) %>%
        select(group, NAs, everything())
}
```

::: {.panel-tabset}

## 30_15_mar
```{r}
#| echo: false
datatable(count[[1]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_15_mar
```{r}
#| echo: false
datatable(count[[2]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 30_50_mar
```{r}
#| echo: false
datatable(count[[3]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_50_mar
```{r}
#| echo: false
datatable(count[[4]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 30_15_mcar
```{r}
#| echo: false
datatable(count[[5]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_15_mcar
```{r}
#| echo: false
datatable(count[[6]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 30_50_mcar
```{r}
#| echo: false
datatable(count[[7]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_50_mcar
```{r}
#| echo: false
datatable(count[[8]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

:::

In these tables we can see that for the MAR mechanism there are some groups with no observations (30_15 and 50_15). Furthermore, there are also groups with 1-5 oberservations in the groups for both MAR and MCAR when the groupsizes are 15. 

### Singularity and non-convergence problem 

```{r}
#| label: listwise-analysis
#| code-fold: true


############################
# Plan parallel processing #
############################
cl <- makeForkCluster(5)
#######################
# Multilevel analysis #
#######################
# Define model
lmer.model.ld <- function(x) {
    model <- x %>% lme4::lmer(y ~ x1 + x2 + x3 + x4 + x5 + x6 + x7 + z1 + z2 + x1 * z1 + x2 * z1 + x3 * z2 + (1 + x1 + x2 + x3 | group),
        REML = TRUE,
        control = lmerControl(optimizer = "bobyqa"),
        data = .
    )

    modelblme <- x %>% blme::blmer(y ~ x1 + x2 + x3 + x4 + x5 + x6 + x7 + z1 + z2 + x1 * z1 + x2 * z1 + x3 * z2 + (1 + x1 + x2 + x3 | group),
        REML = TRUE,
        data = .
    )

    # modelrstanarm <- x %>% rstanarm::stan_glmer(y ~ x1 + x2 + x3 + x4 + x5 + x6 + x7 + z1 + z2 + x1 * z1 + x2 * z1 + x3 * z2 + (1 + x1 + x2 + x3 | group),
    #     data = .
    # )

    results <- broom.mixed::tidy(model, conf.int = TRUE)
    resultsmodelblme <- broom.mixed::tidy(modelblme, conf.int = TRUE)
    # resultsmodelrstanarm <- broom.mixed::tidy(modelrstanarm, conf.int = TRUE)

    return(list(lmer = results, blme = resultsmodelblme))
}
# Perform analyses
analyses_ld <- list()
for (i in seq_len(nrow(combinations))) {
    # Logging iteration
    cat("Processing iteration:", i, "\n")
    analyses_ld <- pblapply(data[[i]], lmer.model.ld, cl = cl)
}
############################
# Stop parallel processing #
############################
stopCluster(cl)
```