---
title: "Singularity/non convergence problem"
author: "Heleen Brüggen"
format: 
    html:
        toc: true
        number-sections: true
        toc-location: right
---

```{r}
#| label: set-up
#| warning: false
#| message: false
#| echo: false

#############
# Libraries #
#############
library(tidyverse)
library(knitr)
library(DT)
library(lme4)
library(mitml)
library(mice)
library(lmerTest)
library(magrittr)
library(purrr)
library(furrr)
library(dplyr)
library(pbapply)
library(parallel)
library(readr)
library(jtools)
library(broom.mixed)
library(ggmice)
library(nlme)
################
# Setting seed #
################
set.seed(123)
################
# Setting path #
################
path <- "/Volumes/Heleen 480GB/MBART-MICE files/"
#######################
# Defining parameters #
#######################
combinations <- read_rds(paste(path, "data/combinations.rds", sep = ""))
#############################
# Storing names of datasets #
#############################
names <- read_rds(paste(path, "data/names.rds", sep = ""))
```

# Missing data mechanism

```{r}
#| label: data
#| code-fold: true
#| eval: false

# Loading data with missing
data <- list()
for (i in seq_len(nrow(combinations))) {
    data[[i]] <- read_rds(paste(path, "data/missing/simdata_miss_", names[i], ".rds", sep = ""))
}

# Extracting amputation objects from results
miss <- list()
for (i in seq_len(nrow(combinations))) {
    miss[[i]] <- read_rds(paste(path, "data/missing/miss_", names[i], ".rds", sep = "")) %>% map(~ .x %$% miss)
}

plot_pattern(data[[1]][[1]][, c("x1", "x2", "x3", "x4", "x5", "x6", "x7", "y", "z1", "z2")])
plot_flux(data[[1]][[1]][, c("x1", "x2", "x3", "x4", "x5", "x6", "x7", "y", "z1", "z2")])
plot_corr(data[[1]][[1]][, c("x1", "x2", "x3", "x4", "x5", "x6", "x7", "y", "z1", "z2")], label = TRUE)
```

# Imputation methods 

## Listwise deletion 

### Groupsizes after listwise deletion

First we load the data for the listwise deletion method. 
```{r}
#| label: listwise-data
#| code-fold: true

data <- list()
for (i in seq_len(nrow(combinations))) {
    data[[i]] <- read_rds(paste(path, "data/missing/simdata_miss_", names[i], ".rds", sep = "")) %>% map(~ .x %>% na.omit())
}
```

Then, we check the amount of observations per group. 

```{r}
#| label: listwise-groups
#| code-fold: true
#| df-print: paged

count <- list()
for (i in seq_len(nrow(combinations))) {
    count[[i]] <- data[[i]] %>%
        map(~ .x %>%
            group_by(group) %>%
            summarise(n = n())) %>%
        reduce(full_join, by = "group")
    colnames(count[[i]]) <- c("group", paste("n", 1:100, sep = "_"))

    # count[[i]] <- count[[i]] %>%
    #     pivot_longer(cols = !group, names_to = "dataset", values_to = "n")

    count[[i]] <- count[[i]] %>%
        mutate(NAs = rowSums(is.na(count[[i]][, 2:101]))) %>%
        select(group, NAs, everything())
}
```

::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| echo: false
datatable(count[[1]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_15_mar
```{r}
#| echo: false
datatable(count[[2]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 30_50_mar
```{r}
#| echo: false
datatable(count[[3]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_50_mar
```{r}
#| echo: false
datatable(count[[4]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 30_15_mcar
```{r}
#| echo: false
datatable(count[[5]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_15_mcar
```{r}
#| echo: false
datatable(count[[6]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 30_50_mcar
```{r}
#| echo: false
datatable(count[[7]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

## 50_50_mcar
```{r}
#| echo: false
datatable(count[[8]],
    rownames = FALSE
) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(0), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 2,
        backgroundColor = styleEqual(c(!0), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(NA), c("#FF3030"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(1), c("#FF7256"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(2), c("#FF7F00"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(3), c("#FFB90F"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(4), c("#FFD700"))
    ) %>%
    formatStyle(
        columns = 3:102,
        backgroundColor = styleEqual(c(5), c("#FFEC8B"))
    )
```

:::

:::

In these tables we can see that for the MAR mechanism there are some groups with no observations (30_15 and 50_15). Furthermore, there are also groups with 1-5 oberservations in the groups for both MAR and MCAR when the groupsizes are 15. 

### Variance

```{r}
#| label: listwise-variance
#| code-fold: true

variance <- list()
variance <- map(seq_len(nrow(combinations)), function(i) {
    result <- data[[i]] %>%
        map(~ .x %>%
            summarise(across(c(x1, x2, x3, x4, x5, x6, x7, y, z1, z2, u0, u1, u2, u3, eij), list(
                var = ~ var(.x, na.rm = TRUE),
                max = ~ max(.x, na.rm = TRUE),
                min = ~ min(.x, na.rm = TRUE)
            ))) %>%
            bind_rows() %>%
            pivot_longer(cols = everything(), names_to = c("variable", ".value"), names_sep = "_")) %>%
        reduce(full_join, by = "variable") %>%
        as_tibble()

    colnames(result) <- c("variable", paste0(rep(c("var", "max", "min")), "_", rep(1:100, each = 3)))

    result
})
plot_variance <- list()
plot_variance <- map(seq_len(nrow(combinations)), function(i) {
    variance[[i]] %>%
        pivot_longer(cols = -variable, names_to = c("function", "dataset"), names_sep = "_")
})
```

::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| label: fig-variance3015mar
#| fig-cap: "Variance in data set"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15

ggplot(plot_variance[[1]], aes(x = variable, y = value)) +
    geom_boxplot() +
    facet_wrap(~`function`) +
    theme_minimal()
```

## 50_15_mar
```{r}
#| label: fig-variance5015mar
#| fig-cap: "Variance in data set"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15

ggplot(plot_variance[[2]], aes(x = variable, y = value)) +
    geom_boxplot() +
    facet_wrap(~`function`) +
    theme_minimal()
```

## 30_50_mar
```{r}
#| label: fig-variance3050mar
#| fig-cap: "Variance in data set"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15

ggplot(plot_variance[[3]], aes(x = variable, y = value)) +
    geom_boxplot() +
    facet_wrap(~`function`) +
    theme_minimal()
```

## 50_50_mar
```{r}
#| label: fig-variance5050mar
#| fig-cap: "Variance in data set"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15

ggplot(plot_variance[[4]], aes(x = variable, y = value)) +
    geom_boxplot() +
    facet_wrap(~`function`) +
    theme_minimal()
```

## 30_15_mcar
```{r}
#| label: fig-variance3015mcar
#| fig-cap: "Variance in data set"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15

ggplot(plot_variance[[5]], aes(x = variable, y = value)) +
    geom_boxplot() +
    facet_wrap(~`function`) +
    theme_minimal()
```

## 50_15_mcar
```{r}
#| label: fig-variance5015mcar
#| fig-cap: "Variance in data set"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15

ggplot(plot_variance[[6]], aes(x = variable, y = value)) +
    geom_boxplot() +
    facet_wrap(~`function`) +
    theme_minimal()
```

## 30_50_mcar
```{r}
#| label: fig-variance3050mcar
#| fig-cap: "Variance in data set"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15

ggplot(plot_variance[[7]], aes(x = variable, y = value)) +
    geom_boxplot() +
    facet_wrap(~`function`) +
    theme_minimal()
```

## 50_50_mcar
```{r}
#| label: fig-variance5050mcar
#| fig-cap: "Variance in data set"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15

ggplot(plot_variance[[8]], aes(x = variable, y = value)) +
    geom_boxplot() +
    facet_wrap(~`function`) +
    theme_minimal()
```

:::

::: 

### Variance analyses

```{r}
#| label: listwise-analyses
#| code-fold: true

analyses <- list()
for (i in seq_len(nrow(combinations))) {
    analyses[[i]] <- read_rds(paste(path, "results/listwise/analyses_ld_", names[i], ".rds", sep = ""))
}
```

```{r}
#| label: listwise-analyses-variance
#| code-fold: true

varianceanalyses <- list()
varianceanalyses <- map(seq_len(nrow(combinations)), function(i) {
    result <- map(analyses[[i]], ~ .x %>%
        select(term, estimate)) %>%
        bind_rows() %>%
        filter(!term %in% c("cor__(Intercept).x1", "cor__(Intercept).x2", "cor__(Intercept).x3", "cor__x1.x2", "cor__x2.x3", "cor__x1.x3")) %>%
        mutate(dataset = paste0(rep(1:100, each = 18)))
})
```

::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| label: fig-varianceanalyses3015mar
#| fig-cap: "Variance in analyses results"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15
#| fig-height: 10

ggplot(varianceanalyses[[1]], aes(x = term, y = estimate)) +
    stat_summary(fun = mean, geom = "point", size = 2, fill = "black") +
    stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.1) +
    geom_violin(color = "lightskyblue4", fill = "lightskyblue", alpha = .8, adjust = .5) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 12, angle = 45, hjust = 1))
```

## 50_15_mar
```{r}
#| label: fig-varianceanalyses5015mar
#| fig-cap: "Variance in analyses results"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15
#| fig-height: 10

ggplot(varianceanalyses[[2]], aes(x = term, y = estimate)) +
    stat_summary(fun = mean, geom = "point", size = 2, fill = "black") +
    stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.1) +
    geom_violin(color = "lightskyblue4", fill = "lightskyblue", alpha = .8, adjust = .5) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 12, angle = 45, hjust = 1))
```

## 30_50_mar
```{r}
#| label: fig-varianceanalyses3050mar
#| fig-cap: "Variance in analyses results"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15
#| fig-height: 10

ggplot(varianceanalyses[[3]], aes(x = term, y = estimate)) +
    stat_summary(fun = mean, geom = "point", size = 2, fill = "black") +
    stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.1) +
    geom_violin(color = "lightskyblue4", fill = "lightskyblue", alpha = .8, adjust = .5) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 12, angle = 45, hjust = 1))
```

## 50_50_mar
```{r}
#| label: fig-varianceanalyses5050mar
#| fig-cap: "Variance in analyses results"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15
#| fig-height: 10

ggplot(varianceanalyses[[4]], aes(x = term, y = estimate)) +
    stat_summary(fun = mean, geom = "point", size = 2, fill = "black") +
    stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.1) +
    geom_violin(color = "lightskyblue4", fill = "lightskyblue", alpha = .8, adjust = .5) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 12, angle = 45, hjust = 1))
```

## 30_15_mcar
```{r}
#| label: fig-varianceanalyses3015mcar
#| fig-cap: "Variance in analyses results"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15
#| fig-height: 10

ggplot(varianceanalyses[[5]], aes(x = term, y = estimate)) +
    stat_summary(fun = mean, geom = "point", size = 2, fill = "black") +
    stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.1) +
    geom_violin(color = "lightskyblue4", fill = "lightskyblue", alpha = .8, adjust = .5) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 12, angle = 45, hjust = 1))
```

## 50_15_mcar
```{r}
#| label: fig-varianceanalyses5015mcar
#| fig-cap: "Variance in analyses results"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15
#| fig-height: 10

ggplot(varianceanalyses[[6]], aes(x = term, y = estimate)) +
    stat_summary(fun = mean, geom = "point", size = 2, fill = "black") +
    stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.1) +
    geom_violin(color = "lightskyblue4", fill = "lightskyblue", alpha = .8, adjust = .5) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 12, angle = 45, hjust = 1))
```

## 30_50_mcar
```{r}
#| label: fig-varianceanalyses3050mcar
#| fig-cap: "Variance in analyses results"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15
#| fig-height: 10

ggplot(varianceanalyses[[7]], aes(x = term, y = estimate)) +
    stat_summary(fun = mean, geom = "point", size = 2, fill = "black") +
    stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.1) +
    geom_violin(color = "lightskyblue4", fill = "lightskyblue", alpha = .8, adjust = .5) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 12, angle = 45, hjust = 1))
```

## 50_50_mcar
```{r}
#| label: fig-varianceanalyses5050mcar
#| fig-cap: "Variance in analyses results"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15
#| fig-height: 10

ggplot(varianceanalyses[[8]], aes(x = term, y = estimate)) +
    stat_summary(fun = mean, geom = "point", size = 2, fill = "black") +
    stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.1) +
    geom_violin(color = "lightskyblue4", fill = "lightskyblue", alpha = .8, adjust = .5) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 12, angle = 45, hjust = 1))
```

:::

:::

### Singularity and non-convergence problem 

```{r}
#| label: listwise-analysis
#| code-fold: true
#| message: false
#| eval: false

############
# Set seed #
############
set.seed(123)
############################
# Plan parallel processing #
############################
cl <- makeForkCluster(5)
#######################
# Multilevel analysis #
#######################
# Define model
lmer.model.ld <- function(x) {
    model <- x %>% lme4::lmer(y ~ x1 + x2 + x3 + x4 + x5 + x6 + x7 + z1 + z2 + x1 * z1 + x2 * z1 + x3 * z2 + (1 + x1 + x2 + x3 | group),
        REML = TRUE,
        control = lmerControl(optimizer = "bobyqa"),
        data = .
    )

    # modelblme <- x %>% blme::blmer(y ~ x1 + x2 + x3 + x4 + x5 + x6 + x7 + z1 + z2 + x1 * z1 + x2 * z1 + x3 * z2 + (1 + x1 + x2 + x3 | group),
    #     REML = TRUE,
    #     data = .
    # )

    # modelrstanarm <- x %>% rstanarm::stan_glmer(y ~ x1 + x2 + x3 + x4 + x5 + x6 + x7 + z1 + z2 + x1 * z1 + x2 * z1 + x3 * z2 + (1 + x1 + x2 + x3 | group),
    #     data = .
    # )

    results <- broom.mixed::tidy(model, conf.int = TRUE)
    # resultsmodelblme <- broom.mixed::tidy(modelblme, conf.int = TRUE)
    # resultsmodelrstanarm <- broom.mixed::tidy(modelrstanarm, conf.int = TRUE)

    return(model)
}
# Perform analyses
map(seq_len(nrow(combinations)), ~ {
    # Perform analyses
    analyses <- pblapply(data[[.x]], lmer.model.ld, cl = cl)
    # Saving results
    write_rds(analyses, file = paste(path, "results/listwise/model_ld_", names[.x], ".rds", sep = ""))
    # Releasing memory
    rm(analyses)
    gc()
})
############################
# Stop parallel processing #
############################
stopCluster(cl)
```

```{r}
#| label: listwise-model
#| code-fold: true

analyses <- list()
for (i in seq_len(nrow(combinations))) {
    analyses[[i]] <- read_rds(paste(path, "results/listwise/model_ld_", names[i], ".rds", sep = ""))
}
```

```{r}
#| label: listwise-results
#| code-fold: true
#| message: false

singular <- list()
for (i in seq_len(nrow(combinations))) {
    singular[[i]] <- map_lgl(analyses[[i]], ~ isSingular(.x)) %>% as.data.frame()
}
singular <- list_cbind(singular)
colnames(singular) <- c("30_15_mar", "50_15_mar", "30_50_mar", "50_50_mar", "30_15_mcar", "50_15_mcar", "30_50_mcar", "50_50_mcar")
```

```{r}
#| label: listwise-table
#| echo: false
#| column: screen-inset-left

datatable(singular,
    rownames = TRUE
) %>%
    formatStyle(
        columns = 1:8,
        backgroundColor = styleEqual(c(FALSE), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 1:8,
        backgroundColor = styleEqual(c(TRUE), c("#FF3030"))
    )

singular %>%
    summarise(across(everything(), ~ sum(.x))) %>%
    t() %>%
    kable(caption = "Amount of singular fits", align = "l")
```

So, especially in the smaller datasets there is a high amount of singular fits. _"Complex mixed-effect models (i.e., those with a large number of variance-covariance parameters) frequently result in singular fits, i.e. estimated variance-covariance matrices with less than full rank. Less technically, this means that some "dimensions" of the variance-covariance matrix have been estimated as exactly zero. For scalar random effects such as intercept-only models, or 2-dimensional random effects such as intercept+slope models, singularity is relatively easy to detect because it leads to random-effect variance estimates of (nearly) zero, or estimates of correlations that are (almost) exactly -1 or 1. However, for more complex models (variance-covariance matrices of dimension >=3) singularity can be hard to detect; models can often be singular without any of their individual variances being close to zero or correlations being close to +/-1."_

```{r}
#| label: rePCA
#| code-fold: true
#| message: false

repca <- list()
sdev <- list()
explained_variance <- list()
for (i in seq_len(nrow(combinations))) {
    repca[[i]] <- map(analyses[[i]], ~ rePCA(.x))
    sdev[[i]] <- map(repca[[i]], \(x) x$group$sdev)

    explained_variance[[i]] <- map(sdev[[i]], \(x) (x)^2 / sum((x)^2)) %>% as.data.frame()
    colnames(explained_variance[[i]]) <- c(paste(1:100))

    explained_variance[[i]] <- explained_variance[[i]] %>%
        mutate(mean = rowMeans(explained_variance[[i]]))
}
meanexplvar <- cbind(explained_variance[[1]]$mean, explained_variance[[2]]$mean, explained_variance[[3]]$mean, explained_variance[[4]]$mean, explained_variance[[5]]$mean, explained_variance[[6]]$mean, explained_variance[[7]]$mean, explained_variance[[8]]$mean) %>%
    as.data.frame() %>%
    mutate(PC = paste0("PC", 1:4)) %>%
    pivot_longer(cols = -PC, names_to = "dataset", values_to = "var_explained")
```

```{r}
#| label: fig-prePCA
#| fig-cap: "Explained variance"
#| echo: false
#| column: screen-inset-left

labels <- c(V1 = "30_15_mar", V2 = "50_15_mar", V3 = "30_50_mar", V4 = "50_50_mar", V5 = "30_15_mcar", V6 = "50_15_mcar", V7 = "30_50_mcar", V8 = "50_50_mcar")
ggplot(
    meanexplvar,
    aes(
        x = PC,
        y = var_explained,
        group = 1
    )
) +
    geom_col(color = "lightskyblue", fill = "lightskyblue") +
    geom_text(aes(label = paste0(sprintf("%.1f", var_explained * 100), "%")), nudge_y = .20, size = 3) +
    geom_point() +
    geom_line() +
    theme_minimal() +
    facet_wrap(~dataset, ncol = 2, labeller = as_labeller(labels))
```

`rePCA()` provides more detail about the singularity pattern, showing the standard deviations of orthogonal variance components and the mapping from variance terms in the model to orthogonal components (i.e., eigenvector/rotation matrices).

### Taking out random slopes

## No missing cases

```{r}
#| label: nomissing-analysis-setup
#| echo: false

combinations.nomissing <- read_rds(paste(path, "data/nomissing/combinations.rds", sep = ""))
names.nomissing <- read_rds(paste(path, "data/nomissing/names.rds", sep = ""))
```

```{r}
#| label: nomissing-data
#| code-fold: true

data <- list()
for (i in seq_len(nrow(combinations.nomissing))) {
    data[[i]] <- read_rds(paste(path, "data/nomissing/simdata_", names.nomissing[i], ".rds", sep = ""))[1:100]
}
```

### Variance

```{r}
#| label: nomissing-variance
#| code-fold: true

variance <- list()
variance <- map(seq_len(nrow(combinations.nomissing)), function(i) {
    result <- data[[i]] %>%
        map(~ .x %>%
            summarise(across(c(x1, x2, x3, x4, x5, x6, x7, y, z1, z2, u0, u1, u2, u3, eij), list(
                var = ~ var(.x, na.rm = TRUE),
                max = ~ max(.x, na.rm = TRUE),
                min = ~ min(.x, na.rm = TRUE)
            ))) %>%
            bind_rows() %>%
            pivot_longer(cols = everything(), names_to = c("variable", ".value"), names_sep = "_")) %>%
        reduce(full_join, by = "variable") %>%
        as_tibble()

    colnames(result) <- c("variable", paste0(rep(c("var", "max", "min")), "_", rep(1:100, each = 3)))

    result
})
plot_variance <- list()
plot_variance <- map(seq_len(nrow(combinations.nomissing)), function(i) {
    variance[[i]] %>%
        pivot_longer(cols = -variable, names_to = c("function", "dataset"), names_sep = "_")
})
```

::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| label: fig-variance3015mar-nomissing
#| fig-cap: "Variance in data set"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15

ggplot(plot_variance[[1]], aes(x = variable, y = value)) +
    geom_boxplot() +
    facet_wrap(~`function`) +
    theme_minimal()
```

## 50_15_mar
```{r}
#| label: fig-variance5015mar-nomissing
#| fig-cap: "Variance in data set"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15

ggplot(plot_variance[[2]], aes(x = variable, y = value)) +
    geom_boxplot() +
    facet_wrap(~`function`) +
    theme_minimal()
```

## 30_50_mar
```{r}
#| label: fig-variance3050mar-nomissing
#| fig-cap: "Variance in data set"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15

ggplot(plot_variance[[3]], aes(x = variable, y = value)) +
    geom_boxplot() +
    facet_wrap(~`function`) +
    theme_minimal()
```

## 50_50_mar
```{r}
#| label: fig-variance5050mar-nomissing
#| fig-cap: "Variance in data set"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15

ggplot(plot_variance[[4]], aes(x = variable, y = value)) +
    geom_boxplot() +
    facet_wrap(~`function`) +
    theme_minimal()
```

## 30_15_mcar
```{r}
#| label: fig-variance3015mcar-nomissing
#| fig-cap: "Variance in data set"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15

ggplot(plot_variance[[5]], aes(x = variable, y = value)) +
    geom_boxplot() +
    facet_wrap(~`function`) +
    theme_minimal()
```

## 50_15_mcar
```{r}
#| label: fig-variance5015mcar-nomissing
#| fig-cap: "Variance in data set"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15

ggplot(plot_variance[[6]], aes(x = variable, y = value)) +
    geom_boxplot() +
    facet_wrap(~`function`) +
    theme_minimal()
```

## 30_50_mcar
```{r}
#| label: fig-variance3050mcar-nomissing
#| fig-cap: "Variance in data set"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15

ggplot(plot_variance[[7]], aes(x = variable, y = value)) +
    geom_boxplot() +
    facet_wrap(~`function`) +
    theme_minimal()
```

## 50_50_mcar
```{r}
#| label: fig-variance5050mcar-nomissing
#| fig-cap: "Variance in data set"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15

ggplot(plot_variance[[8]], aes(x = variable, y = value)) +
    geom_boxplot() +
    facet_wrap(~`function`) +
    theme_minimal()
```

:::

::: 

### Variance analyses

```{r}
#| label: nomissing-analyses
#| code-fold: true

analyses <- list()
for (i in seq_len(nrow(combinations.nomissing))) {
    analyses[[i]] <- read_rds(paste(path, "results/nomissing/analyses_nomiss_", names.nomissing[i], ".rds", sep = ""))
}
```

```{r}
#| label: nomissing-analyses-variance
#| code-fold: true

varianceanalyses <- list()
varianceanalyses <- map(seq_len(nrow(combinations.nomissing)), function(i) {
    result <- map(analyses[[i]], ~ .x %>%
        select(term, estimate)) %>%
        bind_rows() %>%
        filter(!term %in% c("cor__(Intercept).x1", "cor__(Intercept).x2", "cor__(Intercept).x3", "cor__x1.x2", "cor__x2.x3", "cor__x1.x3")) %>%
        mutate(dataset = paste0(rep(1:100, each = 18)))
})
```

::: {.column-screen-inset-left}

::: {.panel-tabset}

## 30_15_mar
```{r}
#| label: fig-varianceanalyses3015mar-nomissing
#| fig-cap: "Variance in analyses results"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15
#| fig-height: 10

ggplot(varianceanalyses[[1]], aes(x = term, y = estimate)) +
    stat_summary(fun = mean, geom = "point", size = 2, fill = "black") +
    stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.1) +
    geom_violin(color = "lightskyblue4", fill = "lightskyblue", alpha = .8, adjust = .5) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 12, angle = 45, hjust = 1))
```

## 50_15_mar
```{r}
#| label: fig-varianceanalyses5015mar-nomissing
#| fig-cap: "Variance in analyses results"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15
#| fig-height: 10

ggplot(varianceanalyses[[2]], aes(x = term, y = estimate)) +
    stat_summary(fun = mean, geom = "point", size = 2, fill = "black") +
    stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.1) +
    geom_violin(color = "lightskyblue4", fill = "lightskyblue", alpha = .8, adjust = .5) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 12, angle = 45, hjust = 1))
```

## 30_50_mar
```{r}
#| label: fig-varianceanalyses3050mar-nomissing
#| fig-cap: "Variance in analyses results"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15
#| fig-height: 10

ggplot(varianceanalyses[[3]], aes(x = term, y = estimate)) +
    stat_summary(fun = mean, geom = "point", size = 2, fill = "black") +
    stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.1) +
    geom_violin(color = "lightskyblue4", fill = "lightskyblue", alpha = .8, adjust = .5) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 12, angle = 45, hjust = 1))
```

## 50_50_mar
```{r}
#| label: fig-varianceanalyses5050mar-nomissing
#| fig-cap: "Variance in analyses results"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15
#| fig-height: 10

ggplot(varianceanalyses[[4]], aes(x = term, y = estimate)) +
    stat_summary(fun = mean, geom = "point", size = 2, fill = "black") +
    stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.1) +
    geom_violin(color = "lightskyblue4", fill = "lightskyblue", alpha = .8, adjust = .5) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 12, angle = 45, hjust = 1))
```

## 30_15_mcar
```{r}
#| label: fig-varianceanalyses3015mcar-nomissing
#| fig-cap: "Variance in analyses results"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15
#| fig-height: 10

ggplot(varianceanalyses[[5]], aes(x = term, y = estimate)) +
    stat_summary(fun = mean, geom = "point", size = 2, fill = "black") +
    stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.1) +
    geom_violin(color = "lightskyblue4", fill = "lightskyblue", alpha = .8, adjust = .5) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 12, angle = 45, hjust = 1))
```

## 50_15_mcar
```{r}
#| label: fig-varianceanalyses5015mcar-nomissing
#| fig-cap: "Variance in analyses results"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15
#| fig-height: 10

ggplot(varianceanalyses[[6]], aes(x = term, y = estimate)) +
    stat_summary(fun = mean, geom = "point", size = 2, fill = "black") +
    stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.1) +
    geom_violin(color = "lightskyblue4", fill = "lightskyblue", alpha = .8, adjust = .5) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 12, angle = 45, hjust = 1))
```

## 30_50_mcar
```{r}
#| label: fig-varianceanalyses3050mcar-nomissing
#| fig-cap: "Variance in analyses results"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15
#| fig-height: 10

ggplot(varianceanalyses[[7]], aes(x = term, y = estimate)) +
    stat_summary(fun = mean, geom = "point", size = 2, fill = "black") +
    stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.1) +
    geom_violin(color = "lightskyblue4", fill = "lightskyblue", alpha = .8, adjust = .5) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 12, angle = 45, hjust = 1))
```

## 50_50_mcar
```{r}
#| label: fig-varianceanalyses5050mcar-nomissing
#| fig-cap: "Variance in analyses results"
#| echo: false
#| column: screen-inset-left
#| fig-width: 15
#| fig-height: 10

ggplot(varianceanalyses[[8]], aes(x = term, y = estimate)) +
    stat_summary(fun = mean, geom = "point", size = 2, fill = "black") +
    stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.1) +
    geom_violin(color = "lightskyblue4", fill = "lightskyblue", alpha = .8, adjust = .5) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 12, angle = 45, hjust = 1))
```

:::

:::

### Singularity and non-convergence problem 

```{r}
#| label: nomissing-analysis
#| code-fold: true
#| message: false
#| warning: false
#| eval: false

############
# Set seed #
############
set.seed(123)
############################
# Plan parallel processing #
############################
cl <- makeForkCluster(5)
#######################
# Multilevel analysis #
#######################
# Define model
lmer.model.nomiss <- function(x) {
    model <- x %>% lme4::lmer(y ~ x1 + x2 + x3 + x4 + x5 + x6 + x7 + z1 + z2 + x1 * z1 + x2 * z1 + x3 * z2 + (1 + x1 + x2 + x3 | group),
        REML = TRUE,
        control = lmerControl(optimizer = "bobyqa"),
        data = .
    )

    nlmemodel <- x %>% nlme::lme(y ~ x1 + x2 + x3 + x4 + x5 + x6 + x7 + z1 + z2 + x1 * z1 + x2 * z1 + x3 * z2,
        random = ~ 1 + x1 + x2 + x3 | group,
        data = .,
        method = "REML",
        control = nlme::lmeControl(returnObject = TRUE)
    )

    results <- broom.mixed::tidy(model, conf.int = TRUE)

    return(list(model = model, nlme = nlmemodel))
}
# Perform analyses
map(seq_len(nrow(combinations.nomissing)), ~ {
    # Perform analyses
    analyses <- pblapply(data[[.x]], lmer.model.nomiss, cl = cl)
    # Saving results
    write_rds(analyses, file = paste(path, "results/nomissing/model_nomiss_", names.nomissing[.x], ".rds", sep = ""))
    # Releasing memory
    rm(analyses)
    gc()
})
############################
# Stop parallel processing #
############################
stopCluster(cl)
```

```{r}
#| label: nomissing-model
#| code-fold: true

analyses <- list()
for (i in seq_len(nrow(combinations.nomissing))) {
    analyses[[i]] <- read_rds(paste(path, "results/nomissing/model_nomiss_", names.nomissing[i], ".rds", sep = "")) %>% map(~ .x %>% .$model)
}
```

```{r}
#| label: nomissing-results
#| code-fold: true
#| message: false

singular <- list()
for (i in seq_len(nrow(combinations.nomissing))) {
    singular[[i]] <- map_lgl(analyses[[i]], ~ isSingular(.x)) %>% as.data.frame()
}
singular <- list_cbind(singular)
colnames(singular) <- c("30_15_mar", "50_15_mar", "30_50_mar", "50_50_mar", "30_15_mcar", "50_15_mcar", "30_50_mcar", "50_50_mcar")
```

```{r}
#| label: nomissing-table
#| echo: false
#| column: screen-inset-left

datatable(singular,
    rownames = TRUE
) %>%
    formatStyle(
        columns = 1:8,
        backgroundColor = styleEqual(c(FALSE), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 1:8,
        backgroundColor = styleEqual(c(TRUE), c("#FF3030"))
    )

singular %>%
    summarise(across(everything(), ~ sum(.x))) %>%
    t() %>%
    kable(caption = "Amount of singular fits", align = "l")
```

```{r}
#| label: rePCA-nomissing
#| code-fold: true
#| message: false

repca <- list()
sdev <- list()
explained_variance <- list()
for (i in seq_len(nrow(combinations.nomissing))) {
    repca[[i]] <- map(analyses[[i]], ~ rePCA(.x))
    sdev[[i]] <- map(repca[[i]], \(x) x$group$sdev)

    explained_variance[[i]] <- map(sdev[[i]], \(x) (x)^2 / sum((x)^2)) %>% as.data.frame()
    colnames(explained_variance[[i]]) <- c(paste(1:100))

    explained_variance[[i]] <- explained_variance[[i]] %>%
        mutate(mean = rowMeans(explained_variance[[i]]))
}
meanexplvar <- cbind(explained_variance[[1]]$mean, explained_variance[[2]]$mean, explained_variance[[3]]$mean, explained_variance[[4]]$mean, explained_variance[[5]]$mean, explained_variance[[6]]$mean, explained_variance[[7]]$mean, explained_variance[[8]]$mean) %>%
    as.data.frame() %>%
    mutate(PC = paste0("PC", 1:4)) %>%
    pivot_longer(cols = -PC, names_to = "dataset", values_to = "var_explained")
```

```{r}
#| label: fig-prePCA-nomissing
#| fig-cap: "Explained variance"
#| echo: false
#| column: screen-inset-left

labels <- c(V1 = "30_15_mar", V2 = "50_15_mar", V3 = "30_50_mar", V4 = "50_50_mar", V5 = "30_15_mcar", V6 = "50_15_mcar", V7 = "30_50_mcar", V8 = "50_50_mcar")
ggplot(
    meanexplvar,
    aes(
        x = PC,
        y = var_explained,
        group = 1
    )
) +
    geom_col(color = "lightskyblue", fill = "lightskyblue") +
    geom_text(aes(label = paste0(sprintf("%.1f", var_explained * 100), "%")), nudge_y = .20, size = 3) +
    geom_point() +
    geom_line() +
    theme_minimal() +
    facet_wrap(~dataset, ncol = 2, labeller = as_labeller(labels))
```

### ICC 

```{r}
#| labels: icc-nomissing
#| code-fold: true
#| message: false

iccvalues <- list()
iccvalues <- map(seq_len(nrow(combinations.nomissing)), function(i) {
    result <- data[[i]] %>%
        map(~ .x %>%
            lmer(y ~ 1 + (1 | group), REML = TRUE, data = .) %>%
            summ() %>%
            .$gvars %>%
            .[3]) %>%
        as.numeric() %>%
        as.data.frame()
    # Reduce("+", .) / length(data[[i]])
    result
})
iccvalues <- list_cbind(iccvalues)
colnames(iccvalues) <- c("30_15_mar", "50_15_mar", "30_50_mar", "50_50_mar", "30_15_mcar", "50_15_mcar", "30_50_mcar", "50_50_mcar")
```

```{r}
#| label: table-icc-nomissing
#| echo: false
#| column: screen-inset-left
#| message: false

datatable(iccvalues,
    rownames = TRUE,
    class = "cell-border stripe"
) %>%
    formatRound(
        columns = 1:8,
        digits = 2
    ) %>%
    formatStyle(
        columns = 1:8,
        backgroundColor = styleInterval(c(.375, .4, .425, .45, .475, .525, .55, .575, .6, .625), c("#ff0000", "#f96200", "#e59400", "#ccbb00", "#a9de00", "#6fff00", "#a9de00", "#ccbb00", "#e59400", "#f96200", "#ff0000"))
    )

iccvalues %>%
    summarise(across(everything(), ~ mean(.x))) %>%
    t() %>%
    kable(caption = "Average ICC value", align = "l", digits = 2)
```



<!-- ## PMM 

```{r}
#| label: pmm-data
#| code-fold: true
#| message: false
#| eval: false

###################
# Loading results #
###################
# Extracting imputation objects from results
data <- list()
for (i in seq_len(nrow(combinations))) {
    data[[i]] <- map(read_rds(paste(path, "results/imputed/pmm/results_pmm_", names[i], ".rds", sep = "")), ~ .x$imp)
}
```

### Singularity and non-convergence problem 

```{r}
#| label: pmm-analysis
#| code-fold: true
#| message: false
#| eval: false

############
# Set seed #
############
set.seed(123)
############################
# Plan parallel processing #
############################
cl <- makeForkCluster(5)
#####################
# Obtaining results #
#####################
# Define model
lmer.model <- function(x) {
    model <- with(x, lme4::lmer(y ~ 1 + x1 + x2 + x3 + x4 + x5 + x6 + x7 + z1 + z2 + x1 * z1 + x2 * z1 + x3 * z2 + (1 + x1 + x2 + x3 | group), REML = TRUE, control = lme4:::lmerControl(optimizer = "bobyqa")))
    result <- mitml::testEstimates(mice::as.mitml.result(model), extra.pars = TRUE)

    return(model)
}
# Perform analyses
map(seq_len(nrow(combinations)), ~ {
    # Perform analyses
    analyses <- pblapply(data[[.x]], lmer.model, cl = cl)
    # Saving results
    write_rds(analyses, file = paste(path, "results/imputed/pmm/model_pmm_", names[.x], ".rds", sep = ""))
    # Releasing memory
    rm(analyses)
    gc()
})
############################
# Stop parallel processing #
############################
stopCluster(cl)
```

```{r}
#| label: pmm-model
#| code-fold: true
#| eval: false

analyses <- list()
for (i in seq_len(nrow(combinations))) {
    analyses[[i]] <- read_rds(paste(path, "results/imputed/pmm/model_pmm_", names[i], ".rds", sep = ""))
}
```

```{r}
#| label: pmm-results
#| code-fold: true
#| message: false
#| eval: false

singular <- map(seq_len(nrow(combinations)), function(i) {
    analyses <- read_rds(paste(path, "results/imputed/pmm/model_pmm_", names[i], ".rds", sep = ""))
    map_lgl(analyses, function(x) {
        sum(map_lgl(x[[4]], isSingular)) > 0
    }) %>% as.data.frame()
})
singular <- list_cbind(singular)
colnames(singular) <- c("30_15_mar", "50_15_mar", "30_50_mar", "50_50_mar", "30_15_mcar", "50_15_mcar", "30_50_mcar", "50_50_mcar")
```

```{r}
#| label: pmmm-table
#| echo: false
#| column: screen-inset-left
#| message: false

datatable(singular,
    rownames = TRUE
) %>%
    formatStyle(
        columns = 1:8,
        backgroundColor = styleEqual(c(FALSE), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 1:8,
        backgroundColor = styleEqual(c(TRUE), c("#FF3030"))
    )

singular %>%
    summarise(across(everything(), ~ sum(.x))) %>%
    t() %>%
    kable(caption = "Amount of singular fits", align = "l")
```

```{r}
#| label: rePCA-pmm
#| code-fold: true
#| message: false
#| eval: false

sdev <- list()
explained_variance <- list()

sdev <- map(seq_len(nrow(combinations)), function(i) {
    analyses <- read_rds(paste(path, "results/imputed/pmm/model_pmm_", names[i], ".rds", sep = ""))
    map(analyses, function(x) {
        map(x[[4]], function(y) {
            rePCA(y) %$% group$sdev
        }) %>%
            map_dfr(., ~ as.data.frame(t(.x))) %>%
            colMeans()
    })
})

for (i in seq_len(nrow(combinations))) {
    explained_variance[[i]] <- map(sdev[[i]], \(x) (x)^2 / sum((x)^2)) %>% as.data.frame()
    colnames(explained_variance[[i]]) <- c(paste(1:100))

    explained_variance[[i]] <- explained_variance[[i]] %>%
        mutate(mean = rowMeans(explained_variance[[i]]))
}
meanexplvar <- cbind(explained_variance[[1]]$mean, explained_variance[[2]]$mean, explained_variance[[3]]$mean, explained_variance[[4]]$mean, explained_variance[[5]]$mean, explained_variance[[6]]$mean, explained_variance[[7]]$mean, explained_variance[[8]]$mean) %>%
    as.data.frame() %>%
    mutate(PC = paste0("PC", 1:4)) %>%
    pivot_longer(cols = -PC, names_to = "dataset", values_to = "var_explained")
```

```{r}
#| label: fig-prePCA-pmm
#| fig-cap: "Explained variance"
#| echo: false
#| column: screen-inset-left
#| eval: false

labels <- c(V1 = "30_15_mar", V2 = "50_15_mar", V3 = "30_50_mar", V4 = "50_50_mar", V5 = "30_15_mcar", V6 = "50_15_mcar", V7 = "30_50_mcar", V8 = "50_50_mcar")
ggplot(
    meanexplvar,
    aes(
        x = PC,
        y = var_explained,
        group = 1
    )
) +
    geom_col(color = "lightskyblue", fill = "lightskyblue") +
    geom_text(aes(label = paste0(sprintf("%.1f", var_explained * 100), "%")), nudge_y = .20, size = 3) +
    geom_point() +
    geom_line() +
    theme_minimal() +
    facet_wrap(~dataset, ncol = 2, labeller = as_labeller(labels))
```

## BART

```{r}
#| label: bart-data
#| code-fold: true
#| message: false
#| eval: false

###################
# Loading results #
###################
# Extracting imputation objects from results
data <- list()
for (i in seq_len(nrow(combinations))) {
    data[[i]] <- map(read_rds(paste(path, "results/imputed/bart/results_bart_", names[i], ".rds", sep = "")), ~ .x$imp)
}
```

### Singularity and non-convergence problem 

```{r}
#| label: bart-analysis
#| code-fold: true
#| message: false
#| eval: false

############
# Set seed #
############
set.seed(123)
############################
# Plan parallel processing #
############################
cl <- makeForkCluster(5)
#####################
# Obtaining results #
#####################
# Define model
lmer.model <- function(x) {
    model <- with(x, lme4::lmer(y ~ 1 + x1 + x2 + x3 + x4 + x5 + x6 + x7 + z1 + z2 + x1 * z1 + x2 * z1 + x3 * z2 + (1 + x1 + x2 + x3 | group), REML = TRUE, control = lme4:::lmerControl(optimizer = "bobyqa")))
    result <- mitml::testEstimates(mice::as.mitml.result(model), extra.pars = TRUE)

    return(model)
}
# Perform analyses
map(seq_len(nrow(combinations)), ~ {
    # Perform analyses
    analyses <- pblapply(data[[.x]], lmer.model, cl = cl)
    # Saving results
    write_rds(analyses, file = paste(path, "results/imputed/bart/model_bart_", names[.x], ".rds", sep = ""))
    # Releasing memory
    rm(analyses)
    gc()
})
############################
# Stop parallel processing #
############################
stopCluster(cl)
```

```{r}
#| label: bart-model
#| code-fold: true
#| eval: false

analyses <- list()
for (i in seq_len(nrow(combinations))) {
    analyses[[i]] <- read_rds(paste(path, "results/imputed/bart/model_bart_", names[i], ".rds", sep = ""))
}
```

```{r}
#| label: bart-results
#| code-fold: true
#| message: false
#| eval: false

singular <- map(seq_len(nrow(combinations)), function(i) {
    analyses <- read_rds(paste(path, "results/imputed/bart/model_bart_", names[i], ".rds", sep = ""))
    map_lgl(analyses, function(x) {
        sum(map_lgl(x[[4]], isSingular)) > 0
    }) %>% as.data.frame()
})
singular <- list_cbind(singular)
colnames(singular) <- c("30_15_mar", "50_15_mar", "30_50_mar", "50_50_mar", "30_15_mcar", "50_15_mcar", "30_50_mcar", "50_50_mcar")
```

```{r}
#| label: bartm-table
#| echo: false
#| column: screen-inset-left
#| eval: false

datatable(singular,
    rownames = TRUE
) %>%
    formatStyle(
        columns = 1:8,
        backgroundColor = styleEqual(c(FALSE), c("#00FF7F"))
    ) %>%
    formatStyle(
        columns = 1:8,
        backgroundColor = styleEqual(c(TRUE), c("#FF3030"))
    )

singular %>%
    summarise(across(everything(), ~ sum(.x))) %>%
    t() %>%
    kable(caption = "Amount of singular fits", align = "l")
```

```{r}
#| label: rePCA-bart
#| code-fold: true
#| message: false
#| eval: false

sdev <- list()
explained_variance <- list()

sdev <- map(seq_len(nrow(combinations)), function(i) {
    analyses <- read_rds(paste(path, "results/imputed/bart/model_bart_", names[i], ".rds", sep = ""))
    map(analyses, function(x) {
        map(x[[4]], function(y) {
            rePCA(y) %$% group$sdev
        }) %>%
            map_dfr(., ~ as.data.frame(t(.x))) %>%
            colMeans()
    })
})

for (i in seq_len(nrow(combinations))) {
    explained_variance[[i]] <- map(sdev[[i]], \(x) (x)^2 / sum((x)^2)) %>% as.data.frame()
    colnames(explained_variance[[i]]) <- c(paste(1:100))

    explained_variance[[i]] <- explained_variance[[i]] %>%
        mutate(mean = rowMeans(explained_variance[[i]]))
}
meanexplvar <- cbind(explained_variance[[1]]$mean, explained_variance[[2]]$mean, explained_variance[[3]]$mean, explained_variance[[4]]$mean, explained_variance[[5]]$mean, explained_variance[[6]]$mean, explained_variance[[7]]$mean, explained_variance[[8]]$mean) %>%
    as.data.frame() %>%
    mutate(PC = paste0("PC", 1:4)) %>%
    pivot_longer(cols = -PC, names_to = "dataset", values_to = "var_explained")
```

```{r}
#| label: fig-prePCA-bart
#| fig-cap: "Explained variance"
#| echo: false
#| column: screen-inset-left
#| eval: false

labels <- c(V1 = "30_15_mar", V2 = "50_15_mar", V3 = "30_50_mar", V4 = "50_50_mar", V5 = "30_15_mcar", V6 = "50_15_mcar", V7 = "30_50_mcar", V8 = "50_50_mcar")
ggplot(
    meanexplvar,
    aes(
        x = PC,
        y = var_explained,
        group = 1
    )
) +
    geom_col(color = "lightskyblue", fill = "lightskyblue") +
    geom_text(aes(label = paste0(sprintf("%.1f", var_explained * 100), "%")), nudge_y = .20, size = 3) +
    geom_point() +
    geom_line() +
    theme_minimal() +
    facet_wrap(~dataset, ncol = 2, labeller = as_labeller(labels))
``` -->